### 2020-02-05 README.Rmd
Update README.Rmd
Notes to M & M re: the template.

---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# New Project

<!-- badges: start -->
<!-- badges: end -->

Hi M & M,

I thought I'd try to use Dani Navarro's github template for a new experiment that 
I learned about late last year. Some of these folders won't be necessary for us 
(e.g., experiments, given that we only have one), but she has notes in 
the folders explaining how she uses them, so I think it's helpful to review and 
keep in mind her workflow. I like learning from folks who do these things more than 
I do! So, feel free to play around and read the various readme files. I'll update this as
we go, and I'll add things to the .gitignore as I see fit too (e.g., data -- we'll want
to hide this given that it's a public repo, but we'll need the folder on our computers so
we can run the code).

jen

This is a template for a new research project. Should contains the following
folders: [analysis](./analysis), [data](./data), [experiments](./experiments),
[other](./other), [preprocessing](./preprocessing). Optionally, it may also 
include a folder `models` containing modelling files, and a `writeup` folder
containing the project writeup.

If there are other resouces (e.g., OSF folders, Overleaf documents, Google docs)
that are linked to the project, they should be listed in this document.

### 2020-12-21 README.Rmd
revise template to our project

@@
 ```
-# New Project
+# What do incoming university students believe about open science practices in psychology?
 
@@
 
-Hi M & M,
+This project explores incoming students' knowledge about, and attitudes toward,
+open science practices. This project is led by Michael Philipp, Matthew Williams, 
+and Jennifer Beaudry.
 
-I thought I'd try to use Dani Navarro's github template for a new experiment that 
-I learned about late last year. Some of these folders won't be necessary for us 
-(e.g., experiments, given that we only have one), but she has notes in 
-the folders explaining how she uses them, so I think it's helpful to review and 
-keep in mind her workflow. I like learning from folks who do these things more than 
-I do! So, feel free to play around and read the various readme files. I'll update this as
-we go, and I'll add things to the .gitignore as I see fit too (e.g., data -- we'll want
-to hide this given that it's a public repo, but we'll need the folder on our computers so
-we can run the code).
+OSF page for this project: https://osf.io/gmsbn/
 
-jen
+<!-- _Notes from Dani's template:_ -->
 
-This is a template for a new research project. Should contains the following
-folders: [analysis](./analysis), [data](./data), [experiments](./experiments),
-[other](./other), [preprocessing](./preprocessing). Optionally, it may also 
-include a folder `models` containing modelling files, and a `writeup` folder
-containing the project writeup.
+<!-- This is a template for a new research project. Should contains the following -->
+<!-- folders: [analysis](./analysis), [data](./data), [experiments](./experiments), -->
+<!-- [other](./other), [preprocessing](./preprocessing). Optionally, it may also  -->
+<!-- include a folder `models` containing modelling files, and a `writeup` folder -->
+<!-- containing the project writeup.  -->
 
-If there are other resouces (e.g., OSF folders, Overleaf documents, Google docs)
-that are linked to the project, they should be listed in this document.
+<!-- If there are other resouces (e.g., OSF folders, Overleaf documents, Google docs) -->
+<!-- that are linked to the project, they should be listed in this document. -->

### 2020-12-21 analysis/untitled.Rmd
revise template to our project

---
title: "Untitled"
author: 'Brandon McMurtrie, ID: 18036371'
date: "09/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
library(tidyverse)
library(Rmisc)
library(rcompanion)

```

```{r loading data}
frames <- read.csv(file = "open_science.csv")
```

### Critical Counter-norm

```{r critical cnorm}

critical_cnorm.NA.RM <- na.omit(frames$critical_cnorm)

sd(critical_cnorm.NA.RM)

CI(critical_cnorm.NA.RM, ci = 0.95)

agree_critical_cnorm <- critical_cnorm.NA.RM >= 4
p.agree_critical_cnorm <- mean(agree_critical_cnorm)

disagree_critical_cnorm <- critical_cnorm.NA.RM <=2
p.disagree_critical_cnorm <- mean(disagree_critical_cnorm)

p.agree_critical_cnorm

p.disagree_critical_cnorm

length(critical_cnorm.NA.RM)

```

| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:---------:|:-------:|:---------:|
| 2.41 | 1.06 | 2.27, 2.54 | 0.24 |0.68|

### Critical Norm
```{r critical_norm}
critical_norm.NA.RM <- na.omit(frames$critical_norm)

sd(critical_norm.NA.RM)

CI(critical_norm.NA.RM, ci = 0.95)

agree_critical_norm <- critical_norm.NA.RM >= 4
p.agree_critical_norm <- mean(agree_critical_norm)

disagree_critical_norm <- critical_norm.NA.RM <=2
p.disagree_critical_norm <- mean(disagree_critical_norm)

p.agree_critical_norm
p.disagree_critical_norm

length(critical_norm.NA.RM)
```

| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:---------:|:-------:|:---------:|
| 4.32 | 0.82 | 4.21,4.42 | 0.93 | 0.05  |

### Preregistration Norm

```{r Prereg_norm}
Prereg_norm.NA.RM <- na.omit(frames$Prereg_norm)

sd(Prereg_norm.NA.RM)

agree_Prereg_norm <- Prereg_norm.NA.RM >= 4
p.agree_Prereg_norm <- mean(agree_Prereg_norm)

disagree_Prereg_norm <- Prereg_norm.NA.RM <=2
p.disagree_Prereg_norm <- mean(disagree_Prereg_norm)

CI(Prereg_norm.NA.RM, ci = 0.95)

p.agree_Prereg_norm
p.disagree_Prereg_norm

length(Prereg_norm.NA.RM)
```

| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:---------:|:-------:|:---------:|
| 3.96 | 1.07 | 3.82, 4.10 | 0.75 | 0.12 |

### Preregistration Counter-norm

```{r Prereg_cnorm}
Prereg_cnorm.NA.RM <- na.omit(frames$Prereg_cnorm)

sd(Prereg_cnorm.NA.RM)

CI(Prereg_cnorm.NA.RM, ci = 0.95)

agree_Prereg_cnorm <- Prereg_cnorm.NA.RM >= 4
p.agree_Prereg_cnorm <- mean(agree_Prereg_cnorm)

disagree_Prereg_cnorm <- Prereg_cnorm.NA.RM <=2
p.disagree_Prereg_cnorm <- mean(disagree_Prereg_cnorm)

p.agree_Prereg_cnorm
p.disagree_Prereg_cnorm

length(Prereg_cnorm.NA.RM)
```

| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:---------:|:-------:|:---------:|
| 2.74 | 1.24 | 2.58, 2.90 | 0.32 | 0.50 |

### Regreport Norm

```{r Regreport norm}
RegReport_norm.NA.RM <- na.omit(frames$RegReport_norm)

sd(RegReport_norm.NA.RM)

CI(RegReport_norm.NA.RM, ci = 0.95)

agree_RegReport_norm <- RegReport_norm.NA.RM >= 4
p.agree_RegReport_norm <- mean(agree_RegReport_norm)

disagree_RegReport_norm <- RegReport_norm.NA.RM <=2
p.disagree_RegReport_norm <- mean(disagree_RegReport_norm)

p.agree_RegReport_norm
p.disagree_RegReport_norm

length(RegReport_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|Reg_report| 3.35 | 1.26 | 3.19, 3.52 | 0.56 | 0.27 |

### Regreport Counter-norm

```{r Regreport cnorm}
RegReport_cnorm.NA.RM <- na.omit(frames$RegReport_cnorm)

sd(RegReport_cnorm.NA.RM)

CI(RegReport_cnorm.NA.RM, ci = 0.95)

agree_RegReport_cnorm <- RegReport_cnorm.NA.RM >= 4
p.agree_RegReport_cnorm <- mean(agree_RegReport_cnorm)

disagree_RegReport_cnorm <- RegReport_cnorm.NA.RM <=2
p.disagree_RegReport_cnorm <- mean(disagree_RegReport_cnorm)

p.agree_RegReport_cnorm
p.disagree_RegReport_cnorm

length(RegReport_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|Reg_report_cnorm| 3.56 | 1.20 | 3.41, 3.71 | 0.59 | 0.26 |

### p hacking counter-norm

```{r phack_cnorm}
phack_cnorm.NA.RM <- na.omit(frames$phack_cnorm)

sd(phack_cnorm.NA.RM)

CI(phack_cnorm.NA.RM, ci = 0.95)

agree_phack_cnorm <- phack_cnorm.NA.RM >= 4
p.agree_phack_cnorm <- mean(agree_phack_cnorm)

disagree_phack_cnorm <- phack_cnorm.NA.RM <=2
p.disagree_phack_cnorm <- mean(disagree_phack_cnorm)

p.agree_phack_cnorm
p.disagree_phack_cnorm

length(phack_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|phack_cnorm| 2.12 | 1.27 | 1.96, 2.29 | 0.19 | 0.75 |

### p hacking Norm

```{r phack_norm}
phack_norm.NA.RM <- na.omit(frames$phack_norm)

sd(phack_norm.NA.RM)

CI(phack_norm.NA.RM, ci = 0.95)

agree_phack_norm <- phack_norm.NA.RM >= 4
p.agree_phack_norm <- mean(agree_phack_norm)

disagree_phack_norm <- phack_norm.NA.RM <=2
p.disagree_phack_norm <- mean(disagree_phack_norm)

p.agree_phack_norm
p.disagree_phack_norm

length(phack_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|phack_norm| 4.33 | 0.90 | 4.22, 4.45 | 0.87 | 0.08 |

### Hark counter-norm

```{r HARK cnorm}
HARK_cnorm.NA.RM <- na.omit(frames$HARK_cnorm)

sd(HARK_cnorm.NA.RM)

CI(HARK_cnorm.NA.RM, ci = 0.95)

agree_HARK_cnorm <- HARK_cnorm.NA.RM >= 4
p.agree_HARK_cnorm <- mean(agree_HARK_cnorm)

disagree_HARK_cnorm <- HARK_cnorm.NA.RM <=2
p.disagree_HARK_cnorm <- mean(disagree_HARK_cnorm)

p.agree_HARK_cnorm
p.disagree_HARK_cnorm

length(HARK_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|HARK_cnorm| 1.65 | 1.07 | 1.52, 1.79 | 0.11 | 0.82 |

### Hark Norm

```{r HARK Norm}
HARK_norm.NA.RM <- na.omit(frames$HARK_norm)

sd(HARK_norm.NA.RM)

CI(HARK_norm.NA.RM, ci = 0.95)

agree_HARK_norm <- HARK_norm.NA.RM >= 4
p.agree_HARK_norm <- mean(agree_HARK_norm)

disagree_HARK_norm <- HARK_norm.NA.RM <=2
p.disagree_HARK_norm <- mean(disagree_HARK_norm)

p.agree_HARK_norm
p.disagree_HARK_norm

length(HARK_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|HARK_norm| 3.88 | 1.09 | 3.74, 4.02 | 0.70 | 0.12 |

### InfoForRep Norm

```{r InfoForRep_norm}
InfoForRep_norm.NA.RM <- na.omit(frames$InfoForRep_norm)

sd(InfoForRep_norm.NA.RM)

CI(InfoForRep_norm.NA.RM, ci = 0.95)

agree_InfoForRep_norm <- InfoForRep_norm.NA.RM >= 4
p.agree_InfoForRep_norm <- mean(agree_InfoForRep_norm)

disagree_InfoForRep_norm <- InfoForRep_norm.NA.RM <=2
p.disagree_InfoForRep_norm <- mean(disagree_InfoForRep_norm)

p.agree_InfoForRep_norm
p.disagree_InfoForRep_norm

length(InfoForRep_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|InfoForRep_norm| 4.42 | 0.99 | 4.29, 4.55 | 0.88 | 0.08 |

### InfoForRep Counter-norm

```{r InfoForRep_cnorm}
InfoForRep_cnorm.NA.RM <- na.omit(frames$InfoForRep_cnorm)

sd(InfoForRep_cnorm.NA.RM)

CI(InfoForRep_cnorm.NA.RM, ci = 0.95)

agree_InfoForRep_cnorm <- InfoForRep_cnorm.NA.RM >= 4
p.agree_InfoForRep_cnorm <- mean(agree_InfoForRep_cnorm)

disagree_InfoForRep_cnorm <- InfoForRep_cnorm.NA.RM <=2
p.disagree_InfoForRep_cnorm <- mean(disagree_InfoForRep_cnorm)

p.agree_InfoForRep_cnorm
p.disagree_InfoForRep_cnorm

length(InfoForRep_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|InfoForRep_cnorm| 1.52 | 0.95 | 1.40, 1.64 | 0.07 | 0.87 |

### Preprint Norm

```{r Preprint_norm}
Preprint_norm.NA.RM <- na.omit(frames$Preprint_norm)

sd(Preprint_norm.NA.RM)

CI(Preprint_norm.NA.RM, ci = 0.95)

agree_Preprint_norm <- Preprint_norm.NA.RM >= 4
p.agree_Preprint_norm <- mean(agree_Preprint_norm)

disagree_Preprint_norm <- Preprint_norm.NA.RM <=2
p.disagree_Preprint_norm <- mean(disagree_Preprint_norm)

p.agree_Preprint_norm
p.disagree_Preprint_norm

length(Preprint_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|Preprint_norm| 1.61 | 0.78 | 1.51, 1.71 | 0.03 | 0.90 |

### Preprint Counter-Norm

```{r Preprint_cnorm}
Preprint_cnorm.NA.RM <- na.omit(frames$Preprint_cnorm)

sd(Preprint_cnorm.NA.RM)

CI(Preprint_cnorm.NA.RM, ci = 0.95)

agree_Preprint_cnorm <- Preprint_cnorm.NA.RM >= 4
p.agree_Preprint_cnorm <- mean(agree_Preprint_cnorm)

disagree_Preprint_cnorm <- Preprint_cnorm.NA.RM <=2
p.disagree_Preprint_cnorm <- mean(disagree_Preprint_cnorm)

p.agree_Preprint_cnorm
p.disagree_Preprint_cnorm

length(Preprint_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|Preprint_cnorm| 4.36 | 0.81 | 4.26, 4.46 | 0.88 | 0.03 |

### Open Materials Norm

```{r OpenMaterials_norm}
OpenMaterials_norm.NA.RM <- na.omit(frames$OpenMaterials_norm)

sd(OpenMaterials_norm.NA.RM)

CI(OpenMaterials_norm.NA.RM, ci = 0.95)

agree_OpenMaterials_norm <- OpenMaterials_norm.NA.RM >= 4
p.agree_OpenMaterials_norm <- mean(agree_OpenMaterials_norm)

disagree_OpenMaterials_norm <- OpenMaterials_norm.NA.RM <=2
p.disagree_OpenMaterials_norm <- mean(disagree_OpenMaterials_norm)

p.agree_OpenMaterials_norm
p.disagree_OpenMaterials_norm

length(OpenMaterials_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|OpenMaterials_norm| 3.68 | 1.03 | 3.55, 3.82 | 0.66 | 0.15 |

### Open Materials Counter-norm

```{r OpenMaterials_cnorm}
OpenMaterials_cnorm.NA.RM <- na.omit(frames$OpenMaterials_cnorm)

sd(OpenMaterials_cnorm.NA.RM)

CI(OpenMaterials_cnorm.NA.RM, ci = 0.95)

agree_OpenMaterials_cnorm <- OpenMaterials_cnorm.NA.RM >= 4
p.agree_OpenMaterials_cnorm <- mean(agree_OpenMaterials_cnorm)

disagree_OpenMaterials_cnorm <- OpenMaterials_cnorm.NA.RM <=2
p.disagree_OpenMaterials_cnorm <- mean(disagree_OpenMaterials_cnorm)

p.agree_OpenMaterials_cnorm
p.disagree_OpenMaterials_cnorm

length(OpenMaterials_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|OpenMaterials_cnorm| 2.5 | 1.15 | 2.35, 2.65 | 0.23 | 0.60 |

### Open Data Norm

```{r OpenData_norm}
OpenData_norm.NA.RM <- na.omit(frames$OpenData_norm)

sd(OpenData_norm.NA.RM)

CI(OpenData_norm.NA.RM, ci = 0.95)

agree_OpenData_norm <- OpenData_norm.NA.RM >= 4
p.agree_OpenData_norm <- mean(agree_OpenData_norm)

disagree_OpenData_norm <- OpenData_norm.NA.RM <=2
p.disagree_OpenData_norm <- mean(disagree_OpenData_norm)

p.agree_OpenData_norm
p.disagree_OpenData_norm

length(OpenData_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|OpenData_norm| 2.65 | 1.21 | 2.49, 2.80 | 0.26 | 0.49 |

### Open Data Counter-norm

```{r OpenData_cnorm}
OpenData_cnorm.NA.RM <- na.omit(frames$OpenData_cnorm)

sd(OpenData_cnorm.NA.RM)

CI(OpenData_cnorm.NA.RM, ci = 0.95)

agree_OpenData_cnorm <- OpenData_cnorm.NA.RM >= 4
p.agree_OpenData_cnorm <- mean(agree_OpenData_cnorm)

disagree_OpenData_cnorm <- OpenData_cnorm.NA.RM <=2
p.disagree_OpenData_cnorm <- mean(disagree_OpenData_cnorm)

p.agree_OpenData_cnorm
p.disagree_OpenData_cnorm

length(OpenData_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|OpenData_cnorm| 3.49 | 1.25 | 3.33, 3.65 | 0.55 | 0.28 |

### Open Acc Norm

```{r OpenAcc_norm}
OpenAcc_norm.NA.RM <- na.omit(frames$OpenAcc_norm)

sd(OpenAcc_norm.NA.RM)

CI(OpenAcc_norm.NA.RM, ci = 0.95)

agree_OpenAcc_norm <- OpenAcc_norm.NA.RM >= 4
p.agree_OpenAcc_norm <- mean(agree_OpenAcc_norm)

disagree_OpenAcc_norm <- OpenAcc_norm.NA.RM <=2
p.disagree_OpenAcc_norm <- mean(disagree_OpenAcc_norm)

p.agree_OpenAcc_norm
p.disagree_OpenAcc_norm

length(OpenAcc_norm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|OpenAcc_norm| 3.85 | 0.90 | 3.74, 3.97 | 0.70 | 0.07 |

### Open Acc Counter-norm

```{r OpenAcc_cnorm}
OpenAcc_cnorm.NA.RM <- na.omit(frames$OpenAcc_cnorm)

sd(OpenAcc_cnorm.NA.RM)

CI(OpenAcc_cnorm.NA.RM, ci = 0.95)

agree_OpenAcc_cnorm <- OpenAcc_cnorm.NA.RM >= 4
p.agree_OpenAcc_cnorm <- mean(agree_OpenAcc_cnorm)

disagree_OpenAcc_cnorm <- OpenAcc_cnorm.NA.RM <=2
p.disagree_OpenAcc_cnorm <- mean(disagree_OpenAcc_cnorm)

p.agree_OpenAcc_cnorm
p.disagree_OpenAcc_cnorm

length(OpenAcc_cnorm.NA.RM)
```

|Question| Mean  | SD    | 95% CI    | P agree | P disagree |
|:-----:|:-----:|:-----:|:---------:|:-------:|:---------:|
|OpenAcc_cnorm| 2.53 | 0.92 | 2.42, 2.65 | 0.13 | 0.48 |

### Norms in Practice 1

``` {r practices 1}

mean(frames$Practices_1, na.rm = TRUE)

sd(frames$Practices_1, na.rm = TRUE)

t.test(frames$Practices_1)

```

### Norms in Practice 2

``` {r practices 2}

mean(frames$Practices_2, na.rm = TRUE)

sd(frames$Practices_2, na.rm = TRUE)

t.test(frames$Practices_2)

```

### Norms in Practice 3

``` {r practices 3}

mean(frames$Practices_3, na.rm = TRUE)

sd(frames$Practices_3, na.rm = TRUE)

t.test(frames$Practices_3)

```

### Norms in Practice 4

``` {r practices 4}

mean(frames$Practices_4, na.rm = TRUE)

sd(frames$Practices_4, na.rm = TRUE)

t.test(frames$Practices_4)

```

### Norms in Practice 5

``` {r practices 5}

mean(frames$Practices_5, na.rm = TRUE)

sd(frames$Practices_5, na.rm = TRUE)

t.test(frames$Practices_5)

```

### Norms in Practice 6

``` {r practices 6}

mean(frames$Practices_6, na.rm = TRUE)

sd(frames$Practices_6, na.rm = TRUE)

t.test(frames$Practices_6)

```

### Norms in Practice 7

``` {r practices 7}

mean(frames$Practices_7, na.rm = TRUE)

sd(frames$Practices_7, na.rm = TRUE)

t.test(frames$Practices_7)

```

### Norms in Practice 8

``` {r practices 8}

mean(frames$Practices_8, na.rm = TRUE)

sd(frames$Practices_8, na.rm = TRUE)

t.test(frames$Practices_8)

```

### Norms in Practice 9

``` {r practices 9}

mean(frames$Practices_9, na.rm = TRUE)

sd(frames$Practices_9, na.rm = TRUE)

t.test(frames$Practices_9)

```

### Norms in Practice 10

``` {r practices 10}

mean(frames$Practices_10, na.rm = TRUE)

sd(frames$Practices_10, na.rm = TRUE)

t.test(frames$Practices_10)

```

### Bivariate Analyses from Preregistration.

```{r correlation between critcal norm and counter norm}
cor.test(frames$critical_norm, frames$critical_cnorm)

cor(frames$critical_norm, frames$critical_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between Preregistration norm and counter norm}
cor.test(frames$Prereg_norm, frames$Prereg_cnorm)

cor(frames$Prereg_norm, frames$Prereg_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between Regreport norm and counter norm}
cor.test(frames$RegReport_norm, frames$RegReport_cnorm)

cor(frames$RegReport_norm, frames$RegReport_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between P hacking norm and counter norm}

cor.test(frames$phack_norm, frames$phack_cnorm)

cor(frames$phack_norm, frames$phack_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between HARK norm and counter norm}
cor.test(frames$HARK_norm, frames$HARK_cnorm)

cor(frames$HARK_norm, frames$HARK_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between InfoForRep norm and counter norm}
cor.test(frames$InfoForRep_norm, frames$InfoForRep_cnorm)

cor(frames$InfoForRep_norm, frames$InfoForRep_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between PrePrint norm and counter norm}
cor.test(frames$Preprint_norm, frames$Preprint_cnorm)

cor(frames$Preprint_norm, frames$Preprint_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between Open Materials norm and counter norm}
cor.test(frames$OpenMaterials_norm, frames$OpenMaterials_cnorm)

cor(frames$OpenMaterials_norm, frames$OpenMaterials_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between Open Data norm and counter norm}
cor.test(frames$OpenData_norm, frames$OpenData_cnorm)

cor(frames$OpenData_norm, frames$OpenData_cnorm, use = "complete.obs", method = "pearson")

```

```{r correlation between Open Acc norm and counter norm}
cor.test(frames$OpenAcc_norm, frames$OpenAcc_cnorm)

cor(frames$OpenAcc_norm, frames$OpenAcc_cnorm, use = "complete.obs", method = "pearson")

```

### Difference in means between responses to norm and counter-norm, and 95% CI

```{r t test critical}

t.test(frames$critical_norm, frames$critical_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test prereg norm}

t.test(frames$Prereg_norm, frames$Prereg_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test Reg Report}

t.test(frames$RegReport_norm, frames$RegReport_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test p hack}

t.test(frames$phack_norm, frames$phack_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test HARKING}

t.test(frames$HARK_norm, frames$HARK_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test InfoForRep}

t.test(frames$InfoForRep_norm, frames$InfoForRep_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test Preprint}

t.test(frames$Preprint_norm, frames$Preprint_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test OpenMaterials}

t.test(frames$OpenMaterials_norm, frames$OpenMaterials_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test Open Data}

t.test(frames$OpenData_norm, frames$OpenData_cnorm, paired = TRUE, alternative = "two.sided")

```

```{r t test OpenAcc}

t.test(frames$OpenAcc_norm, frames$OpenAcc_cnorm, paired = TRUE, alternative = "two.sided")

```

### 2020-12-22 preprocessing/pre_students.R
add a preprocessing file

@@ -1,0 +1,10 @@
+# Preprocessing the data for the incoming students project
+
+library(tidyverse)
+library(here)
+
+# load data
+
+df <- read.csv(here::here("survey", "data", "open_science.csv"))
+
+

### 2020-12-22 preprocessing/pre_students.R
add survey file & start preprocessing

@@ -1,10 +1,41 @@
 # Preprocessing the data for the incoming students project
 
+##### LIBRARY #####
+
 library(tidyverse)
 library(here)
 
-# load data
 
-df <- read.csv(here::here("survey", "data", "open_science.csv"))
+####### FUNCTIONS ############
+# from Mathew Ling's Misinformation repo on Github
+
+# modify Mathew Ling's 'read_qualtrics' function to remove 'janitor_names'
+
+read_qualtrics <- function(file, legacy = TRUE) {
+  a <- readr::read_csv(file)
+  if (legacy == FALSE) {
+    a <- a[3:nrow(a), ]
+  } else {
+    a <- a[2:nrow(a), ]
+  }
+  a %>% readr::type_convert(trim_ws = TRUE)
+}
+
+# Mathew Ling's 'meta_rename' function
+
+meta_rename <-  function(df, metadata, old, new) {
+
+  keys   <- metadata[[deparse(substitute(old))]]
+  values <- metadata[[deparse(substitute(new))]]
+  rename_at(df, vars(keys), ~ values)
+}
+
+##### LOAD DATA #####
+
+df <- read.csv(here::here("survey", "data", "open_science.csv")) %>%
+  select (-c(StartDate, EndDate, Status, RecordedDate, DistributionChannel,
+             UserLanguage, Consent))
+
+
 
 

### 2020-12-22 preprocessing/pre_students.R
remove old files & update preprocessing

@@ -32,9 +32,11 @@ meta_rename <-  function(df, metadata, old, new) {
 
 ##### LOAD DATA #####
 
-df <- read.csv(here::here("survey", "data", "open_science.csv")) %>%
-  select (-c(StartDate, EndDate, Status, RecordedDate, DistributionChannel,
-             UserLanguage, Consent))
+df <- here::here("survey", "data", "raw_data.csv") %>%
+  read_qualtrics()
+
+df <- df %>%
+  select (-c(V1:Consent))
 
 
 

### 2020-12-22 analysis/Manuscript.Rmd
Adding manuscript Rmarkdown file with accompanying .bib

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_pdf: default
  papaja::apa6_word: default
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.
abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  One or two sentences to put the results into a more **general context**.
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  <!-- https://tinyurl.com/ybremelq -->
keywords: open science, psychology, teaching, reproducibility, replication
wordcount: X
bibliography: Matt_Zotero_Library.bib
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
---
<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
-->

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
<!--Intro below is very rough, just making sure everything works here in markdown really.-->

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings. For example, in an attempt to replicate 100 published psychological studies, only 38% were adjudged to have replicated the original result, and the average effect size was half that in the original studies [@opensciencecollaborationEstimatingReproducibilityPsychological2015a].

These apparent problems with replicability led to speculation regarding its causes, and a variety of potential solutions being proferred. Some of these potential solutions include more frequently conducting and publishing replication studies [see @brandtReplicationRecipeWhat2014], more transparent reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018]. In some cases changes to practices have been drastic and widespread: For example, the practice of accepting *Registered Reports* (wherein peer review and in principle acceptance for publication happens *prior* to data collection) was first proposed in 2012 (history details at : 10.31222/osf.io/43298) and is already offered by more than 250 journals (https://osf.io/rr/).

Many of these recent changes have links to the classic *Mertonian* norms of science. For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods. Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility  corresponds to the Mertonian norm of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.

<!--In fact I think our items may have been designed to correspond to specific Mertonian norms and counternorms - we should describe how this works when we come to writing Method > Measures.-->

These rapid changes lead to an important challenging: Training psychology students to understand and apply methodological practices which are rapidly evolving. Training in methodological practices is obviously crucial for graduate students who will apply psychological research methods themselves, but it is also important for early undergraduate students. Only by understanding contemporary methodological practices - and problems with methodological practices in psychology - can they become informed and critical consumers of knowledge about psychology.

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2020-12-22 analysis/Manuscript.tex
Adding manuscript Rmarkdown file with accompanying .bib

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,mask,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={What do incoming university students believe about open science practices in psychology?},
  pdfauthor={Jennifer L. Beaudry1, Michael C. Philipp2, \& Matt N. Williams2},
  pdflang={en-EN},
  pdfkeywords={open science, psychology, teaching, reproducibility, replication},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Psychology students' beliefs about open science}
\keywords{open science, psychology, teaching, reproducibility, replication\newline\indent Word count: X}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{What do incoming university students believe about open science practices in psychology?}
\author{Jennifer L. Beaudry\textsuperscript{1}, Michael C. Philipp\textsuperscript{2}, \& Matt N. Williams\textsuperscript{2}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
Enter author note here.

The authors made the following contributions. Jennifer L. Beaudry: ; Michael C. Philipp: ; Matt N. Williams: .

Correspondence concerning this article should be addressed to Jennifer L. Beaudry, Postal address. E-mail: \href{mailto:jbeaudry@swin.edu.au}{\nolinkurl{jbeaudry@swin.edu.au}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Swinburne University of Technology\\\textsuperscript{2} Massey University}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
One or two sentences to put the results into a more \textbf{general context}.
Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

The last decade has seen unprecedented change in methodological and reporting practices in psychology. These changes were partly precipitated by what is popularly known as the \enquote{replication crisis}: The discovery that close replications of published psychological studies are often unable to replicate the original findings. For example, in an attempt to replicate 100 published psychological studies, only 38\% were adjudged to have replicated the original result, and the average effect size was half that in the original studies (Open Science Collaboration, 2015).

These apparent problems with replicability led to speculation regarding its causes, and a variety of potential solutions being proferred. Some of these potential solutions include more frequently conducting and publishing replication studies (see Brandt et al., 2014), more transparent reporting of methods and results (Simmons, Nelson, \& Simonsohn, 2012), open sharing of data (see Meyer, 2018), and preregistration of data collection and analysis plans (Nosek, Ebersole, DeHaven, \& Mellor, 2018).

\hypertarget{methods}{%
\section{Methods}\label{methods}}

We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R (Version 4.0.3; {\textbf{???}}) and the R-package \emph{papaja} (Version 0.1.0.9997; {\textbf{???}}) for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-brandtReplicationRecipeWhat2014}{}%
Brandt, M. J., IJzerman, H., Dijksterhuis, A., Farach, F. J., Geller, J., Giner-Sorolla, R., \ldots{} van 't Veer, A. (2014). The replication recipe: What makes for a convincing replication? \emph{Journal of Experimental Social Psychology}, \emph{50}, 217--224. \url{https://doi.org/10.1016/j.jesp.2013.10.005}

\leavevmode\hypertarget{ref-meyerPracticalTipsEthical2018}{}%
Meyer, M. N. (2018). Practical tips for ethical data sharing. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 131--144. \url{https://doi.org/10.1177/2515245917747656}

\leavevmode\hypertarget{ref-nosekPreregistrationRevolution2018}{}%
Nosek, B. A., Ebersole, C. R., DeHaven, A. C., \& Mellor, D. T. (2018). The preregistration revolution. \emph{Proceedings of the National Academy of Sciences}, \emph{115}(11), 2600--2606. \url{https://doi.org/10.1073/pnas.1708274114}

\leavevmode\hypertarget{ref-opensciencecollaborationEstimatingReproducibilityPsychological2015a}{}%
Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}

\leavevmode\hypertarget{ref-simmons21WordSolution2012}{}%
Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 word solution} (SSRN Scholarly Paper No. ID 2160588). Rochester, NY: Social Science Research Network.

\endgroup

\end{document}

### 2021-01-12 analysis/Manuscript.Rmd
Revising intro

@@
 output:
+  papaja::apa6_word: default
   papaja::apa6_pdf: default
-  papaja::apa6_word: default
 authornote: |
@@
 The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions.
+To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
+However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
+This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
+papaja and its many dependencies.
 -->
@@
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
-These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings.
-For example, in an attempt to replicate 100 published psychological studies, only 38% were adjudged to have replicated the original result, and the average effect size was half that in the original studies [@opensciencecollaborationEstimatingReproducibilityPsychological2015a].
+These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
+For example, in an attempt to replicate 100 published psychological studies, only 38% were adjudged to have replicated the original result, and the average effect size was half that in the original studies [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
 
@@
 Some of these potential solutions include more frequently conducting and publishing replication studies [see @brandtReplicationRecipeWhat2014], more transparent reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-In some cases changes to practices have been drastic and widespread: For example, the practice of accepting *Registered Reports* (wherein peer review and in principle acceptance for publication happens *prior* to data collection) was first proposed in 2012 (history details at : 10.31222/osf.io/43298) and is already offered by more than 250 journals (https://osf.io/rr/).
+In some cases changes to practices have been drastic and widespread: For example, the practice of accepting *Registered Reports* (wherein peer review and in principle acceptance for publication happens *prior* to data collection) was first proposed in 2012 [see @chambersRegisteredReportsPresent2020 for a history] and is already offered by more than 250 journals (https://osf.io/rr/).
+
+These rapid changes present a pedagogical challenge.
+Traditionally, textbooks and other instructional materials for undergraduate students - especially at the first-year level - emphasise the most fundamental and "well-established" studies and findings in a given discipline.
+Keeping textbooks and other instructional materials "up to date" is currently very difficult in psychology, when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
+Exacerbating this challenge is the presence of dilemmas in approach.
+
+The first of these open questions is: Which methods are most effective for teaching students about replicability and open science?
+This question was addressed by @chopikHowWhetherTeach2018, who tested  a one-hour lecture for undergraduate students pertaining to the replication crisis and methods for increasing reproducibility.
+Using a pre-post survey, they found that students seemed to comprehend the key messages in this lecture.
+
+The second open question relates to the fact that when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than just relying on intuition or anecdote or authority).
+Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
+@chopikHowWhetherTeach2018 found that students trusted the results of studies by psychologists less after their lecture on the replication crisis, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
 
@@
 
-These rapid changes lead to an important challenging: Training psychology students to understand and apply methodological practices which are rapidly evolving.
-Training in methodological practices is obviously crucial for graduate students who will apply psychological research methods themselves, but it is also important for early undergraduate students.
+These rapid changes lead to an important challenge: Training psychology students to understand and apply methodological practices which are rapidly evolving.
+Training in methodological practices is obviously crucial for graduate students who will apply psychological research methods themselves, such that the next generation of researchers can produce research which is more replicable than that of the last.
+But this training is also important for early undergraduate students.
 Only by understanding contemporary methodological practices - and problems with methodological practices in psychology - can they become informed and critical consumers of knowledge about psychology.
+
+Recent research has therefore been dedicated to the question of how undergraduate students might most effectively be taught about the replication crisis (and related open science reforms in psychology) [@chopikHowWhetherTeach2018].
+However, there are several reasons why it might be unwise to assume a simple knowledge deficit situation, where students lack knowledge about the topic and the teacher's only role is to find ways to fill in this knowledge.
+
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues already (and perhaps even more knowledge than some of their teachers).
+Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
+
+Second, when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than just relying on intuition or anecdote or authority).
+Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
+It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students, rather than simply assuming that the correct degree of calibration is always to prompt students to trust psychology research *less* than they already do.
+
+Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice.
+In other words, their naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than traditional practices.
+It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing "naive" assumptions.
+In fact, although beyond the scope of this article, it may possibly be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
+
+These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
+In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses and learning about psychological research in any given year dwarfs the number of academics working in psychology.
+As such, the preferences of these students with respect to reproducibility and open science practices are intrinsically important for psychological researchers to know about.
+If, for example, undergraduate psychology students universally have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce would surely have some bearing on our choices in relation to sharing of manuscripts.
+This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
+In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
+As such, their preferences are intrinsically important.
+
+For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
+Our survey encompassed norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is).
+In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices.
+
+## Aims
 

### 2021-01-12 analysis/Manuscript.tex
Revising intro

@@
 These changes were partly precipitated by what is popularly known as the \enquote{replication crisis}: The discovery that close replications of published psychological studies are often unable to replicate the original findings.
-For example, in an attempt to replicate 100 published psychological studies, only 38\% were adjudged to have replicated the original result, and the average effect size was half that in the original studies (Open Science Collaboration, 2015).
+For example, in an attempt to replicate 100 published psychological studies, only 38\% were adjudged to have replicated the original result, and the average effect size was half that in the original studies ({\textbf{???}}).
 
@@
 Some of these potential solutions include more frequently conducting and publishing replication studies (see Brandt et al., 2014), more transparent reporting of methods and results (Simmons, Nelson, \& Simonsohn, 2012), open sharing of data (see Meyer, 2018), and preregistration of data collection and analysis plans (Nosek, Ebersole, DeHaven, \& Mellor, 2018).
+In some cases changes to practices have been drastic and widespread: For example, the practice of accepting \emph{Registered Reports} (wherein peer review and in principle acceptance for publication happens \emph{prior} to data collection) was first proposed in 2012 (history details at : 10.31222/osf.io/43298) and is already offered by more than 250 journals (\url{https://osf.io/rr/}).
+
+These rapid changes present a pedagogical challenge.
+Traditionally, textbooks and other instructional materials for undergraduate students - especially at the first-year level - emphasise the most fundamental and \enquote{well-established} studies and findings in a given discipline.
+Keeping textbooks and other instructional materials \enquote{up to date} is currently very difficult in psychology, when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
+Exacerbating this challenge is the presence of dilemmas in approach.
+
+The first of these open questions is: Which methods are most effective for teaching students about replicability and open science?
+This question was addressed by Chopik, Bremner, Defever, and Keller (2018), who tested a one-hour lecture for undergraduate students pertaining to the replication crisis and methods for increasing reproducibility.
+Using a pre-post survey, they found that students seemed to comprehend the key messages in this lecture.
+
+The second open question relates to the fact that when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than just relying on intuition or anecdote or authority).
+Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable \emph{at all}, leaving them to favour even less credible alternative sources of knowledge?
+Chopik et al.
+(2018) found that students trusted the results of studies by psychologists less after their lecture on the replication crisis, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
+
+Many of these recent changes have links to the classic \emph{Mertonian} norms of science.
+For example, the practice of sharing open source software directly corresponds to the Mertonian norm of \emph{communism}: Scientists should have common ownership of scientific goods.
+Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the Mertonian norm of \emph{organised skepticism}: Scientific claims should be subjected to critical scrutiny.
+
+These rapid changes lead to an important challenge: Training psychology students to understand and apply methodological practices which are rapidly evolving.
+Training in methodological practices is obviously crucial for graduate students who will apply psychological research methods themselves, such that the next generation of researchers can produce research which is more replicable than that of the last.
+But this training is also important for early undergraduate students.
+Only by understanding contemporary methodological practices - and problems with methodological practices in psychology - can they become informed and critical consumers of knowledge about psychology.
+
+Recent research has therefore been dedicated to the question of how undergraduate students might most effectively be taught about the replication crisis (and related open science reforms in psychology) (Chopik et al., 2018).
+However, there are several reasons why it might be unwise to assume a simple knowledge deficit situation, where students lack knowledge about the topic and the teacher's only role is to find ways to fill in this knowledge.
+
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues already (and perhaps even more knowledge than some of their teachers).
+Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
+
+Second, when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than just relying on intuition or anecdote or authority).
+Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable \emph{at all}, leaving them to favour even less credible alternative sources of knowledge?
+It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students, rather than simply assuming that the correct degree of calibration is always to prompt students to trust psychology research \emph{less} than they already do.
+
+Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not \emph{already} standard practice.
+In other words, their naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than traditional practices.
+It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing \enquote{naive} assumptions.
+In fact, although beyond the scope of this article, it may possibly be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
+
+These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
+In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses and learning about psychological research in any given year dwarfs the number of academics working in psychology.
+As such, the preferences of these students with respect to reproducibility and open science practices are intrinsically important for psychological researchers to know about.
+If, for example, undergraduate psychology students universally have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce would surely have some bearing on our choices in relation to sharing of manuscripts.
+This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
+In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
+As such, their preferences are intrinsically important.
+
+For these reasons
+
+\hypertarget{aims}{%
+\subsection{Aims}\label{aims}}
 
@@
 
-We used R (Version 4.0.3; {\textbf{???}}) and the R-package \emph{papaja} (Version 0.1.0.9997; {\textbf{???}}) for all our analyses.
+We used R (Version 4.0.1; {\textbf{???}}) and the R-package \emph{papaja} (Version 0.1.0.9997; {\textbf{???}}) for all our analyses.
 
@@
 
+\leavevmode\hypertarget{ref-chopikHowWhetherTeach2018}{}%
+Chopik, W.
+J., Bremner, R.
+H., Defever, A.
+M., \& Keller, V.
+N.
+(2018).
+How (and whether) to teach undergraduates about the replication crisis in psychological science.
+\emph{Teaching of Psychology}, \emph{45}(2), 158--163.
+\url{https://doi.org/10.1177/0098628318762900}
+
 \leavevmode\hypertarget{ref-meyerPracticalTipsEthical2018}{}%
@@
 
-\leavevmode\hypertarget{ref-opensciencecollaborationEstimatingReproducibilityPsychological2015a}{}%
-Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}
-
 \leavevmode\hypertarget{ref-simmons21WordSolution2012}{}%

### 2021-01-12 analysis/Manuscript.Rmd
More intro revisions

@@
 output:
+  papaja::apa6_pdf: default
   papaja::apa6_word: default
-  papaja::apa6_pdf: default
 authornote: |
@@
 
-These rapid changes present a pedagogical challenge.
-Traditionally, textbooks and other instructional materials for undergraduate students - especially at the first-year level - emphasise the most fundamental and "well-established" studies and findings in a given discipline.
-Keeping textbooks and other instructional materials "up to date" is currently very difficult in psychology, when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
-Exacerbating this challenge is the presence of dilemmas in approach.
-
-The first of these open questions is: Which methods are most effective for teaching students about replicability and open science?
-This question was addressed by @chopikHowWhetherTeach2018, who tested  a one-hour lecture for undergraduate students pertaining to the replication crisis and methods for increasing reproducibility.
-Using a pre-post survey, they found that students seemed to comprehend the key messages in this lecture.
-
-The second open question relates to the fact that when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than just relying on intuition or anecdote or authority).
-Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
-@chopikHowWhetherTeach2018 found that students trusted the results of studies by psychologists less after their lecture on the replication crisis, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
-
-Many of these recent changes have links to the classic *Mertonian* norms of science.
+Many of these recent changes have links to the classic *Mertonian* norms of science [@mertonSociologyScienceTheoretical1973].
 For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.
 Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the Mertonian norm of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
+Even the practice of preregistration has a connection to the norm of *disinterestedness*, in that a preregistration acts as a social control reducing the potential impact of personal investment in a particular outcome from affecting the choice of results reported in a given study.
+In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.
 
-<!--In fact I think our items may have been designed to correspond to specific Mertonian norms and counternorms - we should describe how this works when we come to writing Method > Measures.-->
+Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
+Keeping textbooks and other instructional materials "up to date" is obviously difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, such that the next generation of researchers can produce research which is more replicable than that of the last.
+Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for these students to become informed and critical consumers of knowledge about psychology.
+However, the question of how best to provide this understanding is by no means trivial.
+Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where students lack knowledge about reproducibility and open science practices and the teacher's only role is to communicate this knowledge.
 
-These rapid changes lead to an important challenge: Training psychology students to understand and apply methodological practices which are rapidly evolving.
-Training in methodological practices is obviously crucial for graduate students who will apply psychological research methods themselves, such that the next generation of researchers can produce research which is more replicable than that of the last.
-But this training is also important for early undergraduate students.
-Only by understanding contemporary methodological practices - and problems with methodological practices in psychology - can they become informed and critical consumers of knowledge about psychology.
-
-Recent research has therefore been dedicated to the question of how undergraduate students might most effectively be taught about the replication crisis (and related open science reforms in psychology) [@chopikHowWhetherTeach2018].
-However, there are several reasons why it might be unwise to assume a simple knowledge deficit situation, where students lack knowledge about the topic and the teacher's only role is to find ways to fill in this knowledge.
-
-First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues already (and perhaps even more knowledge than some of their teachers).
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues already.
 Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
 
-Second, when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than just relying on intuition or anecdote or authority).
+Second, when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
 Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
 It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students, rather than simply assuming that the correct degree of calibration is always to prompt students to trust psychology research *less* than they already do.
+In their examination of the usefulness of a one-hour lecture about the replication crisis, @chopikHowWhetherTeach2018 found that undergraduate students trusted the results of studies by psychologists less after the lecture than they did before it, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
 
@@
 In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses and learning about psychological research in any given year dwarfs the number of academics working in psychology.
-As such, the preferences of these students with respect to reproducibility and open science practices are intrinsically important for psychological researchers to know about.
-If, for example, undergraduate psychology students universally have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce would surely have some bearing on our choices in relation to sharing of manuscripts.
+As such, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
+If, for example, undergraduate psychology students have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce should have some bearing on our choices in relation to sharing of manuscripts.
 This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
 In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
-As such, their preferences are intrinsically important.
 
@@
 In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices.
-
-## Aims
 

### 2021-01-12 analysis/Manuscript.tex
More intro revisions

--- 2020-12-22 analysis/Manuscript.tex
@@
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
-These changes were partly precipitated by what is popularly known as the \enquote{replication crisis}: The discovery that close replications of published psychological studies are often unable to replicate the original findings.
+These changes were partly precipitated by what is popularly known as the \enquote{replication crisis}: The discovery that close replications of published psychological studies are often unable to replicate the original findings(Klein et al., 2014, 2018).
 For example, in an attempt to replicate 100 published psychological studies, only 38\% were adjudged to have replicated the original result, and the average effect size was half that in the original studies (Open Science Collaboration, 2015).
@@
 Some of these potential solutions include more frequently conducting and publishing replication studies (see Brandt et al., 2014), more transparent reporting of methods and results (Simmons, Nelson, \& Simonsohn, 2012), open sharing of data (see Meyer, 2018), and preregistration of data collection and analysis plans (Nosek, Ebersole, DeHaven, \& Mellor, 2018).
+In some cases changes to practices have been drastic and widespread: For example, the practice of accepting \emph{Registered Reports} (wherein peer review and in principle acceptance for publication happens \emph{prior} to data collection) was first proposed in 2012 (see Chambers \& Tzavella, 2020 for a history) and is already offered by more than 250 journals (\url{https://osf.io/rr/}).
+
+Many of these recent changes have links to the classic \emph{Mertonian} norms of science (Merton, 1973).
+For example, the practice of sharing open source software directly corresponds to the Mertonian norm of \emph{communism}: Scientists should have common ownership of scientific goods.
+Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the Mertonian norm of \emph{organised skepticism}: Scientific claims should be subjected to critical scrutiny.
+Even the practice of preregistration has a connection to the norm of \emph{disinterestedness}, in that a preregistration acts as a social control reducing the potential impact of personal investment in a particular outcome from affecting the choice of results reported in a given study.
+In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.
+
+Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
+Keeping textbooks and other instructional materials \enquote{up to date} is obviously difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, such that the next generation of researchers can produce research which is more replicable than that of the last.
+Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for these students to become informed and critical consumers of knowledge about psychology.
+However, the question of how best to provide this understanding is by no means trivial.
+Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where students lack knowledge about reproducibility and open science practices and the teacher's only role is to communicate this knowledge.
+
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues already.
+Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
+
+Second, when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
+Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable \emph{at all}, leaving them to favour even less credible alternative sources of knowledge?
+It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students, rather than simply assuming that the correct degree of calibration is always to prompt students to trust psychology research \emph{less} than they already do.
+In their examination of the usefulness of a one-hour lecture about the replication crisis, Chopik, Bremner, Defever, and Keller (2018) found that undergraduate students trusted the results of studies by psychologists less after the lecture than they did before it, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
+
+Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not \emph{already} standard practice.
+In other words, their naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than traditional practices.
+It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing \enquote{naive} assumptions.
+In fact, although beyond the scope of this article, it may possibly be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
+
+These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
+In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses and learning about psychological research in any given year dwarfs the number of academics working in psychology.
+As such, the \emph{preferences} of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
+If, for example, undergraduate psychology students have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce should have some bearing on our choices in relation to sharing of manuscripts.
+This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
+In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
+
+For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
+Our survey encompassed norms (how students felt research \emph{should} be conducted), norms in practice (how students believe psychological research \emph{is} conducted) and replicability (how replicable students believe psychological research is).
+In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices.
 
@@
 
+\leavevmode\hypertarget{ref-chambersRegisteredReportsPresent2020}{}%
+Chambers, C., \& Tzavella, L. (2020). Registered reports: Past, present and future. \url{https://doi.org/10.31222/osf.io/43298}
+
+\leavevmode\hypertarget{ref-chopikHowWhetherTeach2018}{}%
+Chopik, W.
+J., Bremner, R.
+H., Defever, A.
+M., \& Keller, V.
+N.
+(2018).
+How (and whether) to teach undergraduates about the replication crisis in psychological science.
+\emph{Teaching of Psychology}, \emph{45}(2), 158--163.
+\url{https://doi.org/10.1177/0098628318762900}
+
+\leavevmode\hypertarget{ref-kleinInvestigatingVariationReplicability2014}{}%
+Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams Jr., R.
+B., Bahník, Š., Bernstein, M.
+J., \ldots{} Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A ``many labs'' replication project.
+\emph{Social Psychology}, \emph{45}(3), 142--152.
+\url{https://doi.org/10.1027/1864-9335/a000178}
+
+\leavevmode\hypertarget{ref-kleinManyLabsInvestigating2018}{}%
+Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams, R.
+B., Alper, S., \ldots{} Nosek, B.
+A.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
+\url{https://doi.org/10.1177/2515245918810225}
+
+\leavevmode\hypertarget{ref-mertonSociologyScienceTheoretical1973}{}%
+Merton, R. K. (1973). \emph{The sociology of science : Theoretical and empirical investigations}. Chicago : University of Chicago Press.
+
 \leavevmode\hypertarget{ref-meyerPracticalTipsEthical2018}{}%
@@
 
-\leavevmode\hypertarget{ref-opensciencecollaborationEstimatingReproducibilityPsychological2015a}{}%
+\leavevmode\hypertarget{ref-opensciencecollaborationEstimatingReproducibilityPsychological2015}{}%
 Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}

### 2021-01-12 analysis/Manuscript.Rmd
Removing a comment

@@
 ```
-<!--Intro below is very rough, just making sure everything works here in markdown really.-->
 

### 2021-02-08 preprocessing/students_codebook.Rmd

---
title: "Codebook"
author: "Jennifer Beaudry"
date: "20/01/2021"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: true    
  # pdf_document:
  #   toc: yes
  #   toc_depth: 4
  #   latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  warning = FALSE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE, # do not interrupt codebook generation in case of errors,
                # usually makes debugging easier, and sometimes half a codebook
                # is better than none
  echo = FALSE  # don't show the R code
)
ggplot2::theme_set(ggplot2::theme_bw())
pander::panderOptions("table.split.table", Inf)
```

```{r library}
library(here)
library(tidyverse)
library(codebook)
```

```{r data}

codebook_data <- rio::import(here::here("data", "students_processed.csv"))

# Breadcrumbs: will need to revise this so it imports the cleaned data that I worked with
```

```{r codebook}

codebook_data <- detect_missing(codebook_data,
    only_labelled = TRUE, # only labelled values are autodetected as
                                   # missing
    negative_values_are_missing = FALSE, # negative values are NOT missing values
    ninety_nine_problems = TRUE,   # 99/999 are missing values, if they
                                   # are more than 5 MAD from the median
    )

codebook(codebook_data, 
         metadata_table = TRUE,
         metadata_json = TRUE, 
         survey_overview = FALSE)

# [[breadcrubms: preprocess the data first  & import with the qualtrics reader 
# & then import it into codebook. Use the metadata to change the #labels. 
# Figure out the data labels that we're changing within the raw data itself.]] 
# all done
```

### 2021-02-08 preprocessing/pre_students.R
Delete pre_students.R

@@ -1,50 +1,0 @@
-# Preprocessing the data for the incoming students project
-
-##### LIBRARY #####
-
-library(tidyverse)
-library(here)
-
-
-####### FUNCTIONS ############
-# from Mathew Ling's Misinformation repo on Github
-
-# modify Mathew Ling's 'read_qualtrics' function to remove 'janitor_names'
-
-read_qualtrics <- function(file, legacy = TRUE) {
-  a <- readr::read_csv(file)
-  if (legacy == FALSE) {
-    a <- a[3:nrow(a), ]
-  } else {
-    a <- a[2:nrow(a), ]
-  }
-  a %>% readr::type_convert(trim_ws = TRUE)
-}
-
-# Mathew Ling's 'meta_rename' function
-
-meta_rename <-  function(df, metadata, old, new) {
-
-  keys   <- metadata[[deparse(substitute(old))]]
-  values <- metadata[[deparse(substitute(new))]]
-  rename_at(df, vars(keys), ~ values)
-}
-
-##### LOAD DATA #####
-
-df <- here::here("survey", "data", "raw_data.csv") %>%
-  read_qualtrics()
-
-df <- df %>%
-  mutate(id = 1:n()) %>%
-  select (-c(V1:Consent))
-
-
-# note re: eligibility
-# only those who say "1" are eligible
-
-df <- df %>%
-  filter(Eligibility %in% 1)
-
-
-

### 2021-02-09 analysis/Manuscript.Rmd
starting to import data

@@
 ```{r setup, include = FALSE}
-library("papaja")
+library(papaja)
+library(here)
+library(tidyverse)
+
 r_refs("r-references.bib")
@@
 knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+```
+
+```{r import data}
+
+#import the data. 
+df2 <- read.csv (here::here("data", "students_processed.csv"))
+# [[breadcrumbs: work on parsing the columns. It could be that I didn't need to 
+# write them as factors in the preprocessing]]
+df3 <- read.csv (here::here("data", "students_processed.csv"), 
+                 colClasses = c('numeric','factor','factor',
+                                rep('character', 3),
+                                rep('factor', 2), 'character', 
+                                rep('numeric', 35), rep('character', 3),
+                                rep('factor', 4), rep('character', 2),
+                                rep('factor', 21))
+                 )
+
+# # import the metadata [check if I need it for these analyses?]
+# metadata <- here::here("survey", "data", "os_metadata_raw_data.csv") %>% 
+#   read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
+#   filter(!is.na(OldVariable))
 ```
@@
 
+```{r eligibility}
+
+# I fell down a massive git hub hole, so I'll make progress on this tomorrow!
+
+```
+
 ## Participants
+
+```{r demographics}
+
+```
 

### 2021-02-09 preprocessing/preprocessing_students.R
update with slight changes

@@ -140,4 +140,4 @@ df <- df %>%
 # when done preprocessing, write the data to a new file
 # row.names gets rid of the first column from the dataframe.
 
-write.csv(df, here::here("data", "data_processed.csv"), row.names = FALSE)
+write.csv(df, here::here("data", "students_processed.csv"), row.names = FALSE)

### 2021-02-09 analysis/Manuscript.Rmd
update preprocessing & data import

@@
 
-#import the data. 
-df2 <- read.csv (here::here("data", "students_processed.csv"))
-# [[breadcrumbs: work on parsing the columns. It could be that I didn't need to 
-# write them as factors in the preprocessing]]
-df3 <- read.csv (here::here("data", "students_processed.csv"), 
-                 colClasses = c('numeric','factor','factor',
-                                rep('character', 3),
-                                rep('factor', 2), 'character', 
-                                rep('numeric', 35), rep('character', 3),
-                                rep('factor', 4), rep('character', 2),
-                                rep('factor', 21))
-                 )
+# import the data 
+df <- read.csv (here::here("data", "students_processed.csv"))
+
+# convert variables to factors as needed
+df$age <- as_factor(df$age)
+df$eligibility <- as_factor(df$eligibility)
+
+# convert factors to characters as needed
+df$university <- as.character(df$university)
+df$degree <- as.character(df$degree)
+df$major <- as.character(df$major)
+df$major <- as.character(df$major)
+df$uni_country <- as.character(df$uni_country)
+df$nationality <- as.character(df$nationality)
 
@@
 
+# note re: eligibility
+# only those who say "1" are eligible
+
+df$eligibility <- factor(df$eligibility)
+df$eligibility_lab <- factor(df$eligibility_lab)
+
+el <- df %>%
+  dplyr::count(eligibility_lab)
+
+# filter(eligibility %in% 1)
+
 ```

### 2021-02-09 preprocessing/preprocessing_students.R

@@ -59,7 +59,7 @@ metadata <- read_csv(here::here("data", "students_metadata_working_data.csv")) %
 
 df_num <- df_num %>%
   relocate(id) %>% # move the ID variable to the first column
-  select(-c(v1:consent)) %>%  # remove extraneous columns
+  select(-c(v1:consent,scenario_remind)) %>%  # remove extraneous columns
   select(-c(uni_country:nationality))  # remove Qualtrics-coded variables [use label dataset for these]
 
 df_lab <- df_lab %>%
@@ -93,46 +93,46 @@ df <- meta_rename(df, metadata, old = old_variable, new = new_variable)
 
 #### CONVERT VARIABLES INTO FACTORS ####
 
-df$age <- factor(df$age)
-df$age_lab <- factor(df$age_lab)
-df$eligibility <- factor(df$eligibility)
-df$eligibility_lab <- factor(df$eligibility_lab)
-df$high_school <- factor(df$high_school)
-df$high_school_lab <- factor(df$high_school_lab)
-df$psych_hs <- factor(df$psych_hs)
-df$psych_hs_lab <- factor(df$psych_hs_lab)
-df$first_gen_lab <- factor(df$first_gen_lab)
-df$critical_cnorm_lab <- factor(df$critical_cnorm_lab)
-df$critical_norm_lab <- factor(df$critical_norm_lab)
-df$prereg_norm_lab <- factor(df$prereg_norm_lab)
-df$prereg_cnorm_lab <- factor(df$prereg_cnorm_lab)
-df$reg_report_norm_lab <- factor(df$reg_report_norm_lab)
-df$reg_report_cnorm_lab <- factor(df$reg_report_cnorm_lab)
-df$phack_cnorm_lab <- factor(df$phack_cnorm_lab)
-df$phack_norm_lab <- factor(df$phack_norm_lab)
-df$hark_cnorm_lab <- factor(df$hark_cnorm_lab)
-df$hark_norm_lab <- factor(df$hark_norm_lab)
-df$info_for_rep_norm_lab <- factor(df$info_for_rep_norm_lab)
-df$info_for_rep_cnorm_lab <- factor(df$info_for_rep_cnorm_lab)
-df$preprint_norm_lab <- factor(df$preprint_norm_lab)
-df$preprint_cnorm_lab <- factor(df$preprint_cnorm_lab)
-df$open_materials_norm_lab <- factor(df$open_materials_norm_lab)
[…]

### 2021-02-09 analysis/Manuscript.Rmd
update preprocessing & data import

@@
 
-# I fell down a massive git hub hole, so I'll make progress on this tomorrow!
+# all participants
+n <- nrow(df)
 
@@
 # only those who say "1" are eligible
-
-df$eligibility <- factor(df$eligibility)
-df$eligibility_lab <- factor(df$eligibility_lab)
 
@@
 ## Participants
+
+Of those who started the survey (*n* = `r n`), `r el[5,2]` were eligible based on starting 
+their first unit of study in psychology at a university within the next month.
+
+<!-- [[ Breadcrumbs: work through the eligibility criteria from the prereg ]] -->
 

### 2021-02-10 analysis/Manuscript.Rmd
start on demographics

--- 2021-02-09 analysis/Manuscript.Rmd
@@
 df$major <- as.character(df$major)
-df$uni_country <- as.character(df$uni_country)
-df$nationality <- as.character(df$nationality)
+# df$uni_country <- as.character(df$uni_country)
+# df$nationality <- as.character(df$nationality) [i think these should be factors]
 
@@
 
-# I fell down a massive git hub hole, so I'll make progress on this tomorrow!
+# all participants
+n_all <- nrow(df)
 
@@
 
-df$eligibility <- factor(df$eligibility)
-df$eligibility_lab <- factor(df$eligibility_lab)
+age <- df %>%
+  dplyr::count(age_lab)
 
@@
 
+n <- el[5,2]
 # filter(eligibility %in% 1)
+
+```
+
+```{r demographics}
+
+# gender --> need to run through gendercoder
+# high school status
+# high school psyc 
+# country of university 
+# country of nationality
+# whether parents' attended uni
 
@@
 
-```{r demographics}
+Of those who started the survey (*n* = `r n_all`), we screened out participants who 
+were not eligible to participate based on our preregistration. Specifically, 
+we screened out people who were younger than 18 years of age (*n* = `r age[1,2]`). 
+We also screened out individuals who had already started a psychology unit at a
+university, regardless of whether they completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); 
+were not enrolled in a psychology unit at a university (*n* = `r el[2,2]`); or did 
+not answer this question (*n* = `r el[6,2]`). The remaining `r el[5,2]` participants
+were eligible based on starting their first unit of study in psychology at 
+a university within the next month. For those individuals who were screened out, 
+our Qualtrics program automatically directed them to the debriefing form.
+
+Of the remaining `r n` participants, most reported that they were
+18-24 years old (*n* = `r age[2,2]`), `r age [3,2]` 
+reported that they were 25-34 years old, `r age [4,2]` were 35-44 years old,
+`r age [5,2]` were 45-54 years old, `r age [6,2]` were 55-64 years old, and
+`r age [7,2]` were 65 years or older. A small number of participants did not 
+report their age(*n* = `r age [8,2]`).
+
+```{r qual responses}
+
+# once qual responses are coded, I will need to return here to 
+ # include details about which univrsity the participant is enrolled in
+ # name of qualification
+ # major
 

### 2021-02-10 preprocessing/preprocessing_students.R
update preprocessing to include qual responses

@@ -8,6 +8,7 @@
 
 library(tidyverse)
 library(here)
+library(tools)
 
 
 ####### FUNCTIONS ############
@@ -141,3 +142,48 @@ df <- df %>%
 # row.names gets rid of the first column from the dataframe.
 
 write.csv(df, here::here("data", "students_processed.csv"), row.names = FALSE)
+
+
+
+################### CODING QUALITATIVE RESPONSES #############
+
+# We will need to code their qualitative responses (university, degree,
+# major). To do so, for the eligible participants,
+# I am selecting those variables and exporting
+# them to a separate document.  [[breadcrumbs: rejoin later to the doc &
+# then write that data to the main data file.
+# Move this above when done preprocessing. ]]
+# row.names gets rid of the first column from the dataframe.
+
+qual <- df %>%
+  filter(eligibility %in% 1) %>%
+  select(c(id,university, degree, major))
+
+# force them to title case & then group those that are similar
+  # use the id number to count how many responses matched
+  # do this separately for uni, degree, and major
+qual_uni <- qual %>%
+  transmute(university = toTitleCase(university),id) %>%
+  group_by(university) %>%
+  summarise(n_distinct(id)) %>%
+  rename(`frequency` = `n_distinct(id)`)
+
+qual_deg <- qual %>%
+  transmute(degree = toTitleCase(degree),id) %>%
+  group_by(degree) %>%
+  summarise(n_distinct(id)) %>%
+  rename(`frequency` = `n_distinct(id)`)
+
+qual_maj <- qual %>%
+  transmute(major = toTitleCase(major),id) %>%
+  group_by(major) %>%
+  summarise(n_distinct(id)) %>%
+  rename(`frequency` = `n_distinct(id)`)
+
+# write each of them to csv files
+write.csv(qual_uni, here::here("preprocessing", "qual_responses_uni.csv"), row.names = FALSE)
+
+write.csv(qual_deg, here::here("preprocessing", "qual_responses_deg.csv"), row.names = FALSE)
+
+write.csv(qual_maj, here::here("preprocessing", "qual_responses_maj.csv"), row.names = FALSE)
+

### 2021-02-10 analysis/Manuscript.Rmd
add r-ref bib file

@@
 wordcount: X
-bibliography: Matt_Zotero_Library.bib
+bibliography: [Matt_Zotero_Library.bib,r-references.bib]
 floatsintext: yes

### 2021-02-10 analysis/Manuscript.Rmd
add notes about qual demographic variables

@@
  # name of qualification
- # major
+ # major [how many are majoring in psyc; NAs; will decide later?]
 

### 2021-02-10 analysis/Manuscript.Rmd
Updating manuscript based on group zoom sesh

--- 2021-02-10 analysis/Manuscript.Rmd
@@
 
+<!-- I need to update the main .bib file to be a synced copy of our group library, and then ensure all citations below are in that library (and that the keys match.) -->
+
 ```{r setup, include = FALSE}
@@
 For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.
-Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the Mertonian norm of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
-Even the practice of preregistration has a connection to the norm of *disinterestedness*, in that a preregistration acts as a social control reducing the potential impact of personal investment in a particular outcome from affecting the choice of results reported in a given study.
+Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
+Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
 In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.
@@
 Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
-Keeping textbooks and other instructional materials "up to date" is obviously difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
-Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, such that the next generation of researchers can produce research which is more replicable than that of the last.
+Keeping textbooks and other instructional materials up to date is  difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that the next generation of researchers can produce research which is more replicable than that of the last.
 Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for these students to become informed and critical consumers of knowledge about psychology.
-However, the question of how best to provide this understanding is by no means trivial.
+However, the question of how best to provide this understanding is by no means trivial to answer.
 Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where students lack knowledge about reproducibility and open science practices and the teacher's only role is to communicate this knowledge.
 
-First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues already.
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
 Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
 
-Second, when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
+Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
 Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
-It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students, rather than simply assuming that the correct degree of calibration is always to prompt students to trust psychology research *less* than they already do.
+It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students.
 In their examination of the usefulness of a one-hour lecture about the replication crisis, @chopikHowWhetherTeach2018 found that undergraduate students trusted the results of studies by psychologists less after the lecture than they did before it, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
@@
 Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice.
-In other words, their naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than traditional practices.
+In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices.
+Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
+Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
+In relation to open science practices more specifically, a survey of senior French scientists [@schopfelReadyFutureSurvey2016] found that around one in ten were un
+
 It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing "naive" assumptions.
-In fact, although beyond the scope of this article, it may possibly be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
+In fact, although beyond the scope of this article, it may even be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
+
+<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) -->
 
@@
 In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
+
+<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? -->
 

### 2021-02-10 analysis/Manuscript.Rmd
removed a half-written sentence

@@
 Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
-In relation to open science practices more specifically, a survey of senior French scientists [@schopfelReadyFutureSurvey2016] found that around one in ten were un
-
 It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing "naive" assumptions.
@@
 
-<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) -->
+<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) 
+Also maybe add more about what we know about academics' endorsement of open science norms.
+-->
 

### 2021-02-10 analysis/Manuscript.Rmd
Update Manuscript.Rmd

@@
 
+<!--MP ➔ The paragraph below is an attempt to segue to the aim of our study before getting into the lit review – I'm always of fan of making the general aim of the study clear by the end of the first paragraph.
+I've summarised the sentiment of the original first two paragraphs a bit (and struck out tangential sentences).
+I'd suggest this could make the first paragraph of the paper – highlighting the the research context and the gap that is driving our study-->
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
 These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
-For example, in an attempt to replicate 100 published psychological studies, only 38% were adjudged to have replicated the original result, and the average effect size was half that in the original studies [@opensciencecollaborationEstimatingReproducibilityPsychological2015].
-
-These apparent problems with replicability led to speculation regarding its causes, and a variety of potential solutions being proferred.
-Some of these potential solutions include more frequently conducting and publishing replication studies [see @brandtReplicationRecipeWhat2014], more transparent reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-In some cases changes to practices have been drastic and widespread: For example, the practice of accepting *Registered Reports* (wherein peer review and in principle acceptance for publication happens *prior* to data collection) was first proposed in 2012 [see @chambersRegisteredReportsPresent2020 for a history] and is already offered by more than 250 journals (https://osf.io/rr/).
+These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
+Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices (e.g., Baker, 2016; Chambers & Morey, 2017@[https://osf.io/dmfke/], Harris et al., 2018).
+In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos (e.g., Chopik, 2018; Grahe et al., 2012, Jekel et al., 2019, Schonbrodt, 2019).
+These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 

### 2021-02-10 analysis/Manuscript.Rmd
work on exclusion criteria

--- 2021-02-10 analysis/Manuscript.Rmd
@@
 
-<!-- I need to update the main .bib file to be a synced copy of our group library, and then ensure all citations below are in that library (and that the keys match.) -->
-
 ```{r setup, include = FALSE}
@@
 For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.
-Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
-Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
+Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the Mertonian norm of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
+Even the practice of preregistration has a connection to the norm of *disinterestedness*, in that a preregistration acts as a social control reducing the potential impact of personal investment in a particular outcome from affecting the choice of results reported in a given study.
 In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.
@@
 Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
-Keeping textbooks and other instructional materials up to date is  difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
-Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that the next generation of researchers can produce research which is more replicable than that of the last.
+Keeping textbooks and other instructional materials "up to date" is obviously difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, such that the next generation of researchers can produce research which is more replicable than that of the last.
 Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for these students to become informed and critical consumers of knowledge about psychology.
-However, the question of how best to provide this understanding is by no means trivial to answer.
+However, the question of how best to provide this understanding is by no means trivial.
 Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where students lack knowledge about reproducibility and open science practices and the teacher's only role is to communicate this knowledge.
 
-First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues already.
 Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
 
-Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
+Second, when psychology students are just beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
 Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
-It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students.
+It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students, rather than simply assuming that the correct degree of calibration is always to prompt students to trust psychology research *less* than they already do.
 In their examination of the usefulness of a one-hour lecture about the replication crisis, @chopikHowWhetherTeach2018 found that undergraduate students trusted the results of studies by psychologists less after the lecture than they did before it, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
@@
 Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice.
-In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices.
-Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
-Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
+In other words, their naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than traditional practices.
 It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing "naive" assumptions.
-In fact, although beyond the scope of this article, it may even be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
-
-<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) 
-Also maybe add more about what we know about academics' endorsement of open science norms.
--->
+In fact, although beyond the scope of this article, it may possibly be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
 
@@
 In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
-
-<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? -->
 
@@
 
-```{r eligibility}
+```{r inclusion}
 
@@
 
-# note re: eligibility
-# only those who say "1" are eligible
+# note re: exclusion
+# exclude those who are younger than 18
+# only those who say "1" to eligibility are included; all other responses are excluded
+# those whose `status` variable is an 'IP Address' are included
 
@@
 
-n <- el[5,2]
-# filter(eligibility %in% 1)
+status <- df %>% 
+  dplyr::count(status_lab)
+
+# n <- el[5,2] [need to specify a final n : Breadcrumbs]
 

### 2021-02-10 preprocessing/preprocessing_students.R

@@ -34,6 +34,11 @@ meta_rename <-  function(df, metadata, old, new) {
   rename_at(df, vars(all_of(keys)), ~ values)
 }
 
+# Matt's missing data function; counts how many NAs there are
+miss_fun = function(x){
+  sum(is.na(x))
+}
+
 ##### LOAD DATA #####
 
 # raw data without labels
@@ -49,12 +54,11 @@ df_lab <- here::here("survey", "data", "students_raw_data_with_labels.csv") %>%
 
 # load metadata
 
-metadata <- read_csv(here::here("data", "students_metadata_working_data.csv")) %>%
+metadata <- read_csv(here::here("data", "students_metadata.csv")) %>%
   select(-c(X10,"note:")) %>%  # delete unnecessary columns
-  filter(old_variable != "NA") # remove the instruction variables
+  filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables
 
-
-# Breadcrumb: likely rename to remove working data
+# Breadcrumb: likely rename to remove working data [done!]
 
 #### CLEAN DATA ####
 
@@ -65,7 +69,7 @@ df_num <- df_num %>%
 
 df_lab <- df_lab %>%
   relocate(id) %>% # move the ID variable to the first column
-  select(-c(start_date:consent)) %>%  # remove extraneous columns
+  select(-c(start_date, end_date, progress:consent)) %>%  # remove extraneous columns
   select(-c(uni:major,
             gender,
             q54,
@@ -136,6 +140,73 @@ df <- df %>%
   relocate (c(uni_country, nationality), .after = gender)
 
 
+########## EXCLUSION CRITERIA ############
+
+# Breadcrumbs: random things:
+  # check to see how we used the R refs in the VR document
+  # send M&M the data files & tell them where they belong...
+  # what are we going to do with those folks who did not give their age or
+  # give information about their enrolment
+
+# Breadcrumbs: work through the exclusion criteria, then create a
+  # new 'inclusion' variable using the case when function?
+
+# I need to revisit the numbers here because it looks like extra folks have been
+  # exluded, but I don't know why.... Need to revist when my brain is fresh.
+
+# work with this later....
+df_el <- df %>%
+  filter(eligibility %in% 1) %>%
+  filter(age_lab != "0-17 years")
+# filter(eligibility %in% 1) %>%
+#   filter(status_lab %in% "IP Address")
+
+# key items in the study; look to see who did NOT respond to any of these
+study_var <- c("critical_cnorm",
+                 "critical_norm",
[…]

### 2021-02-11 analysis/Manuscript.Rmd
preprocessing/*.R

@@
 
-# all participants
-n_all <- nrow(df)
+# participant numbers (all & included cases)
+df_all <- df
+n_all <- nrow(df_all)
+df <- df_all %>% 
+  filter(exclude %in% "include") # only those who met the inclusion criterion
+n <- nrow(df)
 
-# note re: exclusion
+ex <- df_all %>% 
+  filter(exclude %in% "exclude") %>% # n for those excluded
+  nrow()
+
+# note re: exclusion [all coded in `exclude` in preprocessing, 
+# but need to summarise exclusion criteria here]
   # exclude those who are younger than 18
@@
 
-age <- df %>%
+age <- df_all %>%
   dplyr::count(age_lab)
 
-el <- df %>%
+el <- df_all %>%
   dplyr::count(eligibility_lab)
 
-status <- df %>% 
+status <- df_all %>% 
   dplyr::count(status_lab)
-
-# n <- el[5,2] [need to specify a final n : Breadcrumbs]
 
@@
 
-Of those who started the survey (*n* = `r n_all`), we screened out participants who 
-were not eligible to participate based on our preregistration. Specifically, 
-we screened out people who were younger than 18 years of age (*n* = `r age[1,2]`). 
-We also screened out individuals who had already started a psychology unit at a
-university, regardless of whether they completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); 
-were not enrolled in a psychology unit at a university (*n* = `r el[2,2]`); or did 
-not answer this question (*n* = `r el[6,2]`). The remaining `r el[5,2]` participants
+Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
+participants who were not eligible to participate based on the combination of our
+preregistered exclusion criteria. Specifically, we screened out people who were younger than 
+18 years (*n* = `r age[1,2]`). We also screened out individuals who had already 
+started a psychology unit at a university, regardless of whether they had 
+completed it (*n* = `r el[1,2] + el[3,2] + el[4,2]`); were not enrolled in a 
+psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
+question (*n* = `r el[6,2]`). We also screened out an additional XX participants
+who met our eligibility criteria, but did not respond to any of the main items
+in the study.
+
+The remaining `r n` participants
 were eligible based on starting their first unit of study in psychology at 
@@
 `r age [5,2]` were 45-54 years old, `r age [6,2]` were 55-64 years old, and
-`r age [7,2]` were 65 years or older. A small number of participants did not 
-report their age(*n* = `r age [8,2]`).
+`r age [7,2]` were 65 years or older.
 

### 2021-02-11 preprocessing/preprocessing_students.R
update exclusion criteria; still need to clean up

@@ -34,7 +34,7 @@ meta_rename <-  function(df, metadata, old, new) {
   rename_at(df, vars(all_of(keys)), ~ values)
 }
 
-# Matt's missing data function; counts how many NAs there are
+# Matt Williams's missing data function; counts how many NAs there are
 miss_fun = function(x){
   sum(is.na(x))
 }
@@ -53,7 +53,6 @@ df_lab <- here::here("survey", "data", "students_raw_data_with_labels.csv") %>%
   mutate(id = 1:n())
 
 # load metadata
-
 metadata <- read_csv(here::here("data", "students_metadata.csv")) %>%
   select(-c(X10,"note:")) %>%  # delete unnecessary columns
   filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables
@@ -145,21 +144,9 @@ df <- df %>%
 # Breadcrumbs: random things:
   # check to see how we used the R refs in the VR document
   # send M&M the data files & tell them where they belong...
-  # what are we going to do with those folks who did not give their age or
-  # give information about their enrolment
+  # what are we going to do with those folks who did not give their age [retain] or
+  # give information about their enrolment [exclude], as per reg
 
-# Breadcrumbs: work through the exclusion criteria, then create a
-  # new 'inclusion' variable using the case when function?
-
-# I need to revisit the numbers here because it looks like extra folks have been
-  # exluded, but I don't know why.... Need to revist when my brain is fresh.
-
-# work with this later....
-df_el <- df %>%
-  filter(eligibility %in% 1) %>%
-  filter(age_lab != "0-17 years")
-# filter(eligibility %in% 1) %>%
-#   filter(status_lab %in% "IP Address")
 
 # key items in the study; look to see who did NOT respond to any of these
 study_var <- c("critical_cnorm",
@@ -196,16 +183,69 @@ study_var <- c("critical_cnorm",
                  "crisis")
 
 # create new variable showing the number of items with missing values
-df$nmiss = apply(X = df[, study_var], MARGIN = 1, FUN = miss_fun)
-df_el$nmiss = apply(X = df_el[, study_var], MARGIN = 1, FUN = miss_fun)
+df$nmiss <- apply(X = df[, study_var], MARGIN = 1, FUN = miss_fun)
+df_el$nmiss <- apply(X = df_el[, study_var], MARGIN = 1, FUN = miss_fun)
 
-miss <- df %>%
[…]

### 2021-02-11 analysis/Manuscript.Rmd

--- 2021-02-10 analysis/Manuscript.Rmd
@@
 
-```{r eligibility}
+```{r inclusion}
 
-# all participants
-n_all <- nrow(df)
+# participant numbers (all & included cases)
+df_all <- df
+n_all <- nrow(df_all)
+df <- df_all %>% 
+  filter(exclude %in% "include") # only those who met the inclusion criterion
+n <- nrow(df)
 
-# note re: eligibility
-# only those who say "1" are eligible
+ex <- df_all %>% 
+  filter(exclude %in% "exclude") %>% # n for those excluded
+  nrow()
 
-age <- df %>%
+# note re: exclusion [all coded in `exclude` in preprocessing, 
+# but need to summarise exclusion criteria here]
+  # exclude those who are younger than 18
+  # only those who say "1" to eligibility are included; all other responses are excluded
+  # those whose `status` variable is an 'IP Address' are included
+
+age <- df_all %>%
   dplyr::count(age_lab)
 
-el <- df %>%
+el <- df_all %>%
   dplyr::count(eligibility_lab)
 
-n <- el[5,2]
-# filter(eligibility %in% 1)
+status <- df_all %>% 
+  dplyr::count(status_lab)
 

### 2021-02-19 analysis/Manuscript.Rmd
stash these

--- 2021-02-11 analysis/Manuscript.Rmd
@@
 
+nmiss <- df_all %>% 
+  dplyr::count(nmiss)
+
 ```
@@
 psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
-question (*n* = `r el[6,2]`). We also screened out an additional XX participants
+question (*n* = `r el[6,2]`). We also screened out an additional  participants
 who met our eligibility criteria, but did not respond to any of the main items

### 2021-02-19 preprocessing/preprocessing_students.R
clean up the exclusion criteria

@@ -35,6 +35,7 @@ meta_rename <-  function(df, metadata, old, new) {
 }
 
 # Matt Williams's missing data function; counts how many NAs there are
+
 miss_fun = function(x){
   sum(is.na(x))
 }
@@ -88,7 +89,7 @@ df <- df_num %>% inner_join(df_lab, by = "id")
 df <- meta_rename(df, metadata, old = old_variable, new = new_variable)
 
 
-# Breadcrumbs turn eligibility into a factor & use the info.
+# Breadcrumbs turn eligibility & criteria into a factor & use the info. [done]
 # again, will need to include the variable labels for those that make sense! [done!]
 # so the next step should be to select columns from the two data files & merge them [done!]
 # Also need to spend time working on the metadata!
@@ -142,10 +143,10 @@ df <- df %>%
 ########## EXCLUSION CRITERIA ############
 
 # Breadcrumbs: random things:
-  # check to see how we used the R refs in the VR document
+  # check to see how we used the R refs in the VR document [done & fixed]
   # send M&M the data files & tell them where they belong...
   # what are we going to do with those folks who did not give their age [retain] or
-  # give information about their enrolment [exclude], as per reg
+  # give information about their enrolment [exclude], as per prereg
 
 
 # key items in the study; look to see who did NOT respond to any of these
@@ -184,68 +185,53 @@ study_var <- c("critical_cnorm",
 
 # create new variable showing the number of items with missing values
 df$nmiss <- apply(X = df[, study_var], MARGIN = 1, FUN = miss_fun)
-df_el$nmiss <- apply(X = df_el[, study_var], MARGIN = 1, FUN = miss_fun)
 
-# create a new variable `exclude` to indicate which participants meet our inclusion criteria
+
+# create a new factor `exclude` to indicate which participants meet our inclusion criteria
+
 df <- df %>%
-  mutate(exclude = case_when(
+  mutate(exclude = factor(case_when(
     eligibility == '1' & nmiss < 32  ~ "include",
-    TRUE ~ "exclude"))
+    TRUE ~ "exclude")))
 
-# can use just eligibility to cover the exclusion criteria of age & Qualtrics status.
+# can use just eligibility == 1 to cover the exclusion criteria of age & Qualtrics status.
[…]

### 2021-02-19 analysis/Manuscript.Rmd
finish the exclusion criteria section

--- 2021-02-11 analysis/Manuscript.Rmd
@@
 wordcount: X
-bibliography: [Matt_Zotero_Library.bib,r-references.bib]
+bibliography: ['r-references.bib','Matt_Zotero_Library.bib']
 floatsintext: yes
@@
 n_all <- nrow(df_all)
+
+# only participants who met the inclusion criterion
 df <- df_all %>% 
-  filter(exclude %in% "include") # only those who met the inclusion criterion
+  filter(exclude %in% "include") 
 n <- nrow(df)
@@
 # but need to summarise exclusion criteria here]
-  # exclude those who are younger than 18
+  # exclude those who are younger than 18 [7]
   # only those who say "1" to eligibility are included; all other responses are excluded
@@
 
-age <- df_all %>%
-  dplyr::count(age_lab)
+age_ex <- df_all %>%
+  filter(age_criteria %in% "exclude") %>% 
+  nrow()
 
 el <- df_all %>%
-  dplyr::count(eligibility_lab)
+  filter(eligibility_criteria %in% "exclude") %>% 
+  dplyr::count(eligibility_lab) # need the breakdown by condition
 
 status <- df_all %>% 
-  dplyr::count(status_lab)
+  filter(status_criteria %in% "exclude") %>% 
+  dplyr::count(status_lab) # need the breakdown by condition
+
+nmiss <- df_all %>% 
+  filter(nmiss_criteria %in% "exclude") %>% 
+  nrow()
 
@@
 preregistered exclusion criteria. Specifically, we screened out people who were younger than 
-18 years (*n* = `r age[1,2]`). We also screened out individuals who had already 
+18 years (*n* = `r age_ex`). We also screened out individuals who had already 
 started a psychology unit at a university, regardless of whether they had 
@@
 psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
-question (*n* = `r el[6,2]`). We also screened out an additional XX participants
-who met our eligibility criteria, but did not respond to any of the main items
-in the study.
+question (*n* = `r el[5,2]`). We then excluded additional responses that 
+Qualtrics flagged as spam (*n* = `r status [1,2]`) or as a survey preview 
+(*n* = `r status [2,2]`). Finally, we excluded participants who met all other 
+eligibility criteria, but did not respond to any of the main items
+in the study (*n* = `r nmiss`).
 
-The remaining `r n` participants
-were eligible based on starting their first unit of study in psychology at 
+The remaining `r n` participants were eligible based on starting their first unit of study in psychology at 
 a university within the next month. For those individuals who were screened out, 
@@
 ## Data analysis
+<!-- Can we move this to a reproducible code statement at the end? It works now -->
+
 We used `r cite_r("r-references.bib")` for all our analyses.
@@
 <div id="refs" custom-style="Bibliography"></div>
+
 \endgroup

### 2021-02-23 analysis/Manuscript.Rmd
OK FINE NO MORE MATT'S ZOTERO LIBRARY OF EVERYTHING

@@
 wordcount: X
-bibliography: ['r-references.bib','Matt_Zotero_Library.bib']
+bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
 floatsintext: yes
@@
 
-<!-- I need to update the main .bib file to be a synced copy of our group library, and then ensure all citations below are in that library (and that the keys match.) -->
+<!-- The .bib file is now just from our shared library -->
 

### 2021-02-24 analysis/Manuscript.Rmd
taking .bib out of gitignore

@@
 These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
-These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
+These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
 Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices (e.g., Baker, 2016; Chambers & Morey, 2017@[https://osf.io/dmfke/], Harris et al., 2018).

### 2021-02-24 preprocessing/preprocessing_students.R
Remove factor variable recoding

@@ -88,49 +88,15 @@ df <- df_num %>% inner_join(df_lab, by = "id")
 
 df <- meta_rename(df, metadata, old = old_variable, new = new_variable)
 
-
 # Breadcrumbs turn eligibility & criteria into a factor & use the info. [done]
 # again, will need to include the variable labels for those that make sense! [done!]
 # so the next step should be to select columns from the two data files & merge them [done!]
-# Also need to spend time working on the metadata!
+# Also need to spend more time working on the metadata!
 # will need to keep the num & label versions for the strongly agree variables [done!]
 
 
 #### CONVERT VARIABLES INTO FACTORS ####
 
-# [[ Breadcrumbs: I think I need to delete all of this from here & just do it
-   # when I import the data into the Rmd file]]
-
-# df$age <- factor(df$age)
-# df$age_lab <- factor(df$age_lab)
-# df$eligibility <- factor(df$eligibility)
-# df$eligibility_lab <- factor(df$eligibility_lab)
-# df$high_school <- factor(df$high_school)
-# df$high_school_lab <- factor(df$high_school_lab)
-# df$psych_hs <- factor(df$psych_hs)
-# df$psych_hs_lab <- factor(df$psych_hs_lab)
-# df$first_gen_lab <- factor(df$first_gen_lab)
-# df$critical_cnorm_lab <- factor(df$critical_cnorm_lab)
-# df$critical_norm_lab <- factor(df$critical_norm_lab)
-# df$prereg_norm_lab <- factor(df$prereg_norm_lab)
-# df$prereg_cnorm_lab <- factor(df$prereg_cnorm_lab)
-# df$reg_report_norm_lab <- factor(df$reg_report_norm_lab)
-# df$reg_report_cnorm_lab <- factor(df$reg_report_cnorm_lab)
-# df$phack_cnorm_lab <- factor(df$phack_cnorm_lab)
-# df$phack_norm_lab <- factor(df$phack_norm_lab)
-# df$hark_cnorm_lab <- factor(df$hark_cnorm_lab)
-# df$hark_norm_lab <- factor(df$hark_norm_lab)
-# df$info_for_rep_norm_lab <- factor(df$info_for_rep_norm_lab)
-# df$info_for_rep_cnorm_lab <- factor(df$info_for_rep_cnorm_lab)
-# df$preprint_norm_lab <- factor(df$preprint_norm_lab)
[…]

### 2021-02-24 analysis/Manuscript.Rmd
continue with demographics

@@
 # but need to summarise exclusion criteria here]
-  # exclude those who are younger than 18 [7]
-  # only those who say "1" to eligibility are included; all other responses are excluded
-  # those whose `status` variable is an 'IP Address' are included
 
@@
 
-```{r demographics}
+```{r demographics for those included in analyses}
 
-# gender --> need to run through gendercoder
+# age
+age <- df %>% dplyr::count(age_lab)
+
+# gender --> need to run through gendercoder [breadcrumb!]
+
 # high school status
+hs_status <- df %>% dplyr::count(high_school_lab)
+
 # high school psyc 
+hs_psyc <- df %>% dplyr::count(psych_hs_lab)
+
 # country of university 
+uni_country <- df %>% dplyr::count(uni_country)
+
 # country of nationality
+nationality <- df %>% dplyr::count(nationality)
+
 # whether parents' attended uni
-
+first_gen <- df %>% dplyr::count(first_gen_lab)
 ```
@@
 Of the remaining `r n` participants, most reported that they were
-18-24 years old (*n* = `r age[2,2]`), `r age [3,2]` 
-reported that they were 25-34 years old, `r age [4,2]` were 35-44 years old,
-`r age [5,2]` were 45-54 years old, `r age [6,2]` were 55-64 years old, and
-`r age [7,2]` were 65 years or older.
+18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
+reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
+`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. ADD GENDER HERE!
+
+Nearly all reported that they graduated from high
+school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
+attended high school, a little less than half completed psychology courses in 
+high school (*n* = `r hs_psyc[2,2]`). In terms of their nationality, most 
+participants reported that they were Australian (*n* = `r nationality[3,2]`), 
+from the United Kingdom (*n* = `r nationality[24,2]`), or Chinese 
+(*n* = `r nationality[6,2]`). In terms of where the participants were attending 
+university, most reported that they were in Australia (*n* = `r uni_country[1,2]`), 
+the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). 
+Finally, about 2/3rds of participants reported that at least one of their parents 
+attended university (*n* = `r first_gen[2,2]`).
 

### 2021-02-24 analysis/Manuscript.Rmd
Mostly updating citations

--- 2021-02-23 analysis/Manuscript.Rmd
@@
 I'd suggest this could make the first paragraph of the paper – highlighting the the research context and the gap that is driving our study-->
+
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
 These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
-These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
-Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices (e.g., Baker, 2016; Chambers & Morey, 2017@[https://osf.io/dmfke/], Harris et al., 2018).
-In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos (e.g., Chopik, 2018; Grahe et al., 2012, Jekel et al., 2019, Schonbrodt, 2019).
+These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
+These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
+Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018).
+In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].
 These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
@@
 
-First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media: Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018; @ogradyPsychologyReplicationCrisis2020].
+Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
 Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
@@
 Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
-It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more of reinforcing "naive" assumptions.
-In fact, although beyond the scope of this article, it may even be the case that incoming undergraduate students more strongly endorse open science norms than do academics.
+It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions.
+In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.
 
@@
 These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
-In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses and learning about psychological research in any given year dwarfs the number of academics working in psychology.
+In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology.
 As such, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
@@
 In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices.
+This study is exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.
 

### 2021-02-24 analysis/Manuscript.Rmd
Mertonian norms intro
A couple of sentences to better link mertoinian norms to prev paragraph and transition to examples of norms

@@
 
-Many of these recent changes have links to the classic *Mertonian* norms of science [@mertonSociologyScienceTheoretical1973].
+The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science.
+Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles.
+Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.
 For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.

### 2021-03-05 preprocessing/preprocessing_degrees.R
Add gender recoding and draft of preprocessing for degrees, majors, and universities

@@ -1,0 +1,275 @@
+df <- df %>%
+  mutate(
+    university_recoded = case_when(
+      university == "Adelaide"                                   ~ "University of Adelaide",
+      university == "adelaide uni"                               ~ "University of Adelaide",
+      university == "Adelaide uni"                               ~ "University of Adelaide",
+      university == "adelaide university"                        ~ "University of Adelaide",
+      university == "Adelaide university"                        ~ "University of Adelaide",
+      university == "the University of Adelaide"                 ~ "University of Adelaide",
+      university == "university of  adelaide"                    ~ "University of Adelaide",
+      university == "university of adelaide"                     ~ "University of Adelaide",
+      university == "the university of adelaide"                 ~ "University of Adelaide",
+      university == "The university of Adelaide"                 ~ "University of Adelaide",
+      university == "University of Adelaide."                    ~ "University of Adelaide",
+      university == "Adelaide University"                        ~ "University of Adelaide",
+      university == "Univerisity of Adelaide"                    ~ "University of Adelaide",
+      university == "University of Adelaide"                     ~ "University of Adelaide",
+      university == "Adelaide Uni"                               ~ "University of Adelaide",
+      university == "Adelaide Universtiy"                        ~ "University of Adelaide",
+      university == "The University of Adelaide"                 ~ "University of Adelaide" ,
+      university == "University of  Adelaide"                    ~ "University of Adelaide" ,
+      university == "Bath"                                       ~ "University of Bath",
+      university == "Batj"                                       ~ "University of Bath" ,
+      university == "University of Bath"                         ~ "University of Bath",
+      university == "Bath University"                            ~ "University of Bath" ,
+      university == "The University of Bath"                     ~ "University of Bath",
+      university == "university of bath"                         ~ "University of Bath",
+      university == "Haverford College"                          ~ "Haverford College",
+      university == "Massey University"                          ~ "Massey University",
[…]

### 2021-03-05 preprocessing/preprocessing_students.R

@@ -9,6 +9,7 @@
 library(tidyverse)
 library(here)
 library(tools)
+library(gendercodeR)
 
 
 ####### FUNCTIONS ############
@@ -43,13 +44,13 @@ miss_fun = function(x){
 ##### LOAD DATA #####
 
 # raw data without labels
-df_num <- here::here("data", "students_raw_data.csv") %>%
+df_num <- here::here("survey", "data", "students_raw_data.csv") %>%
   read_qualtrics(legacy = TRUE) %>%
   mutate(id = 1:n())
 
 
 # raw data with labels
-df_lab <- here::here("data", "students_raw_data_with_labels.csv") %>%
+df_lab <- here::here("survey", "data", "students_raw_data_with_labels.csv") %>%
   read_qualtrics(legacy = FALSE) %>%
   mutate(id = 1:n())
 
@@ -100,54 +101,67 @@ df <- meta_rename(df, metadata, old = old_variable, new = new_variable)
 
 ###### REARRANGE THE VARIABLES IN THE TIBBLE TO ALIGN WITH SURVEY ORDER ######
 # at least somewhat; I haven't moved the number and label variables of each
-  # question together, but this brings the demographics info together
+# question together, but this brings the demographics info together
 
 df <- df %>%
   relocate (c(uni_country, nationality), .after = gender)
+
+######### RECODE GENDER ##########
+
+custom_dictionary <- list(
+  `female.` = "female",
+  `femamle` = "female",
+  `-` = NA_character_,
+  `gender no longer has a place in modern society. sex is male.` = "male",
+  `queer man` = "queer man"
+)
+
+df <- df %>%
+  mutate(gender  = recode_gender(gender, dictionary = c(broad, custom_dictionary), fill = TRUE))
 
 
 ########## EXCLUSION CRITERIA ############
 
 # Breadcrumbs: random things:
-  # check to see how we used the R refs in the VR document [done & fixed]
-  # send M&M the data files & tell them where they belong...
-  # what are we going to do with those folks who did not give their age [retain] or
-  # give information about their enrolment [exclude], as per prereg
+# check to see how we used the R refs in the VR document [done & fixed]
+# send M&M the data files & tell them where they belong... [done]
+# what are we going to do with those folks who did not give their age [retain] or
+# give information about their enrolment [exclude], as per prereg [done]
 
 
 # key items in the study; look to see who did NOT respond to any of these
 study_var <- c("critical_cnorm",
[…]

### 2021-03-05 analysis/Manuscript.Rmd
Emily manuscript comments

@@
 In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].
-These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
+These initiatives hope to engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 
@@
 Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
-In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.
+In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.<!-- EK: citations in this section need to be converted --->
 
@@
 
-<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) 
-Also maybe add more about what we know about academics' endorsement of open science norms.
--->
+<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) <!-- EK - Perhaps we could do a call out on twitter?
+I'm sure I've seen things in the past on this topic, also there might be something about patient assumptions that their data would be shared and papers open access when they take part in clinical trials?
+--->
+<!-- Also maybe add more about what we know about academics' endorsement of open science norms.-->
 

### 2021-03-08 preprocessing/preprocessing_students.R
clean up breadcrumbs

@@ -58,8 +58,6 @@ metadata <- read_csv(here::here("data", "students_metadata.csv")) %>%
   select(-c(X10,"note:")) %>%  # delete unnecessary columns
   filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables
 
-# Breadcrumb: likely rename to remove working data [done!]
-
 #### CLEAN DATA ####
 
 df_num <- df_num %>%
@@ -88,11 +86,7 @@ df <- df_num %>% inner_join(df_lab, by = "id")
 
 df <- meta_rename(df, metadata, old = old_variable, new = new_variable)
 
-# Breadcrumbs turn eligibility & criteria into a factor & use the info. [done]
-# again, will need to include the variable labels for those that make sense! [done!]
-# so the next step should be to select columns from the two data files & merge them [done!]
-# Also need to spend more time working on the metadata!
-# will need to keep the num & label versions for the strongly agree variables [done!]
+# Breadcrumbs finish working on the metadata!
 
 
 #### CONVERT VARIABLES INTO FACTORS ####
@@ -110,13 +104,6 @@ df <- df %>%
 # gender --> need to run through gendercoder [breadcrumb!]
 
 ########## EXCLUSION CRITERIA ############
-
-# Breadcrumbs: random things:
-  # check to see how we used the R refs in the VR document [done & fixed]
-  # send M&M the data files & tell them where they belong... [done]
-  # what are we going to do with those folks who did not give their age [retain] or
-  # give information about their enrolment [exclude], as per prereg [done]
-
 
 # key items in the study; look to see who did NOT respond to any of these
 study_var <- c("critical_cnorm",
@@ -167,16 +154,12 @@ df <- df %>%
   # also need to exclude those who were eligible, but did not answer any of the
   # key questions (nmiss = 32).
 
-
-# [[BREADCRUMBS: CLEAN ALL OF THIS UP & WORK THROUGH THE LOGIC AGAIN, INCLUDE
-#   THE KEY INFO RE HOW MANY WERE ELIGIBLE, BUT DID NOT COMPLETE ANY KEY
-#   MEASURES [88] BASED ON THE ANTI-JOIN!]] [done!]
-# add the exclusion variables to the dataframe & metadata (and remove when
+# breadcrumb: add the exclusion variables to the dataframe & metadata (and remove when
   # loading metadata) [still need to do!]
 
 # create new variables for each of the eliibility criteria
   # capture the hieararchy of decisions, but forcing previously-excluded cases to
[…]

### 2021-03-09 analysis/Manuscript.Rmd
Tightening up third paragraph
Rewriting a few parts of this paragraph to help the flow a bit.

--- 2021-02-24 analysis/Manuscript.Rmd
@@
 
-<!--MP ➔ The paragraph below is an attempt to segue to the aim of our study before getting into the lit review – I'm always of fan of making the general aim of the study clear by the end of the first paragraph.
-I've summarised the sentiment of the original first two paragraphs a bit (and struck out tangential sentences).
-I'd suggest this could make the first paragraph of the paper – highlighting the the research context and the gap that is driving our study-->
-
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
@@
 Keeping textbooks and other instructional materials up to date is  difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
-Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that the next generation of researchers can produce research which is more replicable than that of the last.
-Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for these students to become informed and critical consumers of knowledge about psychology.
-However, the question of how best to provide this understanding is by no means trivial to answer.
-Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where students lack knowledge about reproducibility and open science practices and the teacher's only role is to communicate this knowledge.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that thay may produce research that is even more replicable than that of previous generations.
+Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge.
+However, how we best provide this understanding is no trivial task.
+Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where the teacher's only role is to dispense an understanding of open science and transparent research practices.
 
@@
 
-# gender --> need to run through gendercoder [breadcrumb!]
+# gender --> need to summarise once we've recoded it in preprocessing script
+  # [breadcrumb]
 

### 2021-03-09 docs/index.Rmd
Tightening up third paragraph
Rewriting a few parts of this paragraph to help the flow a bit.

---
title: "Project Documentation"
author: "Danielle Navarro"
date: "23/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The "docs" folder on GitHub is special: if your project is set up to allow it, any files in this folder will appear as a GitHub Pages website. For example, this template is located at https://github.com/djnavarro/newproject, and because I have enabled GitHub pages for this project all the files in this folder are hosted at https://djnavarro.github.io/newproject. It is very often useful to have a public facing website associated with a project that gives people an overview of the whole thing, and this is an easy way to do it.

To help you get started, GitHub have a [nice walkthrough](https://pages.github.com/#project-site) showing you how to enable GitHub Pages for a specific project. There is also a more detailed tutorial [here](https://help.github.com/en/articles/configuring-a-publishing-source-for-github-pages)

### 2021-03-09 analysis/Manuscript.Rmd
Working on differences in means

--- 2021-02-24 analysis/Manuscript.Rmd
@@
 
-The remaining `r n` participants were eligible based on starting their first unit of study in psychology at 
-a university within the next month. For those individuals who were screened out, 
-our Qualtrics program automatically directed them to the debriefing form.
+The remaining `r n` participants were eligible based on starting their first unit 
+of study in psychology at a university within the next month. For those individuals 
+who were screened out, our Qualtrics program automatically directed them to the 
+debriefing form.
 
@@
 reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
-`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. ADD GENDER HERE!
+`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old.
+
+<!-- ADD GENDER HERE! -->
 
@@
 ## Data analysis
-<!-- Can we move this to a reproducible code statement at the end? It works now -->
 
-We used `r cite_r("r-references.bib")` for all our analyses.
+```{r, difference between norm & counternorm, eval = FALSE}
+
+# select all columns that relate to norms & counternorms
+diff <- df %>% select(c(id, ends_with("norm")))
+
+means <- diff %>% 
+  sapply(mean, na.rm = TRUE)
+
+knitr::kable(means)
+
+# select columns that relate to norms
+norms <- df %>% select(c(id, ends_with("_norm")))
+
+# select columns that relate to counternorms
+cnorms <- df %>% select(c(id, ends_with("_cnorm")))
+
+# breadcrumbs - pivot long
+
+norm_long <- norms %>% 
+  pivot_longer (cols = ends_with("norm"),
+                names_to = "practice",
+                values_to = "rating") 
+  str_remove(norm_long, "_norm")
+
+norm_wide <- diff %>% 
+  pivot_wider(names_from = ends_with("_norm"),
+              values_from = c(ends_with("_norm"), ends_with("_cnorm"))
+)
+```
+
+```{r, eval=FALSE}
+# I'm sure there's a fancier way to subtract the counternorm from the norm, 
+  # but for now we will do this...
+
+norms <-  vars_select(names(df), ends_with('_norm'))
+cnorms <-  vars_select(names(df), ends_with('_cnorm'))
+
+miss_fun = function(x){
+  sum(is.na(x))
+}
+
+diff_fun = function(x, y){
+  (norms - cnorms)
+}
+
+diff_fun(x = norms, y = cnorms)
+
+df$diff <- apply(X = df[, ], MARGIN = 1, FUN = miss_fun)
+
+```
 
@@
 # Discussion
+
+\newpage
+# Reproducible Code Statement
+
+We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2021-03-09 analysis/Manuscript.tex
clean up files

--- 2020-12-22 analysis/Manuscript.tex
@@
 \documentclass[
-  english,
   man,mask,floatsintext]{apa6}
@@
   pdftitle={What do incoming university students believe about open science practices in psychology?},
-  pdfauthor={Jennifer L. Beaudry1, Michael C. Philipp2, \& Matt N. Williams2},
-  pdflang={en-EN},
+  pdfauthor={Jennifer L. Beaudry, Michael C. Philipp, \& Matt N. Williams},
   pdfkeywords={open science, psychology, teaching, reproducibility, replication},
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{graphicx,grffile}
+\usepackage{graphicx}
 \makeatletter
@@
 \setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-% Manuscript styling
+\shorttitle{Psychology students' beliefs about open science}
+\affiliation{
+\vspace{0.5cm}
+\textsuperscript{1} Swinburne University of Technology\\\textsuperscript{2} Massey University}
+\keywords{open science, psychology, teaching, reproducibility, replication\newline\indent Word count: X}
+\usepackage{csquotes}
 \usepackage{upgreek}
@@
 
-% Table formatting
 \usepackage{longtable}
 \usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+\usepackage{multirow}
+\usepackage{tabularx}
+\usepackage[flushleft]{threeparttable}
+\usepackage{threeparttablex}
 
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
 \newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
 \makeatletter
@@
 
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{Psychology students' beliefs about open science}
-\keywords{open science, psychology, teaching, reproducibility, replication\newline\indent Word count: X}
 \usepackage{lineno}
@@
 \linenumbers
-\usepackage{csquotes}
-\ifxetex
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[shorthands=off,main=english]{babel}
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newenvironment{cslreferences}%
+  {\setlength{\parindent}{0pt}%
+  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
+  {\par}
 
@@
 
-\authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
+\authornote{Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
 Enter author note here.
 
-The authors made the following contributions. Jennifer L. Beaudry: ; Michael C. Philipp: ; Matt N. Williams: .
-
-Correspondence concerning this article should be addressed to Jennifer L. Beaudry, Postal address. E-mail: \href{mailto:jbeaudry@swin.edu.au}{\nolinkurl{jbeaudry@swin.edu.au}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Swinburne University of Technology\\\textsuperscript{2} Massey University}
+Correspondence concerning this article should be addressed to Jennifer L. Beaudry, Postal address. E-mail: \href{mailto:jbeaudry@swin.edu.au}{\nolinkurl{jbeaudry@swin.edu.au}}}
 
@@
 Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
+
 }
@@
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
-These changes were partly precipitated by what is popularly known as the \enquote{replication crisis}: The discovery that close replications of published psychological studies are often unable to replicate the original findings.
-For example, in an attempt to replicate 100 published psychological studies, only 38\% were adjudged to have replicated the original result, and the average effect size was half that in the original studies (Open Science Collaboration, 2015).
+These changes were partly precipitated by what is popularly known as the ``replication crisis'': The discovery that close replications of published psychological studies are often unable to replicate the original findings(Klein et al., 2014, 2018).
+These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies (see Brandt et al., 2014), more thorough reporting of methods and results (Simmons, Nelson, \& Simonsohn, 2012), open sharing of data (see Meyer, 2018), and preregistration of data collection and analysis plans (Nosek, Ebersole, DeHaven, \& Mellor, 2018).
+These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
+Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices {[}e.g., Baker (2016); Group (2018), Harris et al.
+(2018)).
+In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos (e.g., Chopik, Bremner, Defever, \& Keller, 2018; Grahe et al., 2012, pp.
+Jekel et al.
+(2020), Schönbrodt(2019)).
+These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 
-These apparent problems with replicability led to speculation regarding its causes, and a variety of potential solutions being proferred.
-Some of these potential solutions include more frequently conducting and publishing replication studies (see Brandt et al., 2014), more transparent reporting of methods and results (Simmons, Nelson, \& Simonsohn, 2012), open sharing of data (see Meyer, 2018), and preregistration of data collection and analysis plans (Nosek, Ebersole, DeHaven, \& Mellor, 2018).
+The most comprehensive set of principles for how science \emph{ought} to be practiced are Merton's (1942) norms of science.
+Scientists (Anderson et al., 2000) and graduate students (Anderson \& Louis, 1994) alike have historically endorsed the normative value of Merton's principles.
+Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.
+For example, the practice of sharing open source software directly corresponds to the Mertonian norm of \emph{communism}: Scientists should have common ownership of scientific goods.
+Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of \emph{organised skepticism}: Scientific claims should be subjected to critical scrutiny.
+Preregistration can be connected to the norm of \emph{disinterestedness}: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
+In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.
+
+Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
+Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that the next generation of researchers can produce research which is more replicable than that of the last.
+Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for these students to become informed and critical consumers of knowledge about psychology.
+However, the question of how best to provide this understanding is by no means trivial to answer.
+Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where students lack knowledge about reproducibility and open science practices and the teacher's only role is to communicate this knowledge.
+
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media (e.g., Yong, 2016, 2018; O'Grady, 2020, \& Pm, 2020).
+Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
+Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
+
+Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
+Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable \emph{at all}, leaving them to favour even less credible alternative sources of knowledge?
+It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students.
+In their examination of the usefulness of a one-hour lecture about the replication crisis, Chopik et al.
+(2018) found that undergraduate students trusted the results of studies by psychologists less after the lecture than they did before it, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
+
+Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not \emph{already} standard practice.
+In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than ``business as usual'' practices.
+Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
+Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own (Anderson, Martinson, \& De Vries, 2007).
+It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more one of reinforcing ``naive'' assumptions.
+In fact, although beyond the scope of this article, it is \emph{possible} that incoming undergraduate students more strongly endorse open science norms than do academics.
+
+These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
+In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology.
+As such, the \emph{preferences} of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
+If, for example, undergraduate psychology students have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce should have some bearing on our choices in relation to sharing of manuscripts.
+This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
+In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
+
+For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
+Our survey encompassed norms (how students felt research \emph{should} be conducted), norms in practice (how students believe psychological research \emph{is} conducted) and replicability (how replicable students believe psychological research is).
+In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices.
+This study is exploratory (see Wagenmakers, Wetzels, Borsboom, van der Maas, \& Kievit, 2012) and descriptive, and does not involve the specification or testing of hypotheses.
 
@@
 \subsection{Participants}\label{participants}}
+
+Of those who started the survey (\emph{n} = 423), we screened out 184
+participants who were not eligible to participate based on the combination of our
+preregistered exclusion criteria. Specifically, we screened out people who were younger than
+18 years (\emph{n} = 7). We also screened out individuals who had already
+started a psychology unit at a university, regardless of whether they had
+completed it (\emph{n} = 72); were not enrolled in a
+psychology unit at a university (\emph{n} = 1); or did not answer this
+question (\emph{n} = 14). We then excluded additional responses that
+Qualtrics flagged as spam (\emph{n} = 1) or as a survey preview
+(\emph{n} = 1). Finally, we excluded participants who met all other
+eligibility criteria, but did not respond to any of the main items
+in the study (\emph{n} = 88).
+
+The remaining 239 participants were eligible based on starting their first unit
+of study in psychology at a university within the next month. For those individuals
+who were screened out, our Qualtrics program automatically directed them to the
+debriefing form.
+
+Of the remaining 239 participants, most reported that they were
+18-24 years old (\emph{n} = 193), 21
+reported that they were 25-34 years old, 12 were 35-44 years old,
+12 were 45-54 years old, and 1 was 55-64 years old.
+
+Nearly all reported that they graduated from high
+school or secondary school (\emph{n} = 230). Of those participants who
+attended high school, a little less than half completed psychology courses in
+high school (\emph{n} = 106). In terms of their nationality, most
+participants reported that they were Australian (\emph{n} = 125),
+from the United Kingdom (\emph{n} = 43), or Chinese
+(\emph{n} = 15). In terms of where the participants were attending
+university, most reported that they were in Australia (\emph{n} = 160),
+the United Kingdom (\emph{n} = 63), or New Zealand (\emph{n} = 11).
+Finally, about 2/3rds of participants reported that at least one of their parents
+attended university (\emph{n} = 157).
 
@@
 
-We used R (Version 4.0.3; {\textbf{???}}) and the R-package \emph{papaja} (Version 0.1.0.9997; {\textbf{???}}) for all our analyses.
+\begin{tabular}{l|r}
+\hline
+  & x\\
+\hline
+critical\_cnorm & 2.410042\\
+\hline
+critical\_norm & 4.322176\\
+\hline
+prereg\_norm & 3.974895\\
+\hline
+prereg\_cnorm & 2.753138\\
+\hline
+reg\_report\_norm & 3.355649\\
+\hline
+reg\_report\_cnorm & 3.556485\\
+\hline
+phack\_cnorm & 2.133891\\
+\hline
+phack\_norm & 4.338912\\
+\hline
+hark\_cnorm & 1.661088\\
+\hline
+hark\_norm & 3.887029\\
+\hline
+info\_for\_rep\_norm & 4.422594\\
+\hline
+info\_for\_rep\_cnorm & 1.514644\\
+\hline
+preprint\_norm & 1.610879\\
+\hline
+preprint\_cnorm & 4.357143\\
+\hline
+open\_materials\_norm & 3.689076\\
+\hline
+open\_materials\_cnorm & 2.497908\\
+\hline
+open\_data\_norm & 2.656904\\
+\hline
+open\_data\_cnorm & 3.485356\\
+\hline
+open\_access\_norm & 3.857143\\
+\hline
+open\_access\_cnorm & 2.531381\\
+\hline
+\end{tabular}
 
@@
 \section{Discussion}\label{discussion}}
+
+\newpage
+
+\hypertarget{reproducible-code-statement}{%
+\section{Reproducible Code Statement}\label{reproducible-code-statement}}
+
+We used R (Version 3.6.3; R Core Team, 2020) and the R-packages \emph{dplyr} (Version 1.0.2; Wickham et al., 2020), \emph{forcats} (Version 0.5.0; Wickham, 2020), \emph{ggplot2} (Version 3.3.3; Wickham, 2016), \emph{here} (Version 0.1; Müller, 2017), \emph{papaja} (Version 0.1.0.9842; Aust \& Barth, 2018), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 1.3.1; Wickham, Hester, \& Francois, 2018), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.0.4; Müller \& Wickham, 2020), \emph{tidyr} (Version 1.1.1; Wickham \& Henry, 2020), and \emph{tidyverse} (Version 1.3.0; Wickham, Averick, et al., 2019) for all our analyses.
 
@@
 \hypertarget{refs}{}
+\begin{cslreferences}
+\leavevmode\hypertarget{ref-andersonNormativeDissonanceScience2007}{}%
+Anderson, M.
+S., Martinson, B.
+C., \& De Vries, R.
+(2007).
+Normative dissonance in science: Results from a national survey of U.S.
+Scientists.
+\emph{Journal of Empirical Research on Human Research Ethics}, \emph{2}(4), 3--14.
+doi:\href{https://doi.org/10.1525/jer.2007.2.4.3}{10.1525/jer.2007.2.4.3}
+
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-baker500ScientistsLift2016}{}%
+Baker, M. (2016). 1,500 scientists lift the lid on reproducibility. \emph{Nature News}, \emph{533}(7604), 452. doi:\href{https://doi.org/10.1038/533452a}{10.1038/533452a}
+
 \leavevmode\hypertarget{ref-brandtReplicationRecipeWhat2014}{}%
@@
 \emph{Journal of Experimental Social Psychology}, \emph{50}, 217--224.
-\url{https://doi.org/10.1016/j.jesp.2013.10.005}
+doi:\href{https://doi.org/10.1016/j.jesp.2013.10.005}{10.1016/j.jesp.2013.10.005}
+
+\leavevmode\hypertarget{ref-chopikHowWhetherTeach2018}{}%
+Chopik, W.
+J., Bremner, R.
+H., Defever, A.
+M., \& Keller, V.
+N.
+(2018).
+How (and whether) to teach undergraduates about the replication crisis in psychological science.
+\emph{Teaching of Psychology}, \emph{45}(2), 158--163.
+doi:\href{https://doi.org/10.1177/0098628318762900}{10.1177/0098628318762900}
+
+\leavevmode\hypertarget{ref-graheHarnessingUndiscoveredResource2012}{}%
+Grahe, J.
+E., Reifman, A., Hermann, A.
+D., Walker, M., Oleson, K.
+C., Nario-Redmond, M., \& Wiebe, R.
+P.
+(2012).
+Harnessing the undiscovered resource of student research projects.
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 605--607.
+doi:\href{https://doi.org/10.1177/1745691612459057}{10.1177/1745691612459057}
+
+\leavevmode\hypertarget{ref-openscienceworkinggroup2017SurveyOpen2018}{}%
+Group, O. S. W. (2018). \emph{2017 survey on open research practices administered by the School of Psychology, Cardiff University}. Cardiff University.
+
+\leavevmode\hypertarget{ref-harrisUseReproducibleResearch2018}{}%
+Harris, J.
+K., Johnson, K.
+J., Carothers, B.
+J., Combs, T.
+B., Luke, D.
+A., \& Wang, X.
+(2018).
+Use of reproducible research practices in public health: A survey of public health analysts.
+\emph{PLOS ONE}, \emph{13}(9), e0202447.
+doi:\href{https://doi.org/10.1371/journal.pone.0202447}{10.1371/journal.pone.0202447}
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-jekelHowTeachOpen2020}{}%
+Jekel, M., Fiedler, S., Allstadt Torras, R., Mischkowski, D., Dorrough, A.
+R., \& Glöckner, A.
+(2020).
+How to teach open science principles in the undergraduate curriculumthe Hagen cumulative science project.
+\emph{Psychology Learning \& Teaching}, \emph{19}(1), 91--106.
+doi:\href{https://doi.org/10.1177/1475725719868149}{10.1177/1475725719868149}
+
+\leavevmode\hypertarget{ref-kleinInvestigatingVariationReplicability2014}{}%
+Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams Jr., R.
+B., Bahník, Š., Bernstein, M.
+J., \ldots{} Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A ``many labs'' replication project.
+\emph{Social Psychology}, \emph{45}(3), 142--152.
+doi:\href{https://doi.org/10.1027/1864-9335/a000178}{10.1027/1864-9335/a000178}
+
+\leavevmode\hypertarget{ref-kleinManyLabsInvestigating2018}{}%
+Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams, R.
+B., Alper, S., \ldots{} Nosek, B.
+A.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
+doi:\href{https://doi.org/10.1177/2515245918810225}{10.1177/2515245918810225}
 
 \leavevmode\hypertarget{ref-meyerPracticalTipsEthical2018}{}%
-Meyer, M. N. (2018). Practical tips for ethical data sharing. \emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 131--144. \url{https://doi.org/10.1177/2515245917747656}
+Meyer, M.
+N.
+(2018).
+Practical tips for ethical data sharing.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 131--144.
+doi:\href{https://doi.org/10.1177/2515245917747656}{10.1177/2515245917747656}
+
+\leavevmode\hypertarget{ref-R-here}{}%
+Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
@@
 \emph{Proceedings of the National Academy of Sciences}, \emph{115}(11), 2600--2606.
-\url{https://doi.org/10.1073/pnas.1708274114}
+doi:\href{https://doi.org/10.1073/pnas.1708274114}{10.1073/pnas.1708274114}
 
-\leavevmode\hypertarget{ref-opensciencecollaborationEstimatingReproducibilityPsychological2015a}{}%
-Open Science Collaboration. (2015). Estimating the reproducibility of psychological science. \emph{Science}, \emph{349}(6251), aac4716--aac4716. \url{https://doi.org/10.1126/science.aac4716}
+\leavevmode\hypertarget{ref-ogradyPsychologyReplicationCrisis2020}{}%
+O'Grady, C., 2020, \& Pm, 2. (2020). Psychology's replication crisis inspires ecologists to push for more reliable research. \emph{Science}.
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-schonbrodtTrainingStudentsOpen2019}{}%
+Schönbrodt, F.
+(2019).
+Training students for the Open Science future.
+\emph{Nature Human Behaviour}, \emph{3}(10), 1031--1031.
+doi:\href{https://doi.org/10.1038/s41562-019-0726-z}{10.1038/s41562-019-0726-z}
 
@@
 
+\leavevmode\hypertarget{ref-wagenmakersAgendaPurelyConfirmatory2012}{}%
+Wagenmakers, E.-J., Wetzels, R., Borsboom, D., van der Maas, H.
+L.
+J., \& Kievit, R.
+A.
+(2012).
+An agenda for purely confirmatory research.
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 632--638.
+doi:\href{https://doi.org/10.1177/1745691612463078}{10.1177/1745691612463078}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2020). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the tidyverse.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+doi:\href{https://doi.org/10.21105/joss.01686}{10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2020). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-yongPsychologyReplicationCrisis2016}{}%
+Yong, E. (2016). Psychology's replication crisis can't be wished away. \emph{The Atlantic}.
+
+\leavevmode\hypertarget{ref-yongPsychologyReplicationCrisis2018}{}%
+Yong, E. (2018). Psychology's replication crisis is running out of excuses. \emph{The Atlantic}.
+
+\leavevmode\hypertarget{ref-andersonNormativeDissonanceScience2007}{}%
+Anderson, M.
+S., Martinson, B.
+C., \& De Vries, R.
+(2007).
+Normative dissonance in science: Results from a national survey of U.S.
+Scientists.
+\emph{Journal of Empirical Research on Human Research Ethics}, \emph{2}(4), 3--14.
+doi:\href{https://doi.org/10.1525/jer.2007.2.4.3}{10.1525/jer.2007.2.4.3}
+
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-baker500ScientistsLift2016}{}%
+Baker, M. (2016). 1,500 scientists lift the lid on reproducibility. \emph{Nature News}, \emph{533}(7604), 452. doi:\href{https://doi.org/10.1038/533452a}{10.1038/533452a}
+
+\leavevmode\hypertarget{ref-brandtReplicationRecipeWhat2014}{}%
+Brandt, M.
+J., IJzerman, H., Dijksterhuis, A., Farach, F.
+J., Geller, J., Giner-Sorolla, R., \ldots{} van 't Veer, A.
+(2014).
+The replication recipe: What makes for a convincing replication?
+\emph{Journal of Experimental Social Psychology}, \emph{50}, 217--224.
+doi:\href{https://doi.org/10.1016/j.jesp.2013.10.005}{10.1016/j.jesp.2013.10.005}
+
+\leavevmode\hypertarget{ref-chopikHowWhetherTeach2018}{}%
+Chopik, W.
+J., Bremner, R.
+H., Defever, A.
+M., \& Keller, V.
+N.
+(2018).
+How (and whether) to teach undergraduates about the replication crisis in psychological science.
+\emph{Teaching of Psychology}, \emph{45}(2), 158--163.
+doi:\href{https://doi.org/10.1177/0098628318762900}{10.1177/0098628318762900}
+
+\leavevmode\hypertarget{ref-graheHarnessingUndiscoveredResource2012}{}%
+Grahe, J.
+E., Reifman, A., Hermann, A.
+D., Walker, M., Oleson, K.
+C., Nario-Redmond, M., \& Wiebe, R.
+P.
+(2012).
+Harnessing the undiscovered resource of student research projects.
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 605--607.
+doi:\href{https://doi.org/10.1177/1745691612459057}{10.1177/1745691612459057}
+
+\leavevmode\hypertarget{ref-openscienceworkinggroup2017SurveyOpen2018}{}%
+Group, O. S. W. (2018). \emph{2017 survey on open research practices administered by the School of Psychology, Cardiff University}. Cardiff University.
+
+\leavevmode\hypertarget{ref-harrisUseReproducibleResearch2018}{}%
+Harris, J.
+K., Johnson, K.
+J., Carothers, B.
+J., Combs, T.
+B., Luke, D.
+A., \& Wang, X.
+(2018).
+Use of reproducible research practices in public health: A survey of public health analysts.
+\emph{PLOS ONE}, \emph{13}(9), e0202447.
+doi:\href{https://doi.org/10.1371/journal.pone.0202447}{10.1371/journal.pone.0202447}
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-jekelHowTeachOpen2020}{}%
+Jekel, M., Fiedler, S., Allstadt Torras, R., Mischkowski, D., Dorrough, A.
+R., \& Glöckner, A.
+(2020).
+How to teach open science principles in the undergraduate curriculumthe Hagen cumulative science project.
+\emph{Psychology Learning \& Teaching}, \emph{19}(1), 91--106.
+doi:\href{https://doi.org/10.1177/1475725719868149}{10.1177/1475725719868149}
+
+\leavevmode\hypertarget{ref-kleinInvestigatingVariationReplicability2014}{}%
+Klein, R.
+A., Ratliff, K.
+A., Vianello, M., Adams Jr., R.
+B., Bahník, Š., Bernstein, M.
+J., \ldots{} Nosek, B.
+A.
+(2014).
+Investigating variation in replicability: A ``many labs'' replication project.
+\emph{Social Psychology}, \emph{45}(3), 142--152.
+doi:\href{https://doi.org/10.1027/1864-9335/a000178}{10.1027/1864-9335/a000178}
+
+\leavevmode\hypertarget{ref-kleinManyLabsInvestigating2018}{}%
+Klein, R.
+A., Vianello, M., Hasselman, F., Adams, B.
+G., Adams, R.
+B., Alper, S., \ldots{} Nosek, B.
+A.
+(2018).
+Many labs 2: Investigating variation in replicability across samples and settings.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(4), 443--490.
+doi:\href{https://doi.org/10.1177/2515245918810225}{10.1177/2515245918810225}
+
+\leavevmode\hypertarget{ref-meyerPracticalTipsEthical2018}{}%
+Meyer, M.
+N.
+(2018).
+Practical tips for ethical data sharing.
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{1}(1), 131--144.
+doi:\href{https://doi.org/10.1177/2515245917747656}{10.1177/2515245917747656}
+
+\leavevmode\hypertarget{ref-R-here}{}%
+Müller, K. (2017). \emph{Here: A simpler way to find your files}. Retrieved from \url{https://CRAN.R-project.org/package=here}
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2020). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\hypertarget{ref-nosekPreregistrationRevolution2018}{}%
+Nosek, B.
+A., Ebersole, C.
+R., DeHaven, A.
+C., \& Mellor, D.
+T.
+(2018).
+The preregistration revolution.
+\emph{Proceedings of the National Academy of Sciences}, \emph{115}(11), 2600--2606.
+doi:\href{https://doi.org/10.1073/pnas.1708274114}{10.1073/pnas.1708274114}
+
+\leavevmode\hypertarget{ref-ogradyPsychologyReplicationCrisis2020}{}%
+O'Grady, C., 2020, \& Pm, 2. (2020). Psychology's replication crisis inspires ecologists to push for more reliable research. \emph{Science}.
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-schonbrodtTrainingStudentsOpen2019}{}%
+Schönbrodt, F.
+(2019).
+Training students for the Open Science future.
+\emph{Nature Human Behaviour}, \emph{3}(10), 1031--1031.
+doi:\href{https://doi.org/10.1038/s41562-019-0726-z}{10.1038/s41562-019-0726-z}
+
+\leavevmode\hypertarget{ref-simmons21WordSolution2012}{}%
+Simmons, J. P., Nelson, L. D., \& Simonsohn, U. (2012). \emph{A 21 word solution} (SSRN Scholarly Paper No. ID 2160588). Rochester, NY: Social Science Research Network.
+
+\leavevmode\hypertarget{ref-wagenmakersAgendaPurelyConfirmatory2012}{}%
+Wagenmakers, E.-J., Wetzels, R., Borsboom, D., van der Maas, H.
+L.
+J., \& Kievit, R.
+A.
+(2012).
+An agenda for purely confirmatory research.
+\emph{Perspectives on Psychological Science}, \emph{7}(6), 632--638.
+doi:\href{https://doi.org/10.1177/1745691612463078}{10.1177/1745691612463078}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2020). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the tidyverse.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+doi:\href{https://doi.org/10.21105/joss.01686}{10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2020). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H., \& Henry, L. (2020). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., Hester, J., \& Francois, R. (2018). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-yongPsychologyReplicationCrisis2016}{}%
+Yong, E. (2016). Psychology's replication crisis can't be wished away. \emph{The Atlantic}.
+
+\leavevmode\hypertarget{ref-yongPsychologyReplicationCrisis2018}{}%
+Yong, E. (2018). Psychology's replication crisis is running out of excuses. \emph{The Atlantic}.
+\end{cslreferences}
+
 \endgroup

### 2021-03-09 analysis/Manuscript.Rmd
start on calculating differences between norms

--- 2021-03-09 analysis/Manuscript.Rmd
@@
 ## Data analysis
-<!-- Can we move this to a reproducible code statement at the end? It works now -->
-
-We used `r cite_r("r-references.bib")` for all our analyses.
 
@@
 
+```{r, difference between norm and counternorm}
+
+# select columns that relate to norms & pivot it long
+norm_long <- df %>% 
+  select(c(id, ends_with("_norm"))) %>% 
+    pivot_longer (cols = ends_with("norm"),
+                names_to = "practice",
+                values_to = "norm rating")
+
+# remove "_norm" from the practice variables
+norm_long$practice = gsub(pattern = "_norm", replacement = "", x = norm_long$practice)
+
+# select columns that relate to counternorms
+cnorm_long <- df %>% 
+  select(c(id, ends_with("_cnorm"))) %>% 
+  pivot_longer (cols = ends_with("cnorm"),
+                names_to = "practice",
+                values_to = "cnorm rating")
+
+# remove "_cnorm" from the practice variables
+cnorm_long$practice = gsub(pattern = "_cnorm", replacement = "", x = cnorm_long$practice)
+
+# join the norm and counternorm tibbles
+norm_cnorm <- norm_long %>% inner_join(cnorm_long)
+
+# create a `diff` variable that is the counternorm subtracted from the norm
+norm_cnorm <- norm_cnorm %>% 
+  mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
+      dplyr::select(-(`id`)) # remove this now that I've confirmed it works
+
+norm_means <- norm_cnorm %>% 
+    dplyr::group_by(practice) %>%  
+    summarise(norm_mean = mean(`norm rating`, na.rm = TRUE), 
+              norm_sd = sd(`norm rating`, na.rm = TRUE), 
+              cnorm_mean = mean(`cnorm rating`, na.rm = TRUE), 
+              cnorm_sd = sd(`cnorm rating`, na.rm = TRUE), 
+              diff_mean = mean(`diff`, na.rm = TRUE), 
+              diff_sd = sd(`diff`, na.rm = TRUE)) %>% 
+  ungroup()
+
+# breadcrumb: I need to use papaja tables....
+# pull means & sd into the same column with (sd) in parentheses
+# headings should then be norm, counternorm, difference
+
+knitr::kable(norm_means,
+             caption = "Means (sd) for norms, counternorms, and the difference between the two for each of the practices",
+             digits = 2,
+             align = c('lcccccc'))
+
+# breadcrumbs: rename the practices so it's easier to read
+
+# I don't need this...
+# norm_means <- norm_cnorm %>% 
+    # select(-id) %>% 
+    # group_by(practice) %>%  
+    # mutate(norm_mean = mean(`norm rating`, na.rm = TRUE)) %>% 
+    # mutate(norm_sd = sd(`norm rating`, na.rm = TRUE)) %>% 
+    # mutate(cnorm_mean = mean(`cnorm rating`, na.rm = TRUE)) %>% 
+    # mutate(cnorm_sd = sd(`cnorm rating`, na.rm = TRUE)) %>% 
+    # mutate(diff_mean = mean(`diff`, na.rm = TRUE)) %>% 
+    # mutate(diff_sd = sd(`diff`, na.rm = TRUE))
+
+```
+
+```{r, eval=FALSE}
+# I'm sure there's a fancier way to subtract the counternorm from the norm, 
+  # but for now we will do this...
+
+norms <-  vars_select(names(df), ends_with('_norm'))
+cnorms <-  vars_select(names(df), ends_with('_cnorm'))
+
+miss_fun = function(x){
+  sum(is.na(x))
+}
+
+diff_fun = function(x, y){
+  (norms - cnorms)
+}
+
+diff_fun(x = norms, y = cnorms)
+
+df$diff <- apply(X = df[, ], MARGIN = 1, FUN = miss_fun)
+
+```
+
 # Discussion
+
+\newpage
+# Reproducible Code Statement
+
+We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2021-03-09 analysis/Manuscript.Rmd
Some updates to intro

--- 2021-03-09 analysis/Manuscript.Rmd
@@
 These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
-Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018).
-In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].
+Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices (e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018).
+In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
 These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 
-The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science.
-Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles.
+The most comprehensive set of principles for how science *ought* to be practiced are Merton's [@mertonNoteScienceDemocracy1942] norms of science.
+Scientists [@andersonNormativeDissonanceScience2007] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles - to at least some extent.
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.
@@
 First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018; @ogradyPsychologyReplicationCrisis2020].
-Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
-Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
+Many students may plausibly have some knowledge about replicability issues in psychology which they obtained prior to (or independently of) their formal studies.
+Teaching methods should thus be informed by some understanding of what students' typical pre-existing levels of knowledge are.
 
-Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
+<!--Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
 Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
@@
 
-Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice.
-In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices.
-Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
-Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
-It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions.
+#I've commented this paragraph out because on reflection I'm not sure it's a very strong argument, and the potential effect of teaching about replicability on levels of trust in psych science isn't really something we can directly address in this study.
+However, it was one of the only places where we really talked about the Chopik et al. 2018 paper, which probably needs more coverage.
+
+-->
+
+Second, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g., @duyguuygun-tuncLastNightWas2021].
+In other words, these is a possibility that students' naive conception of how science works may in some respects be closer to that embodied in recent reforms rather than "business as usual" practices.
+Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists [@andersonExtendingMertonianNorms2010].
+Furthermore, scientists typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
+It is thus possible that, for some students, teaching about reform might in some cases involve reinforcing "naive" assumptions.
 In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.
@@
 
-These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
-In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology.
-As such, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
-If, for example, undergraduate psychology students have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce should have some bearing on our choices in relation to sharing of manuscripts.
-This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
-In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
+Third, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology.<!--I assume this is true but cannot find any good numbers to pack it up!
+--> Furthermore, by serving as participants for course credit or cash payments [@bowenCashCreditCompensation2017], undergraduate psychology students provide the data underlying a substantial portion of psychological research.
+For example, @thalmayerNeglected95Revisited2021 found that 42% of studies reported in the *Journal of Personality and Social Psychology* in the period 2014 to 2018 were based on undergraduate student samples.
+As such, undergraduate students are both key consumers of psychological research as well as much-needed suppliers of the data used in psychological research.
+Therefore, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
+If, for example, undergraduate psychology students have a strong preference that journal articles are freely available, and that the data underlying claims is widely shared, these preference on the part of some of the key stakeholders in psychological research should have some bearing on our willingness to engage in these practices.
 
-<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? -->
+<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch?
+9Mar: On reflection I think it's kinda an ok argument, albeit we need more evidence for the claims in it. 
+I almost want to phrase it as saying that "Undergraduate students are both our most important customers and our most important suppliers of data"...
+-Matt
+-->
+
+These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students know and believe about these topics already.
+Currently, relatively little is know about undergraduate students' beliefs about replicability and open science practices.
+A study of by @chopikHowWhetherTeach2018 (focused on the effect of a one-hour lecture about open science) found that students tended to endorse pro-replicability/open science beliefs after the lecture (e.g., 92.7% thought it was "very" or "extremely" important that researchers "make data publicly available so that results can be verified by other researchers").
+However, this study was obviously not
 

### 2021-03-09 analysis/Manuscript.Rmd
Drafting method section
Added the three measures to the Method section

--- 2021-03-09 analysis/Manuscript.Rmd
@@
 
+### Open Science Norms and Counternorms
+
+Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
+Anderson et al., 2007).
+The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total.
+For example, the practice of posting article preprints was evaluated with the pro-open science item, "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read, "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
+
+### Norms in Practice
+
+We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world.
+To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices named above.
+For example, "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." Participants were given a slider bar ranging from 0% to 100% to record their estimate.
+
+### Beliefs About Replications
+
+Participants' beliefs about the replicabilty of results in psychological science were indexed by two questions.
+The first asked participants to "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+We call repeating a study like this a “replication study”.
+At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?” Estimates were recorded using a slider bar ranging from 0% to 100%.
+The second question asked participants whether they had heard of the replication crisis.
+For those who said they had, two open-ended
+
 ## Procedure

### 2021-03-09 analysis/Manuscript.Rmd

@@
 
-```{r, difference between norm & counternorm, eval = FALSE}
+# Results
 
-# select all columns that relate to norms & counternorms
-diff <- df %>% select(c(id, ends_with("norm")))
+```{r, difference between norm and counternorm}
 
-means <- diff %>% 
-  sapply(mean, na.rm = TRUE)
+# select columns that relate to norms & pivot it long
+norm_long <- df %>% 
+  select(c(id, ends_with("_norm"))) %>% 
+    pivot_longer (cols = ends_with("norm"),
+                names_to = "practice",
+                values_to = "norm rating")
 
-knitr::kable(means)
-
-# select columns that relate to norms
-norms <- df %>% select(c(id, ends_with("_norm")))
+# remove "_norm" from the practice variables
+norm_long$practice = gsub(pattern = "_norm", replacement = "", x = norm_long$practice)
 
 # select columns that relate to counternorms
-cnorms <- df %>% select(c(id, ends_with("_cnorm")))
+cnorm_long <- df %>% 
+  select(c(id, ends_with("_cnorm"))) %>% 
+  pivot_longer (cols = ends_with("cnorm"),
+                names_to = "practice",
+                values_to = "cnorm rating")
 
-# breadcrumbs - pivot long
+# remove "_cnorm" from the practice variables
+cnorm_long$practice = gsub(pattern = "_cnorm", replacement = "", x = cnorm_long$practice)
 
-norm_long <- norms %>% 
-  pivot_longer (cols = ends_with("norm"),
-                names_to = "practice",
-                values_to = "rating") 
-  str_remove(norm_long, "_norm")
+# join the norm and counternorm tibbles
+norm_cnorm <- norm_long %>% inner_join(cnorm_long)
 
-norm_wide <- diff %>% 
-  pivot_wider(names_from = ends_with("_norm"),
-              values_from = c(ends_with("_norm"), ends_with("_cnorm"))
-)
+# create a `diff` variable that is the counternorm subtracted from the norm
+norm_cnorm <- norm_cnorm %>% 
+  mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
+      dplyr::select(-(`id`)) # remove this now that I've confirmed it works
+
+norm_means <- norm_cnorm %>% 
+    dplyr::group_by(practice) %>%  
+    summarise(norm_mean = mean(`norm rating`, na.rm = TRUE), 
+              norm_sd = sd(`norm rating`, na.rm = TRUE), 
+              cnorm_mean = mean(`cnorm rating`, na.rm = TRUE), 
+              cnorm_sd = sd(`cnorm rating`, na.rm = TRUE), 
+              diff_mean = mean(`diff`, na.rm = TRUE), 
+              diff_sd = sd(`diff`, na.rm = TRUE)) %>% 
+  ungroup()
+
+# breadcrumb: I need to use papaja tables....
+# pull means & sd into the same column with (sd) in parentheses
+# headings should then be norm, counternorm, difference
+
+knitr::kable(norm_means,
+             caption = "Means (sd) for norms, counternorms, and the difference between the two for each of the practices",
+             digits = 2,
+             align = c('lcccccc'))
+
+# breadcrumbs: rename the practices so it's easier to read
+
+# I don't need this...
+# norm_means <- norm_cnorm %>% 
+    # select(-id) %>% 
+    # group_by(practice) %>%  
+    # mutate(norm_mean = mean(`norm rating`, na.rm = TRUE)) %>% 
+    # mutate(norm_sd = sd(`norm rating`, na.rm = TRUE)) %>% 
+    # mutate(cnorm_mean = mean(`cnorm rating`, na.rm = TRUE)) %>% 
+    # mutate(cnorm_sd = sd(`cnorm rating`, na.rm = TRUE)) %>% 
+    # mutate(diff_mean = mean(`diff`, na.rm = TRUE)) %>% 
+    # mutate(diff_sd = sd(`diff`, na.rm = TRUE))
+
 ```
@@
 
-# Results
-
 # Discussion

### 2021-03-09 analysis/Manuscript.Rmd
One para amended slightly

@@
 #I've commented this paragraph out because on reflection I'm not sure it's a very strong argument, and the potential effect of teaching about replicability on levels of trust in psych science isn't really something we can directly address in this study.
-However, it was one of the only places where we really talked about the Chopik et al. 2018 paper, which probably needs more coverage.
 
@@
 
-<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch?
-9Mar: On reflection I think it's kinda an ok argument, albeit we need more evidence for the claims in it. 
-I almost want to phrase it as saying that "Undergraduate students are both our most important customers and our most important suppliers of data"...
--Matt
--->
-
 These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students know and believe about these topics already.
@@
 A study of by @chopikHowWhetherTeach2018 (focused on the effect of a one-hour lecture about open science) found that students tended to endorse pro-replicability/open science beliefs after the lecture (e.g., 92.7% thought it was "very" or "extremely" important that researchers "make data publicly available so that results can be verified by other researchers").
-However, this study was obviously not
+However, this study was aimed primarily at estimating the effect of the lecture rather than describing students knowledge and beliefs per se.
+@bottesiniParticipantsCareIf2019 plan a registered report focusing on participants' (including undergraduate students') attitudes to p-hacking, but the final report has not yet been published.
+In sum, little is currently known about undergraduate psychology students' beliefs about replicability and open science.
 

### 2021-03-09 preprocessing/preprocessing_degrees.R
WIP coding for university, degree, and major coding

@@ -67,7 +67,7 @@ df <- df %>%
   )
 
 ## Recode degrees using the rule below
-# Note: hons and advanced degrees are collapsed into the more generic degree type
+# Note: hons and advanced degrees are collapsed into the more generic degree type (e.g. BPsych and BPsych Hons are both categorised as BPsych)
 
 df <- df %>%
   mutate(degree_recoded = toTitleCase(degree)) %>%

### 2021-03-24 analysis/Manuscript.Rmd
Updated with panel figure

@@
 library(tidyverse)
+library(psych) #for correlation matrices
+library(tidyselect)
 
@@
 
+ \@ref(tab:chunk-name)
+
 ```{r, difference between norm and counternorm}
@@
 
-diff_fun(x = norms, y = cnorms)
+diff_fun(x = norms, y = cnorms) #throws error non-numeric argument to binary operator
 
 df$diff <- apply(X = df[, ], MARGIN = 1, FUN = miss_fun)
+
+```
+
+```{r correlation_matrix}
+#pairs.panel etc. won't really work because there are too many variables
+#And we only need corrs between matched pairs
+#So doing this a bit more manually
+layout(matrix(1:8, ncol = 4))
+
+plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "Critical counternorm", ylab = "Critical norm")
+abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))
+
+plot(df$prereg_norm ~ jitter(df$prereg_cnorm), ylab = "Prereg norm", xlab = "Prereg counternorm")
+abline(lm(df$prereg_norm ~ df$prereg_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$prereg_norm, df$prereg_cnorm),2)))
+
+plot(df$reg_report_norm ~ jitter(df$reg_report_cnorm), ylab = "Reg Reports norm", xlab = "Reg Reports counternorm")
+abline(lm(df$reg_report_norm ~ df$reg_report_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$reg_report_norm, df$reg_report_cnorm),2)))
+
+plot(df$phack_norm ~ jitter(df$phack_cnorm), ylab = "p-hacking rnorm", xlab = "p-hacking counternorm")
+#potential confusion here about direction of phrasing (pro p-hacking = counternorm?)
+abline(lm(df$phack_norm ~ df$phack_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$phack_cnorm, df$phack_norm),2)))
+
+plot(df$hark_norm ~ jitter(df$hark_cnorm), ylab = "HARKing norm", xlab = "HARKing counternorm")
+abline(lm(df$hark_norm ~ df$hark_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$hark_cnorm, df$hark_norm),2)))
+
+plot(df$info_for_rep_norm ~ jitter(df$info_for_rep_cnorm), ylab = "Replicability norm", xlab = "Replicability counternorm")
+abline(lm(df$info_for_rep_norm ~ df$info_for_rep_cnorm), col = "blue")
+legend(x='right', legend=paste('Cor =', round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)))
+
+plot(df$preprint_norm ~ jitter(df$preprint_cnorm), ylab = "Preprints norm", xlab = "Preprints counternorm")
+abline(lm(df$preprint_norm ~ df$preprint_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$preprint_norm, df$preprint_cnorm,
+                                                       use = "pairwise.complete.obs"),2)))
+
+plot(df$open_materials_norm ~ jitter(df$open_materials_cnorm), ylab = "Open materials norm", xlab = "Open materials counternorm")
+abline(lm(df$open_materials_norm ~ df$open_materials_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_materials_norm, df$open_materials_cnorm, use = "pairwise.complete.obs"),2)))
+
+plot(df$open_data_norm ~ jitter(df$open_data_cnorm), ylab = "Open data norm", xlab = "Open data counternorm")
+abline(lm(df$open_data_norm ~ df$open_data_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_data_norm, df$open_data_cnorm),2)))
+
+plot(df$open_access_norm ~ jitter(df$open_access_cnorm), ylab = "Open access norm", xlab = "Open access counternorm")
+abline(lm(df$open_access_norm ~ df$open_access_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$open_access_norm, df$open_access_cnorm),2)))
 

### 2021-03-24 analysis/Manuscript.Rmd
tidy up means table

--- 2021-03-09 analysis/Manuscript.Rmd
@@
 library(tidyverse)
+library(finalfit) # to keep trailing zeros
 
@@
 set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
+knitr::opts_chunk$set(
+  cache.extra = knitr::rand_seed,
+  results = 'as.is')
 ```
@@
 These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
-Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices (e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018).
-In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
+Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018).
+In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].
 These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 
-The most comprehensive set of principles for how science *ought* to be practiced are Merton's [@mertonNoteScienceDemocracy1942] norms of science.
-Scientists [@andersonNormativeDissonanceScience2007] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles - to at least some extent.
+The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science.
+Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles.
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.
@@
 First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018; @ogradyPsychologyReplicationCrisis2020].
-Many students may plausibly have some knowledge about replicability issues in psychology which they obtained prior to (or independently of) their formal studies.
-Teaching methods should thus be informed by some understanding of what students' typical pre-existing levels of knowledge are.
+Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
+Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
 
-<!--Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
+Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
 Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
@@
 
-#I've commented this paragraph out because on reflection I'm not sure it's a very strong argument, and the potential effect of teaching about replicability on levels of trust in psych science isn't really something we can directly address in this study.
-However, it was one of the only places where we really talked about the Chopik et al. 2018 paper, which probably needs more coverage.
-
--->
-
-Second, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g., @duyguuygun-tuncLastNightWas2021].
-In other words, these is a possibility that students' naive conception of how science works may in some respects be closer to that embodied in recent reforms rather than "business as usual" practices.
-Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists [@andersonExtendingMertonianNorms2010].
-Furthermore, scientists typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
-It is thus possible that, for some students, teaching about reform might in some cases involve reinforcing "naive" assumptions.
+Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice.
+In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices.
+Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
+Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
+It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions.
 In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.
@@
 
-Third, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology.<!--I assume this is true but cannot find any good numbers to pack it up!
---> Furthermore, by serving as participants for course credit or cash payments [@bowenCashCreditCompensation2017], undergraduate psychology students provide the data underlying a substantial portion of psychological research.
-For example, @thalmayerNeglected95Revisited2021 found that 42% of studies reported in the *Journal of Personality and Social Psychology* in the period 2014 to 2018 were based on undergraduate student samples.
-As such, undergraduate students are both key consumers of psychological research as well as much-needed suppliers of the data used in psychological research.
-Therefore, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
-If, for example, undergraduate psychology students have a strong preference that journal articles are freely available, and that the data underlying claims is widely shared, these preference on the part of some of the key stakeholders in psychological research should have some bearing on our willingness to engage in these practices.
+These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
+In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology.
+As such, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
+If, for example, undergraduate psychology students have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce should have some bearing on our choices in relation to sharing of manuscripts.
+This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
+In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
 
-<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch?
-9Mar: On reflection I think it's kinda an ok argument, albeit we need more evidence for the claims in it. 
-I almost want to phrase it as saying that "Undergraduate students are both our most important customers and our most important suppliers of data"...
--Matt
--->
-
-These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students know and believe about these topics already.
-Currently, relatively little is know about undergraduate students' beliefs about replicability and open science practices.
-A study of by @chopikHowWhetherTeach2018 (focused on the effect of a one-hour lecture about open science) found that students tended to endorse pro-replicability/open science beliefs after the lecture (e.g., 92.7% thought it was "very" or "extremely" important that researchers "make data publicly available so that results can be verified by other researchers").
-However, this study was obviously not
+<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? -->
 
@@
 
+# [breadcrumbs] 
  # once qual responses are coded, I will need to return here to 
@@
 
-### Open Science Norms and Counternorms
-
-Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
-Anderson et al., 2007).
-The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total.
-For example, the practice of posting article preprints was evaluated with the pro-open science item, "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read, "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
-
-### Norms in Practice
-
-We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world.
-To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices named above.
-For example, "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." Participants were given a slider bar ranging from 0% to 100% to record their estimate.
-
-### Beliefs About Replications
-
-Participants' beliefs about the replicabilty of results in psychological science were indexed by two questions.
-The first asked participants to "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
-We call repeating a study like this a “replication study”.
-At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?” Estimates were recorded using a slider bar ranging from 0% to 100%.
-The second question asked participants whether they had heard of the replication crisis.
-For those who said they had, two open-ended
-
 ## Procedure
@@
 # Results
+
+In line with our preregisterd analysis plan, we cacluated the difference in means
+between responses to each norm item and its accompanying counternorm, along with 
+95% confidence intervals. For this analysis, we removed three cases with missing values. 
+Table XX displays the means and standard deviations for each norm, counternorm, 
+and the difference values.
 
@@
   mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
+    drop_na() %>% # drop the three NA values
       dplyr::select(-(`id`)) # remove this now that I've confirmed it works
 
-norm_means <- norm_cnorm %>% 
+# get the n values for each of the practices
+prac_counts <- norm_cnorm %>% 
     dplyr::group_by(practice) %>%  
-    summarise(norm_mean = mean(`norm rating`, na.rm = TRUE), 
-              norm_sd = sd(`norm rating`, na.rm = TRUE), 
-              cnorm_mean = mean(`cnorm rating`, na.rm = TRUE), 
-              cnorm_sd = sd(`cnorm rating`, na.rm = TRUE), 
-              diff_mean = mean(`diff`, na.rm = TRUE), 
-              diff_sd = sd(`diff`, na.rm = TRUE)) %>% 
+    count()
+
+# calculate means
+prac_ms_sds <- norm_cnorm %>% 
+    dplyr::group_by(practice) %>%  
+    summarise(norm_mean = mean(`norm rating`), 
+              norm_sd = sd(`norm rating`),
+              cnorm_mean = mean(`cnorm rating`), 
+              cnorm_sd = sd(`cnorm rating`),
+              diff_mean = mean(`diff`), 
+              diff_sd = sd(`diff`)) %>% 
   ungroup()
+
+# join the n values with the means
+prac_means <- prac_counts %>% inner_join(prac_ms_sds)
+
+# calculate 95% CIs
+error <- qnorm(0.975) * prac_means$diff_sd/sqrt(prac_means$n)
+prac_means$lower <- prac_means$diff_mean - error
+prac_means$upper <- prac_means$diff_mean + error
+
+# combine means & SDs
+prac_means$Norm <- paste0(round_tidy(prac_means$norm_mean,2),
+                          " (", 
+                          round_tidy(prac_means$norm_sd,2), 
+                          ")")
+prac_means$Counternorm <- paste0(round_tidy(prac_means$cnorm_mean,2), 
+                            " (", 
+                            round_tidy(prac_means$cnorm_sd,2), 
+                            ")")
+prac_means$Difference <- paste0(round_tidy(prac_means$diff_mean,2), 
+                            " (", 
+                            round_tidy(prac_means$diff_sd,2),
+                            ")", 
+                            " [",
+                            round_tidy(prac_means$lower,2),
+                            ", ", 
+                            round_tidy(prac_means$upper,2),
+                            "]")
+
+# clean it up into a new dataframe
+practice_means <- prac_means %>% 
+  select(practice,Norm, Counternorm, Difference)
 
@@
 # pull means & sd into the same column with (sd) in parentheses
-# headings should then be norm, counternorm, difference
+# first level headings should then be norm, counternorm, difference
 
-knitr::kable(norm_means,
+knitr::kable(practice_means,
              caption = "Means (sd) for norms, counternorms, and the difference between the two for each of the practices",
              digits = 2,
-             align = c('lcccccc'))
+             align = c('lccc'))
 

### 2021-03-24 analysis/Manuscript.Rmd
Methods section tweak
Tweaking measures and writing procedures.

--- 2021-03-24 analysis/Manuscript.Rmd
@@
 
-Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
+Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
 Anderson et al., 2007).
+<!-- Mention here our discussions workshopping of common open science norms at SIPs?
+!
+-->
 The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
 Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total.
-For example, the practice of posting article preprints was evaluated with the pro-open science item, "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read, "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
+For example, the practice of posting article preprints was evaluated with the pro-open science item: "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read: "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
 
@@
 
-Participants' beliefs about the replicabilty of results in psychological science were indexed by two questions.
-The first asked participants to "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
-We call repeating a study like this a “replication study”.
-At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?” Estimates were recorded using a slider bar ranging from 0% to 100%.
-The second question asked participants whether they had heard of the replication crisis.
-For those who said they had, two open-ended
+Participants' beliefs about the replicabilty of results in psychological science were indexed by two questions. The first asked participants to, 
+> "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+We call repeating a study like this a 'replication study.' At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?”
+
+Estimates were recorded using a slider bar ranging from 0% to 100%. 
+A second question asked participants whether they had heard of the replication crisis.
+Those who had heard of the replication crisis were asked two additional open-ended questions.
+First, they were asked to describe what the replication crisis is.
+Second, they were asked which scientific disciplines were most affected by the replication crisis.
 
 ## Procedure
+
+Collaborators/Contributors/Colleagues from ## tertiary institutions in Australia (n=), New Zealand (n=), the UK (n=), and the USA (n=) invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics (CITE?).
+An invitation was sent to participants via email or a course website 1-2 weeks before their course began.
+After completing demographic information, participants completed measures of Open Science Norms and Counternorms, Norms in Practice, and Beliefs about Replications in that order.
+At the conclusion of the study participants were invited to share any comments about the survey before they were thanked for their participation and provided an informative debriefing about the aims of the study and links to further reading about open science practices in psychology.
+The survey took most participants approximately #-# minutes to complete.
 

### 2021-03-30 analysis/Manuscript.Rmd
unknown changes...

--- 2021-03-24 analysis/Manuscript.Rmd
@@
 library(finalfit) # to keep trailing zeros
+library(psych) #for correlation matrices
+library(tidyselect)
 
@@
 
+Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
+Anderson et al., 2007).
+<!-- Mention here our discussions workshopping of common open science norms at SIPs?
+!
+-->
+The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total.
+For example, the practice of posting article preprints was evaluated with the pro-open science item: "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read: "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
+
+### Norms in Practice
+
+We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world.
+To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices named above.
+For example, "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." Participants were given a slider bar ranging from 0% to 100% to record their estimate.
+
+### Beliefs About Replications
+
+Participants' beliefs about the replicabilty of results in psychological science were indexed by two questions. The first asked participants to, 
+> "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+We call repeating a study like this a 'replication study.' At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?”
+
+Estimates were recorded using a slider bar ranging from 0% to 100%. 
+A second question asked participants whether they had heard of the replication crisis.
+Those who had heard of the replication crisis were asked two additional open-ended questions.
+First, they were asked to describe what the replication crisis is.
+Second, they were asked which scientific disciplines were most affected by the replication crisis.
+
 ## Procedure
+
+Collaborators/Contributors/Colleagues from ## tertiary institutions in Australia (n=), New Zealand (n=), the UK (n=), and the USA (n=) invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics (CITE?).
+An invitation was sent to participants via email or a course website 1-2 weeks before their course began.
+After completing demographic information, participants completed measures of Open Science Norms and Counternorms, Norms in Practice, and Beliefs about Replications in that order.
+At the conclusion of the study participants were invited to share any comments about the survey before they were thanked for their participation and provided an informative debriefing about the aims of the study and links to further reading about open science practices in psychology.
+The survey took most participants approximately #-# minutes to complete.
 
@@
 and the difference values.
+
+ \@ref(tab:chunk-name)
 
@@
 
-# clean it up into a new dataframe
+# clean it up into a new dataframe with only the columns we need
 practice_means <- prac_means %>% 
@@
 
-# breadcrumb: I need to use papaja tables....
-# pull means & sd into the same column with (sd) in parentheses
-# first level headings should then be norm, counternorm, difference
+# breadcrumb: I need to use apa_tables.... (in line with papaja)
+# pull means & sd into the same column with (sd) in parentheses [done!]
+# headings should then be norm, counternorm, difference [done!]
 
@@
 
-# I don't need this...
-# norm_means <- norm_cnorm %>% 
-    # select(-id) %>% 
-    # group_by(practice) %>%  
-    # mutate(norm_mean = mean(`norm rating`, na.rm = TRUE)) %>% 
-    # mutate(norm_sd = sd(`norm rating`, na.rm = TRUE)) %>% 
-    # mutate(cnorm_mean = mean(`cnorm rating`, na.rm = TRUE)) %>% 
-    # mutate(cnorm_sd = sd(`cnorm rating`, na.rm = TRUE)) %>% 
-    # mutate(diff_mean = mean(`diff`, na.rm = TRUE)) %>% 
-    # mutate(diff_sd = sd(`diff`, na.rm = TRUE))
-
 ```
 
-```{r, eval=FALSE}
-# I'm sure there's a fancier way to subtract the counternorm from the norm, 
-  # but for now we will do this...
+```{r correlation_matrix}
+#pairs.panel etc. won't really work because there are too many variables
+#And we only need corrs between matched pairs
+#So doing this a bit more manually
+layout(matrix(1:8, ncol = 4))
 
-norms <-  vars_select(names(df), ends_with('_norm'))
-cnorms <-  vars_select(names(df), ends_with('_cnorm'))
+plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "Critical counternorm", ylab = "Critical norm")
+abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))
 
-miss_fun = function(x){
-  sum(is.na(x))
-}
+plot(df$prereg_norm ~ jitter(df$prereg_cnorm), ylab = "Prereg norm", xlab = "Prereg counternorm")
+abline(lm(df$prereg_norm ~ df$prereg_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$prereg_norm, df$prereg_cnorm),2)))
 
-diff_fun = function(x, y){
-  (norms - cnorms)
-}
+plot(df$reg_report_norm ~ jitter(df$reg_report_cnorm), ylab = "Reg Reports norm", xlab = "Reg Reports counternorm")
+abline(lm(df$reg_report_norm ~ df$reg_report_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$reg_report_norm, df$reg_report_cnorm),2)))
 
-diff_fun(x = norms, y = cnorms)
+plot(df$phack_norm ~ jitter(df$phack_cnorm), ylab = "p-hacking rnorm", xlab = "p-hacking counternorm")
+#potential confusion here about direction of phrasing (pro p-hacking = counternorm?)
+abline(lm(df$phack_norm ~ df$phack_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$phack_cnorm, df$phack_norm),2)))
 
-df$diff <- apply(X = df[, ], MARGIN = 1, FUN = miss_fun)
+plot(df$hark_norm ~ jitter(df$hark_cnorm), ylab = "HARKing norm", xlab = "HARKing counternorm")
+abline(lm(df$hark_norm ~ df$hark_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$hark_cnorm, df$hark_norm),2)))
+
+plot(df$info_for_rep_norm ~ jitter(df$info_for_rep_cnorm), ylab = "Replicability norm", xlab = "Replicability counternorm")
+abline(lm(df$info_for_rep_norm ~ df$info_for_rep_cnorm), col = "blue")
+legend(x='right', legend=paste('Cor =', round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)))
+
+plot(df$preprint_norm ~ jitter(df$preprint_cnorm), ylab = "Preprints norm", xlab = "Preprints counternorm")
+abline(lm(df$preprint_norm ~ df$preprint_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$preprint_norm, df$preprint_cnorm,
+                                                       use = "pairwise.complete.obs"),2)))
+
+plot(df$open_materials_norm ~ jitter(df$open_materials_cnorm), ylab = "Open materials norm", xlab = "Open materials counternorm")
+abline(lm(df$open_materials_norm ~ df$open_materials_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_materials_norm, df$open_materials_cnorm, use = "pairwise.complete.obs"),2)))
+
+plot(df$open_data_norm ~ jitter(df$open_data_cnorm), ylab = "Open data norm", xlab = "Open data counternorm")
+abline(lm(df$open_data_norm ~ df$open_data_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_data_norm, df$open_data_cnorm),2)))
+
+plot(df$open_access_norm ~ jitter(df$open_access_cnorm), ylab = "Open access norm", xlab = "Open access counternorm")
+abline(lm(df$open_access_norm ~ df$open_access_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$open_access_norm, df$open_access_cnorm),2)))
 

### 2021-03-30 analysis/Manuscript.Rmd
calculate correlations

@@
 library(tidyselect) 
+library(psychometric) # for correlation confidence intervals
 
@@
 
- \@ref(tab:chunk-name)
+```{r, difference between norm and counternorm}
 
-```{r, difference between norm and counternorm}
+ # \@ref(tab:chunk-name)  [JB removed this from the text above to see if that solves
+  # our table caption issue]
 
@@
 
-# breadcrumb: I need to use apa_tables.... (in line with papaja)
+# ADD CORRELATIONS (per participant, use df)
+
+critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
+
+# I'm sure there's a way to automate it, but I can't figure it out...just hard code it
+# all_cnorms <- df %>% 
+#     select(ends_with("_cnorm"))
+#   
+# corr <- round(cor(all_), ends_with("_cnorm"),2)))
+# 
+# 
+#   all_norms %>% 
+#     cor(ends_with("_norm"), ends_with("_cnorm"))
+#   
+#  
+#   cor(all_norms, method = "pearson") %>% 
+#   as.tibble()
+# 
+# all_correlation <- df %>% 
+#     select(c(ends_with("_norm"), ends_with("_cnorm"))) %>% 
+#   mutate(item = row.names(.)) %>% 
+#   select(item, everything())
+
+# this code works, but I must be able to do this all at once...
+
+# breadcrumbs: when I come back to this, I need to combine these in a tibble
+  # and then join it with the existing table...
+critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
+critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
+
+hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
+hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
+
+info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
+info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
+
+open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
+open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
+
+open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
+open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
+
+open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
+open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
+
+phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
+phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
+
+preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
+preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
+
+prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
+prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)
+
+rbind()
+
+# breadcrumbs: 
+# I need to use apa_tables.... (in line with papaja)
 # pull means & sd into the same column with (sd) in parentheses [done!]
 # headings should then be norm, counternorm, difference [done!]
+# add correlations with 95% CIs 
+# update practice descriptions so they make sense to readers
 
@@
              align = c('lccc'))
-
-# breadcrumbs: rename the practices so it's easier to read
 
@@
 
-plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "Critical counternorm", ylab = "Critical norm")
+plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "critical counternorm", ylab = "critical norm")
 abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")

### 2021-04-01 analysis/Manuscript.Rmd
tidy version of correlations

@@
 In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].
-These initiatives help engrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
+These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 
@@
 Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
-In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of old norms.
+In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.
 
 Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
-Keeping textbooks and other instructional materials up to date is  difficult when supposedly well-established findings are being contradicted by new replications emerging at a rapid pace.
-Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that thay may produce research that is even more replicable than that of previous generations.
+Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that they may produce research that is even more replicable than that of previous generations.
 Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge.
@@
 Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
-Could an over-emphasis on problems with replicability leave such students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
-It is therefore important to determine what levels of trust in psychological research (and its replicability) are prevalent in incoming undergraduate students.
-In their examination of the usefulness of a one-hour lecture about the replication crisis, @chopikHowWhetherTeach2018 found that undergraduate students trusted the results of studies by psychologists less after the lecture than they did before it, although the effect size was fairly small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
+An over-emphasis on problems with replicability could leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
+For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis[^1].
+[^1]: Notably, the effect of the lecture on trust of psychological stuides was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
 
 Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice.
-In other words, students' naive conception of how science works may in some ways be closer to that embodied in recent reforms rather than "business as usual" practices.
+In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices.
 Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
 Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
-It is thus possible that, for some students, teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions.
+Therefore - for some students - teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions.
 In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.
@@
 
-<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? -->
+<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? 
+MP: Maybe a stretch, but given we have a good rationale already, it might be worth trying to keep it. We may need a reference to two to help make some of the claims more concrete though.-->
 
@@
 
+### Open Science Norms and Counternorms
+
 Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
@@
 The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total.
-For example, the practice of posting article preprints was evaluated with the pro-open science item: "Deborah should post a manuscript describing the Findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." The counter-open preprint item read: "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal." Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total (see Table X).
+Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
 
-### Norms in Practice
+<!-- Add Table X of norms and counternorms statements that map to each practice -->
+
+### Beliefs About the Practice of Psychological Science
 
 We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world.
-To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices named above.
-For example, "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal." Participants were given a slider bar ranging from 0% to 100% to record their estimate.
+To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices (see Table XX).
+Participants were given a slider bar ranging from 0% to 100% to record their estimate.
+
+<!-- Add Table XX of 10 belief statements -->
 
@@
 
-In line with our preregisterd analysis plan, we cacluated the difference in means
+In line with our preregisterd analysis plan, we calculated the difference in means
 between responses to each norm item and its accompanying counternorm, along with 
@@
 
+\@ref(tab:chunk-name)
+
 ```{r, difference between norm and counternorm}
-
- # \@ref(tab:chunk-name)  [JB removed this from the text above to see if that solves
-  # our table caption issue]
 
@@
 norm_long <- df %>% 
-  select(c(id, ends_with("_norm"))) %>% 
+  dplyr::select(c(id, ends_with("_norm"))) %>% 
     pivot_longer (cols = ends_with("norm"),
@@
 cnorm_long <- df %>% 
-  select(c(id, ends_with("_cnorm"))) %>% 
+  dplyr::select(c(id, ends_with("_cnorm"))) %>% 
   pivot_longer (cols = ends_with("cnorm"),
@@
 # create a `diff` variable that is the counternorm subtracted from the norm
-norm_cnorm <- norm_cnorm %>% 
+norm_cnorm_long <- norm_cnorm %>% 
   mutate (diff = (`norm rating` - `cnorm rating`)) %>% 
@@
 # get the n values for each of the practices
-prac_counts <- norm_cnorm %>% 
+prac_counts <- norm_cnorm_long %>% 
     dplyr::group_by(practice) %>%  
-    count()
+    count() %>% 
+  ungroup()
 
 # calculate means
-prac_ms_sds <- norm_cnorm %>% 
+prac_ms_sds <- norm_cnorm_long %>% 
     dplyr::group_by(practice) %>%  
@@
 # combine means & SDs
+prac_means$Practice <- prac_means$practice
 prac_means$Norm <- paste0(round_tidy(prac_means$norm_mean,2),
@@
 practice_means <- prac_means %>% 
-  select(practice,Norm, Counternorm, Difference)
+  dplyr::select(Practice, Norm, Counternorm, Difference)
 
@@
 
+# notes for the correlations....
+# just the correlation with CI
 critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
+critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
+
+#correlation test with CI and p-values in a clean tibble
+critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
+tidy(critical_corr_test)
+
+cor(df$`norm rating`, df$`cnorm rating`)
+
+# use this tutorial to try to get the correlations for each practice (using the long data)
+# https://cran.r-project.org/web/packages/broom/vignettes/broom_and_dplyr.html
+
+# this will create a tibble for each practice and then calculate
+
+# calculates the correlation test for each tibble & then tidies it up
+corr <- norm_cnorm_long %>% 
+  nest(data = -practice) %>% # create a tibble for each practice
+  mutate (test = map(data, ~ cor.test(.x$`norm rating`, .x$`cnorm rating`)), 
+          tidied = map(test,tidy)) %>% # run the corr & tidy it
+  unnest(tidied) # unnest it to look at the results
+
+# breadcrumbs: keep the values that I need from this tibble
+# use p_tidy? to clean up the pvalues
+# round the corr & CI
+# join with the practice_means tibble & turn into a table
 
@@
 # breadcrumbs: when I come back to this, I need to combine these in a tibble
-  # and then join it with the existing table...
+  # and then join it with the existing table...I probably need to mutate, but I 
+  # need to sort out how to do this...
+
+# practice_corr <- practice_means %>% 
+  # mutate()
+
 critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)

### 2021-04-01 analysis/Manuscript.Rmd

@@
 
+In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm.
+However, the extent to which participants endorsed open science norms varied very substantially across different practices.
+Participants tended to agree or strongly agree that p-hacking should be avoided, and that researchers should provide sufficient information about studies to permit replicability.
+On the other hand, they were very skeptical of the practice of sharing preprints prior to peer review, and to a lesser extent about sharing open data.
+There also a degree of equivocation about registered reports, with very similar levels of agreement with both norm and counternorm for this item.
+This may be relatively unsurprising, given that the registered reports are perhaps the most recent innovation in the list of practices.
+
+Unsurprisingly, there were fairly substantial negative correlations between the norm and counternorm pairs, although this was not the case for all pairs: For the norm and counternorm items relating to preregistrations, the correlation was `r sprintf('%.2f', cor(df$prereg_norm, df$prereg_cnorm))`.
+Similarly for the norm and counternorm items relating to HARKing, the correlation was negative but very small.
+
 ```{r, difference between norm and counternorm}
@@
 
+## Norms in practice
+Participants were also asked to estimate the proportion of psychology studies estimated globally which apply ten practices (corresponding to the ten norm-counternorm pairs) .
+For many of these practices, participants estimates were near the midpoint of 50%.
+This said, participants perceived some practices as being applied relatively infrequently: For example, the mean esitmate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
+Participants seemed to perceived that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
+It is perhaps fair to say that participants mean estimate that `r paste(round(mean(df$detailed_methodology, na.rm = TRUE), 2), "%", sep = "")` of studies have this characteristic represents a rather optimistic projection.
+
+<!-- There's a key point for the discussion here, I think, in that the fact that many participants guessed near 50% for these practices suggests that students may have little idea of the prevalence of these practices in reality, and certainly education is needed on that point.
+-->
+
+## The replication crisis
+Interestingly, the vast majority of participants had not heard of "the replication crisis".
+Participants' estimates of the replicability of psychological studies was also near the midpoint of the possible range (ABOUT 56%).
+Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
+However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
+
 # Discussion

### 2021-04-01 analysis/Manuscript.Rmd
remove extra corr code

@@
 
-# I'm sure there's a way to automate it, but I can't figure it out...just hard code it
-# all_cnorms <- df %>% 
-#     select(ends_with("_cnorm"))
+# just keeping this here for now, but will be able to delete
+# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
+# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
 # 
-# corr <- round(cor(all_), ends_with("_cnorm"),2)))
+# hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
+# hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
 # 
+# info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
+# info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
 # 
-#   all_norms %>% 
-#     cor(ends_with("_norm"), ends_with("_cnorm"))
+# open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
+# open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
 # 
+# open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
+# open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
 # 
-#   cor(all_norms, method = "pearson") %>% 
-#   as.tibble()
+# open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
+# open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
 # 
-# all_correlation <- df %>% 
-#     select(c(ends_with("_norm"), ends_with("_cnorm"))) %>% 
-#   mutate(item = row.names(.)) %>% 
-#   select(item, everything())
-
-# this code works, but I must be able to do this all at once...
-
-# breadcrumbs: when I come back to this, I need to combine these in a tibble
-  # and then join it with the existing table...I probably need to mutate, but I 
-  # need to sort out how to do this...
-
-# practice_corr <- practice_means %>% 
-  # mutate()
-
-critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
-critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
-
-hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
-hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
-
-info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
-info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
-
-open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
-open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
-
-open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
-open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
-
-open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
-open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
-
-phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
-phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
-
-preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
-preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
-
-prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
-prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)
-
-rbind()
+# phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
+# phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
+# 
+# preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
+# preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
+# 
+# prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
+# prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)
 

### 2021-04-01 analysis/Manuscript.Rmd
clean up code

@@
 library(tidyselect) 
-library(psychometric) # for correlation confidence intervals
+library(psychometric) # for correlation confidence intervals - might not need...
+library(broom)
 
@@
 critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
-tidy(critical_corr_test)
-
-cor(df$`norm rating`, df$`cnorm rating`)
+# tidy(critical_corr_test)
 

### 2021-04-14 analysis/Manuscript.Rmd
Adding items to method; some extra text in results; very rough start on discussion.

@@
 
+```{r norm_counternorm_items}
+norm_items = data.frame(
+  "Practice" = c("critical", "critical", "HARKing", "HARKing", "Info for replicability", "Info for replicability",
+                 "Open access", "open access", "Open data", "Open data", "Open materials", "Open materials",
+                 "p-hacking", "p-hacking", "Preprints", "Preprints", "Pregistration", "Preregistration",
+                 "Registered reports", "Registered reports"),
+  "Category" = rep(c("Norm", "Counternorm"), times = 10),
+  "Item" = c("Deborah used previously published research to inform her research study. Deborah should be critical of the findings published in journals because published research can be wrong.",
+             "Deborah used previously published research to inform her research study.
+Deborah should accept the findings published in journals because journals would not publish research with errors.",
+             "Deborah should only describe her study as a test of a hypothesis if she decided on her hypothesis and how she would test it before she started collecting data.",
+             "Once Deborah has analysed her results, it would be good scientific practice for her to write her manuscript as if she predicted those results from the beginning.",
+             "When reporting the findings of her study, Deborah should describe how she completed the study in enough detail that another researcher could repeat her entire study without having to check any details with her - even if this means including lots of “boring” practical details in her report, or in an appendix.",
+             "When reporting the findings of her study, it would be good scientific practice for Deborah to gloss over some of the practical details so she can tell a good story.",
+             "Once her study is complete, Deborah should publish her findings in a journal that is free for others to access.",
+             "Once her study is complete, Deborah should publish the findings in the most prestigious journal she can, even if that journal charges others a fee to access the report.",
+             "When Deborah publishes her study, she should post the anonymous responses from participants online so that anyone can access and use the responses in their own research.",
+             "Deborah should keep the participants’ responses from her study protected, so that only she and her research team can access them.",
+             "Deborah should share the written materials and measures for her study openly online so that other researchers and members of the public can access and use them.",
+             "Deborah should keep the written materials and measures for her study protected, so that only she and her research team can access them.",
+             "Deborah should report the findings of all analyses of her data that she conducts.",
+             "It would be good scientific practice for Deborah to run many different analyses of her data, and report only those that produce interesting findings.",
+             "Deborah should post a manuscript describing the findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal.",
+             "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal.",
+             "Before collecting her data, Deborah should write down what her hypotheses are and how she plans to collect and analyse data.
+She should then save her plan in an online registry so others can tell what methods and analyses she will use to test her hypotheses after collecting data.",
+             "Deborah should decide which data analyses are suitable to test her hypotheses only after looking at her data.",
+             "Deborah should submit a plan for her study to a journal to be checked by experts (peer reviewed) before she collects and analyses data.",
+             "Deborah should submit her study to a journal to be checked by experts (peer reviewed) only after she has finished collecting and analysing her data."))
+
+knitr::kable(norm_items,
+             caption = "Norm and counternorm items",
+             align = c('lll'))
+```
+
 ### Beliefs About the Practice of Psychological Science
@@
 
+```{r norms_in_practice_items}
+practice_items = data.frame(
+  "Practice" = c("Preregistration", "Registered reports", "p-hacking", "HARKing", "Info for replicability",
+                 "Preprint", "open materials", "Open data", "Data on request", "Open access"),
+  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
+             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
+             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
+             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
+             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
+             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
+             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
+             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
+             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
+             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
+)
+
+knitr::kable(practice_items,
+             caption = "Norms in practice items",
+             align = c('ll'))
+
+#Note to selves: The norm in practice items map fairly closely to norms and counternorms, but not exactly
+#I.e., there is no norm in practice item about critically evaluating published literature, but there is one about sharing
+#data on request (which isn't in the norms/counternorms)
+#I can't remember why we did this, but so it goes.
+#The ordering of this table also doesn't match the one above, which I'm leaving for the moment since we probably want to set
+#an order of items/norms and stick to it consistently throughout
+
+```
+
 ### Beliefs About Replications
 
-Participants' beliefs about the replicabilty of results in psychological science were indexed by two questions. The first asked participants to, 
+Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to, 
 > "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
@@
 However, the extent to which participants endorsed open science norms varied very substantially across different practices.
-Participants tended to agree or strongly agree that p-hacking should be avoided, and that researchers should provide sufficient information about studies to permit replicability.
-On the other hand, they were very skeptical of the practice of sharing preprints prior to peer review, and to a lesser extent about sharing open data.
-There also a degree of equivocation about registered reports, with very similar levels of agreement with both norm and counternorm for this item.
+In terms of open science norms, participants most strongly endorsed the idea that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4).
+They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items were all between 3.5 and 4 (4 representing 'agree').
+On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review, and to a lesser extent with sharing open data.
+The practice of registered reports was the one about which participants were most equivocal, with very similar levels of agreement (near the midpoint of 3) with both norm and counternorm for this item.
 This may be relatively unsurprising, given that the registered reports are perhaps the most recent innovation in the list of practices.
@@
 ## Norms in practice
-Participants were also asked to estimate the proportion of psychology studies estimated globally which apply ten practices (corresponding to the ten norm-counternorm pairs) .
+Participants were also asked to estimate the proportion of psychology studies estimated globally which apply ten practices.
+These practices corresponded approximately to the ten norm-counternorm pairs, albeit with one norm excluded on the basis of not referring to behaviour (critically evaluating published studies vs.
+accepting them), and one practice added out of interest (data sharing on request).
 For many of these practices, participants estimates were near the midpoint of 50%.
-This said, participants perceived some practices as being applied relatively infrequently: For example, the mean esitmate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
+This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
 Participants seemed to perceived that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
@@
 <!-- There's a key point for the discussion here, I think, in that the fact that many participants guessed near 50% for these practices suggests that students may have little idea of the prevalence of these practices in reality, and certainly education is needed on that point.
+
+We can add a table here with descriptive statistics (means? more?) for the norms in practice items.
+
 -->
@@
 Interestingly, the vast majority of participants had not heard of "the replication crisis".
-Participants' estimates of the replicability of psychological studies was also near the midpoint of the possible range (ABOUT 56%).
-Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
+Participants' estimates of the replicability of psychological studies was also near the midpoint of the possible range <!-- about 56% - need to code this in--> .
+
+<!-- Something about what they thought the replication crisis was... There were a couple of open-ended follow-up items
+
+Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
 However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
+-->
 
 # Discussion
+
+Our findings suggest that despite fairly significant media attention, most incoming psychology students are unaware of the replication crisis in psychology.
+In our study they tended to agree more with open science norms than they did counternorms, although this wasn't the case for all open science practices (and especially not sharing of preprints).
+
+Participants' estimates of the proportion of psychological studies published each which apply each of a set of ten open science practices mostly tended to hover near 50%.
+Although this could be read as implying literally that participants believe these practices are roughly as commonly applied as they are not, it could also be read as implying a great deal of uncertainty on the part of participants [might need to unpack this idea - i.e., that if people have no idea they'll probably pick 50%].
+
+Overall these findings suggest that while incoming psychology students may have a degree of enthusiasm for open science norms, they know relatively little about replicability and open science.
+
+<!--
+Obviously more to say - just starting with a very rough summary.
+-->
+
+## Strengths and limitations
+
+## Directions for future research
 

### 2021-04-16 analysis/Manuscript.Rmd
add the correlations and CI to the norm & counternorm table

@@
 library(tidyverse)
-library(finalfit) # to keep trailing zeros
+library(finalfit) # to keep trailing zeros & round_tidy
 library(psych) #for correlation matrices
@@
   results = 'as.is')
+```
+
+```{r functions}
+
+p_tidy <- function (x, digits, prefix = "= ") {
+    x.out = paste0(prefix, round_tidy(x, digits))
+    all_zeros = paste0(prefix, round_tidy(0, digits))
+    less_than = paste0("< ", format(10^-digits, scientific = FALSE))
+    x.out[x.out == all_zeros] = less_than
+    return(x.out)
+}
 ```
@@
 
-```{r, difference between norm and counternorm}
+```{r difference between norm and counternorm}
 
@@
 # combine means & SDs
-prac_means$Practice <- prac_means$practice
 prac_means$Norm <- paste0(round_tidy(prac_means$norm_mean,2),
@@
 practice_means <- prac_means %>% 
-  dplyr::select(Practice, Norm, Counternorm, Difference)
+  dplyr::select(practice, Norm, Counternorm, Difference)
 
@@
 # just the correlation with CI
-critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
-critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
+# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
+# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
 
 #correlation test with CI and p-values in a clean tibble
-critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
+# critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
 # tidy(critical_corr_test)
@@
 
-# this will create a tibble for each practice and then calculate
+# this will create a tibble for each practice
 
@@
 
+# remove unnecessary columns, round the values, and move columns
+corr <- corr %>% 
+  dplyr::select(-c(data, test, statistic, parameter, method, alternative))  %>% 
+  mutate(p.value = p_tidy(p.value, 3, prefix = "")) %>% 
+  mutate(estimate = round_tidy(estimate,2), 
+         conf.low = round_tidy(conf.low, 2), 
+         conf.high = round_tidy(conf.high, 2)) %>% 
+  dplyr::relocate(estimate, .before = conf.low) %>%  
+    dplyr::relocate(p.value, .after = last_col())
+
+# join the corr tibble with the means tibble 
+practice_means_corr <- practice_means %>% inner_join(corr, by = "practice")
+
+# combine the confidence intervals into one column
+practice_means_corr$Correlation <- paste0(practice_means_corr$estimate, 
+                            " [",
+                            practice_means_corr$conf.low,
+                            ", ", 
+                            practice_means_corr$conf.high,
+                            "]")
+
+# clean up the tibble                          
+practice_means_corr <- practice_means_corr %>% 
+  mutate(Practice = practice) %>% 
+  dplyr::select(-c(practice,estimate, conf.low, conf.high)) %>% 
+  relocate (Practice, .before = Norm) %>% 
+  relocate (p.value, .after = last_col())
+
 # breadcrumbs: keep the values that I need from this tibble
-# use p_tidy? to clean up the pvalues
-# round the corr & CI
-# join with the practice_means tibble & turn into a table
+# use p_tidy? to clean up the pvalues {done!}
+# round the corr & CI {done!}
+# join with the practice_means tibble & turn into a table {done!}
+# need to figure out whether I can rotate a page in papaja
 
@@
 
-knitr::kable(practice_means,
-             caption = "Means (sd) for norms, counternorms, and the difference between the two for each of the practices",
+knitr::kable(practice_means_corr,
+             caption = "Means (sd) for norms, counternorms, the difference between norms and counternorms, and correlations between norms and counternorms",
              digits = 2,
@@
 ```
+
+<!-- I imagine we will remove the p.value column, but we might want this for now.  -->
 

### 2021-04-19 analysis/Manuscript.Rmd
Fixes to references, added gender, added twitter refs for anecdotal claim

--- 2021-04-14 analysis/Manuscript.Rmd
@@
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
-These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
+These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
 These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
 These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
-Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018).
-In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].
-These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
+Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018].
+In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
+These initiatives may help ingrain open science norms and change attitudes about research practices, but are difficult to evaluate when we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 
-The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science.
-Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles.
+The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942].
+Scientists [@Anderson2000] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.
@@
 Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
-In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.
+In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.<!--Should we consider citing someone for these links?
+Personally I have seen Simine draw these parallels between norms and open science practices and would favour crediting her here, however I'm sure that others have made similar analyses and so would be happy to cite others or to see this as such a commonly held set of beliefs that no citations are required--->
 
@@
 
-First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018; @ogradyPsychologyReplicationCrisis2020].
+First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018].
 Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
@@
 Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
-An over-emphasis on problems with replicability could leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge?
-For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis[^1].
-[^1]: Notably, the effect of the lecture on trust of psychological stuides was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
+An over-emphasis on problems with replicability could leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge.
+For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis
+^[1 Notably, the effect of the lecture on trust of psychological studies was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).].
 
-Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice.
+Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g.
+see tweets on this topic: @burak_tunca_uygun_tunc_2021; @duygu_uygun-tunc_uygun_tunc_last_2021; @lorne_campbell_distributary_academic_minzlicht_2018].
 In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices.
@@
   # [breadcrumb]
+gender <- df %>% dplyr::count(gender)
 
@@
 
-<!-- ADD GENDER HERE! -->
+The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
+`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
+their gender identity as "queer man", and `r gender[3,2]` participant reported 
+non-binary gender.^[While the response "queer man" could potentially be coded as
+"male", we are aware that some individuals who report gender in this way would
+not feel that such reclassification was appropriate. We have retained the original
+response in order to provide a faithful representation of the participant's 
+self-reported gender.]
 
@@
 The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total (see Table X).
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total (see Table \@ref(tab:norm_counternorm_items)).
 Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.

### 2021-04-19 preprocessing/preprocessing_students.R

@@ -9,6 +9,7 @@
 library(tidyverse)
 library(here)
 library(tools)
+library(gendercoder)
 
 
 ####### FUNCTIONS ############
@@ -55,20 +56,20 @@ df_lab <- here::here("data", "students_raw_data_with_labels.csv") %>%
 
 # load metadata
 metadata <- read_csv(here::here("data", "students_metadata.csv")) %>%
-  select(-c(X10,"note:")) %>%  # delete unnecessary columns
+  dplyr::select(-c(X10,"note:")) %>%  # delete unnecessary columns
   filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables
 
 #### CLEAN DATA ####
 
 df_num <- df_num %>%
   relocate(id) %>% # move the ID variable to the first column
-  select(-c(v1:consent,scenario_remind)) %>%  # remove extraneous columns
-  select(-c(uni_country:nationality))  # remove Qualtrics-coded variables [use label dataset for these]
+  dplyr::select(-c(v1:consent,scenario_remind)) %>%  # remove extraneous columns
+  dplyr::select(-c(uni_country:nationality))  # remove Qualtrics-coded variables [use label dataset for these]
 
 df_lab <- df_lab %>%
   relocate(id) %>% # move the ID variable to the first column
-  select(-c(start_date, end_date, progress:consent)) %>%  # remove extraneous columns
-  select(-c(uni:major,
+  dplyr::select(-c(start_date, end_date, progress:consent)) %>%  # remove extraneous columns
+  dplyr::select(-c(uni:major,
             gender,
             q54,
             practices_1:rep_perc_1,
@@ -101,7 +102,18 @@ df <- df %>%
 
 ######### RECODE GENDER ##########
 
-# gender --> need to run through gendercoder [breadcrumb!]
+######### RECODE GENDER ##########
+
+custom_dictionary <- list(
+  `female.` = "female",
+  `femamle` = "female",
+  `-` = NA_character_,
+  `gender no longer has a place in modern society. sex is male.` = "male",
+  `queer man` = "queer man"
+)
+
+df <- df %>%
+  mutate(gender  = recode_gender(gender, dictionary = c(broad, custom_dictionary), fill = TRUE))
 
 ########## EXCLUSION CRITERIA ############
 

### 2021-04-19 analysis/Manuscript.Rmd

--- 2021-04-16 analysis/Manuscript.Rmd
@@
 
-The most comprehensive set of principles for how science *ought* to be practiced are Merton's (1942) norms of science.
-Scientists (Anderson et al., 2000) and graduate students (Anderson & Louis, 1994) alike have historically endorsed the normative value of Merton's principles.
+The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942].
+Scientists [@Anderson2000] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.

### 2021-05-04 analysis/Manuscript.Rmd
some minor editing of references etc

@@
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
-These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings[@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
+These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
 These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
 These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
-Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018, @harrisUseReproducibleResearch2018).
-In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012, @jekelHowTeachOpen2020, @schonbrodtTrainingStudentsOpen2019].
+Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018].
+In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
 These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
@@
 Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g.
-see tweets on this topic: @burak_tunca_uygun_tunc_2021; @duygu_uygun-tunc_uygun_tunc_last_2021; @lorne_campbell_distributary_academic_minzlicht_2018].
-In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices.
+see tweets on this topic: @burak_tunca_uygun_tunc_2021; @duygu_uygun-tunc_uygun_tunc_last_2021; @lorne_campbell_distributary_academic_minzlicht_2018].<!--I'm not sure what happened to these citations but I can't find them in our library anymore - need to fix --> In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices.
 Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
@@
 ## The replication crisis
-Interestingly, the vast majority of participants had not heard of "the replication crisis".
-Participants' estimates of the replicability of psychological studies was also near the midpoint of the possible range <!-- about 56% - need to code this in--> .
+Interestingly, the vast majority of participants had not heard of "the replication crisis" <!-- add numeric estimate-->.
 
-<!-- Something about what they thought the replication crisis was... There were a couple of open-ended follow-up items
+<!-- For people who answered "yes" (they had heard the term) there were a couple of open-ended follow-up items: What do think the replication is?
+Which scientific disciplines do you think are most affected by the replication crisis?
+We could analyse these and try to give some indication of whether the students who *had* heard of it actually knew what the term refers to.
+-->
 
-Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
+Participants' estimates of the replicability of psychological studies was near the midpoint of the possible range <!-- about 56% - need to code this in--> .
+
+<!--Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
 However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
@@
 
-Overall these findings suggest that while incoming psychology students may have a degree of enthusiasm for open science norms, they know relatively little about replicability and open science.
+Overall these findings suggest that while incoming psychology students may have a degree of sympathy for open science norms, they know relatively little about replicability and open science.
 
@@
 ## Strengths and limitations
+Our study had a relatively large sample size, but used convenience/haphazard sampling.
+The results also reflect responses of just one sample of students at one point in time.
+Generalisations to a wider population of incoming students (or students beginning psychology students in the future) can be made only very tentatively.
+Our questions also focused primarily on attitudes and beliefs, rather than probing students' factual knowledge of findings or concepts.
+
+<!--
+More to say here.
+-->
 

### 2021-05-11 analysis/Manuscript.Rmd
Restoring code for Jen

@@
 ## The replication crisis
-Interestingly, the vast majority of participants had not heard of "the replication crisis" <!-- add numeric estimate-->.
+Interestingly, only (`r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% ) of participants had heard of "the replication crisis", with (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and %  ) <!-- add numeric estimate-->.
 

### 2021-05-11 analysis/Manuscript.Rmd
tidy up the correlation chunk

--- 2021-05-04 analysis/Manuscript.Rmd
@@
 
-# breadcrumbs: keep the values that I need from this tibble
-# use p_tidy? to clean up the pvalues {done!}
-# round the corr & CI {done!}
-# join with the practice_means tibble & turn into a table {done!}
+# breadcrumbs:
 # need to figure out whether I can rotate a page in papaja
-
-# just keeping this here for now, but will be able to delete
-# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
-# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
-# 
-# hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
-# hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
-# 
-# info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
-# info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
-# 
-# open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
-# open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
-# 
-# open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
-# open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
-# 
-# open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
-# open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
-# 
-# phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
-# phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
-# 
-# preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
-# preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
-# 
-# prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
-# prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)
-
-# breadcrumbs: 
 # I need to use apa_tables.... (in line with papaja)
-# pull means & sd into the same column with (sd) in parentheses [done!]
-# headings should then be norm, counternorm, difference [done!]
-# add correlations with 95% CIs 
 # update practice descriptions so they make sense to readers

### 2021-05-11 analysis/Manuscript.Rmd
create table for norms in practice

@@
 practice_means_corr <- practice_means_corr %>% 
-  mutate(Practice = practice) %>% 
-  dplyr::select(-c(practice,estimate, conf.low, conf.high)) %>% 
+  rename(Practice = practice) %>% 
+  dplyr::select(-c(estimate, conf.low, conf.high)) %>% 
   relocate (Practice, .before = Norm) %>% 
@@
 This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
-Participants seemed to perceived that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
-It is perhaps fair to say that participants mean estimate that `r paste(round(mean(df$detailed_methodology, na.rm = TRUE), 2), "%", sep = "")` of studies have this characteristic represents a rather optimistic projection.
+Participants seemed to perceive that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
+It is perhaps fair to say that participants' mean estimate that `r paste(round(mean(df$detailed_methodology, na.rm = TRUE), 2), "%", sep = "")` of studies have this characteristic represents a rather optimistic projection.
+
+```{r norms in practice}
+
+# select columns that relate to norms in practice & pivot it long & drop the na values
+in_prac_long <- df %>% 
+  dplyr::select(c(id,preregistration:open_access)) %>% 
+      pivot_longer (cols = -id,
+                names_to = "practice",
+                values_to = "prevalence rating") %>% 
+  drop_na()
+
+# get the n values for each of the practices
+in_prac_counts <- in_prac_long %>% 
+  dplyr::group_by(practice) %>% 
+  count() %>% 
+  ungroup()
+
+# calculate means
+in_prac_ms_sds <- in_prac_long %>%
+  dplyr::group_by(practice) %>%
+  summarise(mean = mean(`prevalence rating`),
+            sd = sd(`prevalence rating`)) %>%
+  ungroup()
+
+# join the n values with the means
+in_prac_means <- in_prac_counts %>% inner_join(in_prac_ms_sds)
+
+# calculate 95% CIs
+error <- qnorm(0.975) * in_prac_means$sd/sqrt(in_prac_means$n)
+in_prac_means$lower <- in_prac_means$mean - error
+in_prac_means$upper <- in_prac_means$mean + error
+
+# combine means & SDs
+in_prac_means$`Prevalence Ratings` <- paste0(round_tidy(in_prac_means$mean,2),
+                          " (", 
+                          round_tidy(in_prac_means$sd,2),
+                            ")", 
+                            " [",
+                            round_tidy(in_prac_means$lower,2),
+                            ", ", 
+                            round_tidy(in_prac_means$upper,2),
+                            "]")
+
+# clean it up into a new dataframe with only the columns we need
+in_practice_means <- in_prac_means %>% 
+  dplyr::select(practice, `Prevalence Ratings`) %>% 
+  rename(Practice = practice)
+
+# breadcrumbs:
+# I need to use apa_tables.... (in line with papaja)
+# update practice descriptions so they make sense to readers
+
+knitr::kable(in_practice_means,
+             caption = "Means, standard deviations, and 95% confidence intervals for the prevalence ratings for each research practice",
+             digits = 2,
+             align = c('lc'))
+
+```
 

### 2021-05-11 analysis/Manuscript.Rmd
Deleting pairs panel, updating replication crisis subsection of results

--- 2021-05-11 analysis/Manuscript.Rmd
@@
 
-```{r correlation_matrix}
-#pairs.panel etc. won't really work because there are too many variables
-#And we only need corrs between matched pairs
-#So doing this a bit more manually
-layout(matrix(1:8, ncol = 4))
-
-plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "critical counternorm", ylab = "critical norm")
-abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
-legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))
-
-plot(df$prereg_norm ~ jitter(df$prereg_cnorm), ylab = "Prereg norm", xlab = "Prereg counternorm")
-abline(lm(df$prereg_norm ~ df$prereg_cnorm), col = "blue")
-legend(x='bottomright', legend=paste('Cor =', round(cor(df$prereg_norm, df$prereg_cnorm),2)))
-
-plot(df$reg_report_norm ~ jitter(df$reg_report_cnorm), ylab = "Reg Reports norm", xlab = "Reg Reports counternorm")
-abline(lm(df$reg_report_norm ~ df$reg_report_cnorm), col = "blue")
-legend(x='bottomleft', legend=paste('Cor =', round(cor(df$reg_report_norm, df$reg_report_cnorm),2)))
-
-plot(df$phack_norm ~ jitter(df$phack_cnorm), ylab = "p-hacking rnorm", xlab = "p-hacking counternorm")
-#potential confusion here about direction of phrasing (pro p-hacking = counternorm?)
-abline(lm(df$phack_norm ~ df$phack_cnorm), col = "blue")
-legend(x='bottomleft', legend=paste('Cor =', round(cor(df$phack_cnorm, df$phack_norm),2)))
-
-plot(df$hark_norm ~ jitter(df$hark_cnorm), ylab = "HARKing norm", xlab = "HARKing counternorm")
-abline(lm(df$hark_norm ~ df$hark_cnorm), col = "blue")
-legend(x='bottomright', legend=paste('Cor =', round(cor(df$hark_cnorm, df$hark_norm),2)))
-
-plot(df$info_for_rep_norm ~ jitter(df$info_for_rep_cnorm), ylab = "Replicability norm", xlab = "Replicability counternorm")
-abline(lm(df$info_for_rep_norm ~ df$info_for_rep_cnorm), col = "blue")
-legend(x='right', legend=paste('Cor =', round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)))
-
-plot(df$preprint_norm ~ jitter(df$preprint_cnorm), ylab = "Preprints norm", xlab = "Preprints counternorm")
-abline(lm(df$preprint_norm ~ df$preprint_cnorm), col = "blue")
-legend(x='bottomleft', legend=paste('Cor =', round(cor(df$preprint_norm, df$preprint_cnorm,
-                                                       use = "pairwise.complete.obs"),2)))
-
-plot(df$open_materials_norm ~ jitter(df$open_materials_cnorm), ylab = "Open materials norm", xlab = "Open materials counternorm")
-abline(lm(df$open_materials_norm ~ df$open_materials_cnorm), col = "blue")
-legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_materials_norm, df$open_materials_cnorm, use = "pairwise.complete.obs"),2)))
-
-plot(df$open_data_norm ~ jitter(df$open_data_cnorm), ylab = "Open data norm", xlab = "Open data counternorm")
-abline(lm(df$open_data_norm ~ df$open_data_cnorm), col = "blue")
-legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_data_norm, df$open_data_cnorm),2)))
-
-plot(df$open_access_norm ~ jitter(df$open_access_cnorm), ylab = "Open access norm", xlab = "Open access counternorm")
-abline(lm(df$open_access_norm ~ df$open_access_cnorm), col = "blue")
-legend(x='bottomright', legend=paste('Cor =', round(cor(df$open_access_norm, df$open_access_cnorm),2)))
-
-```
-
 ## Norms in practice
@@
 ## The replication crisis
-Interestingly, only (`r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% ) of participants had heard of "the replication crisis", with (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and %  ) <!-- add numeric estimate-->.
+Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis", with `r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% missing.
 
-<!-- For people who answered "yes" (they had heard the term) there were a couple of open-ended follow-up items: What do think the replication is?
-Which scientific disciplines do you think are most affected by the replication crisis?
-We could analyse these and try to give some indication of whether the students who *had* heard of it actually knew what the term refers to.
--->
+```{r include = FALSE}
+write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
+crisis_descriptions = read.csv("crisis_descriptions_marked.csv") #categorised as accurate or not
+```
+Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"?
+Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term.
+Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
+Just `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
 
-Participants' estimates of the replicability of psychological studies was near the midpoint of the possible range <!-- about 56% - need to code this in--> .
+Participants' estimates of the replicability of psychological studies were variable.
+The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`.
+A histogram of participants' responses is provided in Figure X.
 
-<!--Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
-However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
--->
+```{r rep_perc_histogram}
+hist(df$rep_perc, main = NULL, xlab = "Percentage")
+```
+_Figure X_.
+Histogram of participants' responses to the question: "Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+We call repeating a study like this a “replication study”.
+At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?" Responses provided on a visual slider.
+
+<!-- Participants were also asked "Which scientific disciplines do you think are most affected by the replication crisis?" As we discussed, I'm not sure this response will really be useful to look at given that we have "primed" them to think of psychology as being most affected (and indeed that's what the responses largely indicate).-->
 

### 2021-05-11 preprocessing/preprocessing_students.R
Add first pass coding for degrees/majors and universities

@@ -241,6 +241,8 @@ qual_maj <- qual %>%
   summarise(n_distinct(id)) %>%
   rename(`frequency` = `n_distinct(id)`)
 
+
+
 # write each of them to csv files
 write.csv(qual_uni, here::here("preprocessing", "qual_responses_uni.csv"), row.names = FALSE)
 
@@ -248,3 +250,278 @@ write.csv(qual_deg, here::here("preprocessing", "qual_responses_deg.csv"), row.n
 
 write.csv(qual_maj, here::here("preprocessing", "qual_responses_maj.csv"), row.names = FALSE)
 
+df <- df %>%
+  mutate(
+    university_recoded = case_when(
+      university == "Adelaide"                                   ~ "University of Adelaide",
+      university == "adelaide uni"                               ~ "University of Adelaide",
+      university == "Adelaide uni"                               ~ "University of Adelaide",
+      university == "adelaide university"                        ~ "University of Adelaide",
+      university == "Adelaide university"                        ~ "University of Adelaide",
+      university == "the University of Adelaide"                 ~ "University of Adelaide",
+      university == "university of  adelaide"                    ~ "University of Adelaide",
+      university == "university of adelaide"                     ~ "University of Adelaide",
+      university == "the university of adelaide"                 ~ "University of Adelaide",
+      university == "The university of Adelaide"                 ~ "University of Adelaide",
+      university == "University of Adelaide."                    ~ "University of Adelaide",
+      university == "Adelaide University"                        ~ "University of Adelaide",
+      university == "Univerisity of Adelaide"                    ~ "University of Adelaide",
+      university == "University of Adelaide"                     ~ "University of Adelaide",
+      university == "Adelaide Uni"                               ~ "University of Adelaide",
+      university == "Adelaide Universtiy"                        ~ "University of Adelaide",
+      university == "The University of Adelaide"                 ~ "University of Adelaide" ,
+      university == "University of  Adelaide"                    ~ "University of Adelaide" ,
+      university == "Bath"                                       ~ "University of Bath",
+      university == "Batj"                                       ~ "University of Bath" ,
+      university == "University of Bath"                         ~ "University of Bath",
[…]

### 2021-05-11 analysis/Manuscript.Rmd
Add degree information

@@
 the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`).
-Finally, about 2/3rds of participants reported that at least one of their parents 
-attended university (*n* = `r first_gen[2,2]`).
+About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`).
+Students were recruited from nine universities, with the largest number of responses recorded from participants enrolled at the University of Queensland (*n* = `r nrow(filter(df, university_recoded == "University of Queensland"))`), University of Adelaide (*n* = `r nrow(filter(df, university_recoded == "University of Adelaide"))`), and the University of Bath (*n* = `r nrow(filter(df, university_recoded == "University of Bath"))`).
+While, the majority of participants (*n* = `r nrow(filter(df, degree_type == "Non-psychology"))`) indicated that they were enrolled in a non-psychology degree such as a Bachelor of Science or Bachelor of Arts (*n* = `r nrow(filter(df, degree_recoded == "Bachelor of Science"))`, *n* = `r nrow(filter(df, degree_recoded == "Bachelor of Arts"))` respectively), most were completing a psychology major (*n* = `r nrow(filter(df, major_recoded == "Psychology"))`).
 
@@
 
-```{r include = FALSE}
+```{r include = FALSE, evaluate = FALSE}
 write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")

### 2021-05-11 preprocessing/preprocessing_students.R

@@ -203,8 +203,6 @@ df <- df %>%
 # when done preprocessing, write the data to a new file
 # row.names gets rid of the first column from the dataframe.
 
-write.csv(df, here::here("data", "students_processed.csv"), row.names = FALSE)
-
 ################### CODING QUALITATIVE RESPONSES #############
 
 # Breadcrumbs: We will need to code their qualitative responses (university, degree,
@@ -217,7 +215,7 @@ write.csv(df, here::here("data", "students_processed.csv"), row.names = FALSE)
 
 qual <- df %>%
   filter(exclude %in% "include") %>%
-  select(c(id,university, degree, major))
+  dplyr::select(c(id,university, degree, major))
 
 # force the responses to title case & then group those that are similar
   # use the id number to count how many responses matched
@@ -521,7 +519,20 @@ df <- df %>%
       major == 'Sociology' ~ 'Not psychology',
       major == 'Speech Pathology' ~ 'Not psychology',
       major == 'Sport Studies' ~ 'Not psychology',
+      major == "Biology, Anatomy, Psychology, Physiotherapy"  ~ 'Not psychology',
+      major == "blank"  ~ 'Not psychology',
+      major == "International Relations"  ~ 'Not psychology',
+      major == "Marketing"  ~ 'Not psychology',
+      major == "Medical science"  ~ 'Not psychology',
+      major == "psychological science and law" ~ "Psychology",
+      major == "Psychology Extended Major and Philosophy, Spanish" ~ "Psychology",
+      major == "PSYCHOLOGY/ENVIRONMENT AND SOCIETY" ~ "Psychology",
+      major == "Neuroscience" ~ "Psychology",
+      major == "-" ~ "Psychology",
       is.na(major_recoded) ~ NA_character_,
+      degree_type == "Psychology" ~ "Psychology",
       TRUE ~ "Uncoded"
     )
   )
+
+write.csv(df, here::here("data", "students_processed.csv"), row.names = FALSE)

### 2021-07-30 analysis/Manuscript.Rmd
minimal changes to Rmd

@@
 ```{r setup, include = FALSE}
-library(papaja)
+library(papaja) #install with devtools1
 library(here)
@@
 While, the majority of participants (*n* = `r nrow(filter(df, degree_type == "Non-psychology"))`) indicated that they were enrolled in a non-psychology degree such as a Bachelor of Science or Bachelor of Arts (*n* = `r nrow(filter(df, degree_recoded == "Bachelor of Science"))`, *n* = `r nrow(filter(df, degree_recoded == "Bachelor of Arts"))` respectively), most were completing a psychology major (*n* = `r nrow(filter(df, major_recoded == "Psychology"))`).
-
-```{r qual responses}
-
-# [breadcrumbs] 
- # once qual responses are coded, I will need to return here to 
- # include details about which univrsity the participant is enrolled in
- # name of qualification
- # major [how many are majoring in psyc; NAs; will decide later?]
-
-```
 
@@
 
-```{r include = FALSE, evaluate = FALSE}
+```{r crisis descriptions, eval=FALSE, include=FALSE}
 write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
@@
 ```
+
+<!-- This needs another csv file in order to run the code above. Also, revise where the csv file is written to and loaded from.  -->
+
 Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"?

### 2021-07-30 preprocessing/preprocessing_students.R

@@ -9,7 +9,7 @@
 library(tidyverse)
 library(here)
 library(tools)
-library(gendercoder)
+library(gendercoder) #devtools::install_github("ropenscilabs/gendercoder")
 
 
 ####### FUNCTIONS ############
@@ -44,13 +44,13 @@ miss_fun = function(x){
 ##### LOAD DATA #####
 
 # raw data without labels
-df_num <- here::here("data", "students_raw_data.csv") %>%
+df_num <- here::here("survey", "data", "students_raw_data.csv") %>%
   read_qualtrics(legacy = TRUE) %>%
   mutate(id = 1:n())
 
 
 # raw data with labels
-df_lab <- here::here("data", "students_raw_data_with_labels.csv") %>%
+df_lab <- here::here("survey", "data", "students_raw_data_with_labels.csv") %>%
   read_qualtrics(legacy = FALSE) %>%
   mutate(id = 1:n())
 
@@ -238,7 +238,6 @@ qual_maj <- qual %>%
   group_by(major) %>%
   summarise(n_distinct(id)) %>%
   rename(`frequency` = `n_distinct(id)`)
-
 
 
 # write each of them to csv files

### 2021-08-27 analysis/Manuscript.Rmd
update replication crisis code, update table

@@
 
-# import the data 
+# import the main data 
 df <- read.csv (here::here("data", "students_processed.csv"))
+
+# upload the replication crisis responses, marked as accurate and inaccurate (outside of R)
+crisis_descriptions = read.csv(here::here ("data", "crisis_descriptions_marked.csv"))
 
@@
 The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942].
-Scientists [@Anderson2000] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
+Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.
@@
   "Practice" = c("critical", "critical", "HARKing", "HARKing", "Info for replicability", "Info for replicability",
-                 "Open access", "open access", "Open data", "Open data", "Open materials", "Open materials",
-                 "p-hacking", "p-hacking", "Preprints", "Preprints", "Pregistration", "Preregistration",
+                 "Open access", "Open access", "Open data", "Open data", "Open materials", "Open materials",
+                 "p-hacking", "p-hacking", "Preprints", "Preprints", "Preregistration", "Preregistration",
                  "Registered reports", "Registered reports"),
@@
 
-knitr::kable(norm_items,
+norm_items_wide <- pivot_wider(
+  norm_items,
+  names_from = Category,
+  values_from = Item)
+
+knitr::kable(norm_items_wide,
              caption = "Norm and counternorm items",
@@
 
-```{r crisis descriptions, eval=FALSE, include=FALSE}
-write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
-crisis_descriptions = read.csv("crisis_descriptions_marked.csv") #categorised as accurate or not
-```
-
-<!-- This needs another csv file in order to run the code above. Also, revise where the csv file is written to and loaded from.  -->
-
 Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"?
@@
 Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
-Just `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
+Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
 

### 2021-08-27 preprocessing/preprocessing_students.R

@@ -198,54 +198,11 @@ df <- df %>%
     TRUE ~ "exclude")
   ))
 
-################### WRITE DATA TO CSV #############
 
-# when done preprocessing, write the data to a new file
-# row.names gets rid of the first column from the dataframe.
 
 ################### CODING QUALITATIVE RESPONSES #############
 
-# Breadcrumbs: We will need to code their qualitative responses (university, degree,
-  # major). To do so, for the eligible participants, I am selecting those
-  # variables and exporting them to a separate document.
-
-# [[breadcrumbs: rejoin the coded values back to the df &
-  # then write that data to the main data file.
-  # Move this above when done preprocessing. ]]
-
-qual <- df %>%
-  filter(exclude %in% "include") %>%
-  dplyr::select(c(id,university, degree, major))
-
-# force the responses to title case & then group those that are similar
-  # use the id number to count how many responses matched
-  # do this separately for uni, degree, and major
-
-qual_uni <- qual %>%
-  transmute(university = toTitleCase(university),id) %>%
-  group_by(university) %>%
-  summarise(n_distinct(id)) %>%
-  rename(`frequency` = `n_distinct(id)`)
-
-qual_deg <- qual %>%
-  transmute(degree = toTitleCase(degree),id) %>%
-  group_by(degree) %>%
-  summarise(n_distinct(id)) %>%
-  rename(`frequency` = `n_distinct(id)`)
-
-qual_maj <- qual %>%
-  transmute(major = toTitleCase(major),id) %>%
-  group_by(major) %>%
-  summarise(n_distinct(id)) %>%
-  rename(`frequency` = `n_distinct(id)`)
-
-
-# write each of them to csv files
-write.csv(qual_uni, here::here("preprocessing", "qual_responses_uni.csv"), row.names = FALSE)
-
-write.csv(qual_deg, here::here("preprocessing", "qual_responses_deg.csv"), row.names = FALSE)
-
-write.csv(qual_maj, here::here("preprocessing", "qual_responses_maj.csv"), row.names = FALSE)
+### ACTUAL RECODING OF QUALITATIVE VARIABLES UNIVERSITY, DEGREE, MAJOR
 
 df <- df %>%
   mutate(
@@ -534,4 +491,18 @@ df <- df %>%
     )
   )
 
+################### WRITE DATA TO CSV #############
+
+# when done preprocessing, write the data to a new file
+# row.names gets rid of the first column from the dataframe.
+
[…]

### 2021-09-09 analysis/Manuscript.Rmd
include histograms for norms in practice
update with changes

@@
   institution: Massey University
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
+```{r norms in practice histogram}
+
+p <- in_prac_long %>%
+  ggplot(aes(x = `prevalence rating`)) +
+  geom_histogram(aes(y=stat(count)), binwidth = 10) +
+    xlab("Prevalence Ratings (%)") +
+    ylab("Frequency") +
+    facet_wrap(~practice)
+p
+
+#[breadcrumb: need to update the theme & the practice names]
+
+```
+
 <!-- There's a key point for the discussion here, I think, in that the fact that many participants guessed near 50% for these practices suggests that students may have little idea of the prevalence of these practices in reality, and certainly education is needed on that point.

### 2021-09-10 analysis/Manuscript.Rmd

--- 2021-07-30 analysis/Manuscript.Rmd
@@
   Enter author note here.
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-  One or two sentences to put the results into a more **general context**.
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-  <!-- https://tinyurl.com/ybremelq -->
-keywords: open science, psychology, teaching, reproducibility, replication
+
+# Abstract: |
+
+## BACKGROUND: Rapid changes to methodological best practices present significant challenges for educating students new to the field of psychology.
+Some students may have existing knowledge about recent methodological reforms (e.g., preregistration, replication).
+Yet, where knowledge is lacking, overemphasizing the problems that precipitate these reforms (e.g., p-hacking, HARKing) may lead students to de-value scientific methods as a credible means for generating knowledge.
+## OBJECTIVE: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
+## METHOD: This study examined ### incoming undergraduate psychology students’ understandings of how research *should* be conducted (norms) and how they believed research *is* conducted (practice) using an online survey.
+## RESULTS: We found that XXX. . .
+## CONCLUSION:
+
+Keywords: open science, psychology, teaching, reproducibility, replication
 wordcount: X
+
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
@@
 ```{r setup, include = FALSE}
-library(papaja) #install with devtools1
+library(papaja)
 library(here)
@@
 These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
-These apparent problems with replication have lead to a variety of potential solutions to make research practices more transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-These calls for more transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
+These apparent problems with replication have lead to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
+These calls for more reproducible and transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
 Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018].
-In turn, initiatives have been directed toward training undergraduate students in the adoption of an open science ethos [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
-These initiatives help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
 
 The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942].
-Scientists [@Anderson2000] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
-Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms.
-For example, the practice of sharing open source software directly corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.
-Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, but also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
+Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
+Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe; vazireWhereAreSelfcorrecting2020].
+For example, the practice of sharing open source software corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.
+Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
 Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
-In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.<!--Should we consider citing someone for these links?
-Personally I have seen Simine draw these parallels between norms and open science practices and would favour crediting her here, however I'm sure that others have made similar analyses and so would be happy to cite others or to see this as such a commonly held set of beliefs that no citations are required--->
+In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.
 
-Nevertheless, rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
+Rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
 Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace.
-Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves, so that they may produce research that is even more replicable than that of previous generations.
+Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves.
 Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge.
-However, how we best provide this understanding is no trivial task.
-Indeed, there are several reasons why it might be unwise to assume a simple knowledge deficit, where the teacher's only role is to dispense an understanding of open science and transparent research practices.
+Studies have therefore begun to explore strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
+These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
+There are several reasons why this knowledge could be useful.
 
-First, unlike some areas of psychology covered in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018].
-Many students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
+First, unlike some psychological phenomena in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018].
+Students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
 Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
@@
 Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
-An over-emphasis on problems with replicability could leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge.
-For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis
-^[1 Notably, the effect of the lecture on trust of psychological studies was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).].
+An emphasis on problems with replicability could at least in principle leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge.
+For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis.
+This said, the effect of the lecture on trust of psychological studies was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
+Knowledge about incoming students’ “baseline” perceptions of the replicability of psychological science could further inform teachers about the salience of this risk.
 
-Third, anecdotal evidence suggests that students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that this is not *already* standard practice [e.g.
-see tweets on this topic: @burak_tunca_uygun_tunc_2021; @duygu_uygun-tunc_uygun_tunc_last_2021; @lorne_campbell_distributary_academic_minzlicht_2018].<!--I'm not sure what happened to these citations but I can't find them in our library anymore - need to fix --> In other words, students' naive conception of how science works may, in some ways, be closer to that embodied in recent reforms rather than "business as usual" practices.
-Indeed, surveys of scientists' subscriptions to Mertonian norms have often found that while most scientists endorse Mertonian norms such as communality, universalism and disinterestedness, this is by no means the case for all scientists.
-Furthermore, they typically perceive the behaviour of other scientists as being less consistent with these norms than their own [@andersonNormativeDissonanceScience2007].
-Therefore - for some students - teaching about reform may be less a matter of conveying new information and more one of reinforcing "naive" assumptions.
-In fact, although beyond the scope of this article, it is *possible* that incoming undergraduate students more strongly endorse open science norms than do academics.
-
-<!-- I think it'd be useful here if we were able to point to examples of the anecdotal evidence mentioned above - anyone come across anything (even just on social media?) 
-Also maybe add more about what we know about academics' endorsement of open science norms.
--->
-
-These considerations suggest that it is important that teachers wishing to inform undergraduate psychology students about the replication crisis and open science practices have some understanding of what such students actually know and believe about these topics already.
-In addition, undergraduate psychology students themselves represent one of the most important audiences for psychological research: The number of undergraduate students enrolled in psychology courses in any given year dwarfs the number of academics working in psychology.
-As such, the *preferences* of these students with respect to reproducibility and open science practices are themselves important as a phenomenon of interest.
-If, for example, undergraduate psychology students have a strong preference that journal articles are freely available to members of the public, this preference on the part of some of the consumers of the knowledge we produce should have some bearing on our choices in relation to sharing of manuscripts.
-This is especially the case given that undergraduate students are directly or indirectly responsible for much of the funding which allows universities to operate and research to be conducted.
-In fact, in serving as participants for course credit in many universities, undergraduate psychology students also provide the data underlying much psychological research.
-
-<!-- I'm not sure about the argument in the above paragraph - might be somewhat of a stretch? 
-MP: Maybe a stretch, but given we have a good rationale already, it might be worth trying to keep it. We may need a reference to two to help make some of the claims more concrete though.-->
+Third, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice [e.g.
+see tweets on this topic: @buraktuncaUygunTuncRmounce2021; @duyguuygun-tuncLastNightWas2021].
+This could imply a need for educators to reinforce and build on students “naive” impressions rather than radically altering their understanding of how science should be done.
+On the other hand, other evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility.
+For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values.
+The extent to which incoming psychology students may - or may not - typically be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
 
 For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
-Our survey encompassed norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is).
+Our survey encompassed questions norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is).
 In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices.
@@
 
-Of the remaining `r n` participants, most reported that they were
+Of the remaining `r n` participants, most reported being
 18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
@@
 The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
-`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
-their gender identity as "queer man", and `r gender[3,2]` participant reported 
+`r gender[2,2]` reported that they were male, `r gender[3,2]` participants reported 
+their gender identity as "queer man", and `r gender[3,2]` participants reported 
 non-binary gender.^[While the response "queer man" could potentially be coded as
@@
 
-Nearly all reported that they graduated from high
+Most participants reported attending university in Australia (*n* = `r uni_country[1,2]`), 
+the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). Nearly all reported graduating from high
 school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
-attended high school, a little less than half completed psychology courses in 
-high school (*n* = `r hs_psyc[2,2]`). In terms of their nationality, most 
-participants reported that they were Australian (*n* = `r nationality[3,2]`), 
-from the United Kingdom (*n* = `r nationality[24,2]`), or Chinese 
-(*n* = `r nationality[6,2]`). In terms of where the participants were attending 
-university, most reported that they were in Australia (*n* = `r uni_country[1,2]`), 
-the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`).
-About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`).
-Students were recruited from nine universities, with the largest number of responses recorded from participants enrolled at the University of Queensland (*n* = `r nrow(filter(df, university_recoded == "University of Queensland"))`), University of Adelaide (*n* = `r nrow(filter(df, university_recoded == "University of Adelaide"))`), and the University of Bath (*n* = `r nrow(filter(df, university_recoded == "University of Bath"))`).
-While, the majority of participants (*n* = `r nrow(filter(df, degree_type == "Non-psychology"))`) indicated that they were enrolled in a non-psychology degree such as a Bachelor of Science or Bachelor of Arts (*n* = `r nrow(filter(df, degree_recoded == "Bachelor of Science"))`, *n* = `r nrow(filter(df, degree_recoded == "Bachelor of Arts"))` respectively), most were completing a psychology major (*n* = `r nrow(filter(df, major_recoded == "Psychology"))`).
+attended high school, fewer than half completed psychology courses in 
+high school (*n* = `r hs_psyc[2,2]`). Most reported their nationality as being from Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = `r nationality[24,2]`), or China
+(*n* = `r nationality[6,2]`). About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`).
+
+```{r qual responses}
+
+# [breadcrumbs] 
+ # once qual responses are coded, I will need to return here to 
+ # include details about which univrsity the participant is enrolled in
+ # name of qualification
+ # major [how many are majoring in psyc; NAs; will decide later?]
+
+```
 
@@
 -->
-The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." There were 20 scenarios in total (see Table \@ref(tab:norm_counternorm_items)).
+The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing.
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [e.g., @TQMP16-4-376, @rubinWhenDoesHARKing2017, @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
+
+There were 20 scenarios in total (see Table \@ref(tab:norm_counternorm_items)).
 Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
@@
 We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world.
-To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" The ten characteristics explicitly described each of the ten open science practices (see Table XX).
+To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm-counternorm pairs described above, albeit with one norm excluded on the basis of not referring to externally observable behaviour (critically evaluating published studies vs.
+accepting them), and one practice added out of interest (data sharing on request).
+(see Table XX).
 Participants were given a slider bar ranging from 0% to 100% to record their estimate.
@@
 
-In line with our preregisterd analysis plan, we calculated the difference in means
+In line with our preregistered analysis plan, we calculated the difference in means
 between responses to each norm item and its accompanying counternorm, along with 
@@
 However, the extent to which participants endorsed open science norms varied very substantially across different practices.
-In terms of open science norms, participants most strongly endorsed the idea that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4).
-They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items were all between 3.5 and 4 (4 representing 'agree').
-On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review, and to a lesser extent with sharing open data.
+Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing 'agree').
+They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items were all between 3.5 and 4.
+On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.
 The practice of registered reports was the one about which participants were most equivocal, with very similar levels of agreement (near the midpoint of 3) with both norm and counternorm for this item.
@@
 
-Unsurprisingly, there were fairly substantial negative correlations between the norm and counternorm pairs, although this was not the case for all pairs: For the norm and counternorm items relating to preregistrations, the correlation was `r sprintf('%.2f', cor(df$prereg_norm, df$prereg_cnorm))`.
-Similarly for the norm and counternorm items relating to HARKing, the correlation was negative but very small.
+Unsurprisingly, there were substantial negative correlations between most norm and counternorm pairs, with the exception of the norm and counternorm items relating to preregistrations and HARKing.
 
@@
 practice_means_corr <- practice_means_corr %>% 
-  rename(Practice = practice) %>% 
-  dplyr::select(-c(estimate, conf.low, conf.high)) %>% 
+  mutate(Practice = practice) %>% 
+  dplyr::select(-c(practice,estimate, conf.low, conf.high)) %>% 
   relocate (Practice, .before = Norm) %>% 
@@
 
+# breadcrumbs: keep the values that I need from this tibble
+# use p_tidy? to clean up the pvalues {done!}
+# round the corr & CI {done!}
+# join with the practice_means tibble & turn into a table {done!}
+# need to figure out whether I can rotate a page in papaja
+
+# just keeping this here for now, but will be able to delete
+# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
+# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
+# 
+# hark_corr <- round(cor(df$hark_norm, df$hark_cnorm),2)
+# hark_CI <- round(CIr(r = hark_corr, n = nrow(df), level = 0.95),2)
+# 
+# info_for_rep_corr <- round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)
+# info_for_rep_CI <- round(CIr(r = info_for_rep_corr, n = nrow(df), level = 0.95),2)
+# 
+# open_access_corr <- round(cor(df$open_access_norm, df$open_access_cnorm),2)
+# open_access_CI <- round(CIr(r = open_access_corr, n = nrow(df), level = 0.95),2)
+# 
+# open_data_corr <- round(cor(df$open_data_norm, df$open_data_cnorm),2)
+# open_data_CI <- round(CIr(r = open_data_corr, n = nrow(df), level = 0.95),2)
+# 
+# open_materials_corr <- round(cor(df$open_materials_norm, df$open_materials_cnorm),2)
+# open_materials_CI <- round(CIr(r = open_materials_corr, n = nrow(df), level = 0.95),2)
+# 
+# phack_corr <- round(cor(df$phack_norm, df$phack_cnorm),2)
+# phack_CI <- round(CIr(r = phack_corr, n = nrow(df), level = 0.95),2)
+# 
+# preprint_corr <- round(cor(df$preprint_norm, df$preprint_cnorm),2)
+# preprint_CI <- round(CIr(r = preprint_corr, n = nrow(df), level = 0.95),2)
+# 
+# prereg_corr <- round(cor(df$prereg_norm, df$prereg_cnorm),2)
+# prereg_CI <- round(CIr(r = prereg_corr, n = nrow(df), level = 0.95),2)
+
 # breadcrumbs: 
-# need to figure out whether I can rotate a page in papaja
 # I need to use apa_tables.... (in line with papaja)
+# pull means & sd into the same column with (sd) in parentheses [done!]
+# headings should then be norm, counternorm, difference [done!]
+# add correlations with 95% CIs 
 # update practice descriptions so they make sense to readers
@@
 
-## Norms in practice
-Participants were also asked to estimate the proportion of psychology studies estimated globally which apply ten practices.
-These practices corresponded approximately to the ten norm-counternorm pairs, albeit with one norm excluded on the basis of not referring to behaviour (critically evaluating published studies vs.
-accepting them), and one practice added out of interest (data sharing on request).
-For many of these practices, participants estimates were near the midpoint of 50%.
-This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
-Participants seemed to perceive that the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
-It is perhaps fair to say that participants' mean estimate that `r paste(round(mean(df$detailed_methodology, na.rm = TRUE), 2), "%", sep = "")` of studies have this characteristic represents a rather optimistic projection.
+```{r correlation_matrix}
+#pairs.panel etc. won't really work because there are too many variables
+#And we only need corrs between matched pairs
+#So doing this a bit more manually
+layout(matrix(1:8, ncol = 4))
 
-```{r norms in practice}
+plot(df$critical_norm ~ jitter(df$critical_cnorm), xlab = "critical counternorm", ylab = "critical norm")
+abline(lm(df$critical_norm ~ df$critical_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$critical_norm, df$critical_cnorm),2)))
 
-# select columns that relate to norms in practice & pivot it long & drop the na values
-in_prac_long <- df %>% 
-  dplyr::select(c(id,preregistration:open_access)) %>% 
-      pivot_longer (cols = -id,
-                names_to = "practice",
-                values_to = "prevalence rating") %>% 
-  drop_na()
+plot(df$prereg_norm ~ jitter(df$prereg_cnorm), ylab = "Prereg norm", xlab = "Prereg counternorm")
+abline(lm(df$prereg_norm ~ df$prereg_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$prereg_norm, df$prereg_cnorm),2)))
 
-# get the n values for each of the practices
-in_prac_counts <- in_prac_long %>% 
-  dplyr::group_by(practice) %>% 
-  count() %>% 
-  ungroup()
+plot(df$reg_report_norm ~ jitter(df$reg_report_cnorm), ylab = "Reg Reports norm", xlab = "Reg Reports counternorm")
+abline(lm(df$reg_report_norm ~ df$reg_report_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$reg_report_norm, df$reg_report_cnorm),2)))
 
-# calculate means
-in_prac_ms_sds <- in_prac_long %>%
-  dplyr::group_by(practice) %>%
-  summarise(mean = mean(`prevalence rating`),
-            sd = sd(`prevalence rating`)) %>%
-  ungroup()
+plot(df$phack_norm ~ jitter(df$phack_cnorm), ylab = "p-hacking rnorm", xlab = "p-hacking counternorm")
+#potential confusion here about direction of phrasing (pro p-hacking = counternorm?)
+abline(lm(df$phack_norm ~ df$phack_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$phack_cnorm, df$phack_norm),2)))
 
-# join the n values with the means
-in_prac_means <- in_prac_counts %>% inner_join(in_prac_ms_sds)
+plot(df$hark_norm ~ jitter(df$hark_cnorm), ylab = "HARKing norm", xlab = "HARKing counternorm")
+abline(lm(df$hark_norm ~ df$hark_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$hark_cnorm, df$hark_norm),2)))
 
-# calculate 95% CIs
-error <- qnorm(0.975) * in_prac_means$sd/sqrt(in_prac_means$n)
-in_prac_means$lower <- in_prac_means$mean - error
-in_prac_means$upper <- in_prac_means$mean + error
+plot(df$info_for_rep_norm ~ jitter(df$info_for_rep_cnorm), ylab = "Replicability norm", xlab = "Replicability counternorm")
+abline(lm(df$info_for_rep_norm ~ df$info_for_rep_cnorm), col = "blue")
+legend(x='right', legend=paste('Cor =', round(cor(df$info_for_rep_norm, df$info_for_rep_cnorm),2)))
 
-# combine means & SDs
-in_prac_means$`Prevalence Ratings` <- paste0(round_tidy(in_prac_means$mean,2),
-                          " (", 
-                          round_tidy(in_prac_means$sd,2),
-                            ")", 
-                            " [",
-                            round_tidy(in_prac_means$lower,2),
-                            ", ", 
-                            round_tidy(in_prac_means$upper,2),
-                            "]")
+plot(df$preprint_norm ~ jitter(df$preprint_cnorm), ylab = "Preprints norm", xlab = "Preprints counternorm")
+abline(lm(df$preprint_norm ~ df$preprint_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$preprint_norm, df$preprint_cnorm,
+                                                       use = "pairwise.complete.obs"),2)))
 
-# clean it up into a new dataframe with only the columns we need
-in_practice_means <- in_prac_means %>% 
-  dplyr::select(practice, `Prevalence Ratings`) %>% 
-  rename(Practice = practice)
+plot(df$open_materials_norm ~ jitter(df$open_materials_cnorm), ylab = "Open materials norm", xlab = "Open materials counternorm")
+abline(lm(df$open_materials_norm ~ df$open_materials_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_materials_norm, df$open_materials_cnorm, use = "pairwise.complete.obs"),2)))
 
-# breadcrumbs:
-# I need to use apa_tables.... (in line with papaja)
-# update practice descriptions so they make sense to readers
+plot(df$open_data_norm ~ jitter(df$open_data_cnorm), ylab = "Open data norm", xlab = "Open data counternorm")
+abline(lm(df$open_data_norm ~ df$open_data_cnorm), col = "blue")
+legend(x='bottomleft', legend=paste('Cor =', round(cor(df$open_data_norm, df$open_data_cnorm),2)))
 
-knitr::kable(in_practice_means,
-             caption = "Means, standard deviations, and 95% confidence intervals for the prevalence ratings for each research practice",
-             digits = 2,
-             align = c('lc'))
+plot(df$open_access_norm ~ jitter(df$open_access_cnorm), ylab = "Open access norm", xlab = "Open access counternorm")
+abline(lm(df$open_access_norm ~ df$open_access_cnorm), col = "blue")
+legend(x='bottomright', legend=paste('Cor =', round(cor(df$open_access_norm, df$open_access_cnorm),2)))
 
@@
 
+## Norms in practice
+Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices.
+For many of these practices, participants’ estimates were near the midpoint of 50%.
+This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
+Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
+
 <!-- There's a key point for the discussion here, I think, in that the fact that many participants guessed near 50% for these practices suggests that students may have little idea of the prevalence of these practices in reality, and certainly education is needed on that point.
 
-We can add a table here with descriptive statistics (means? more?) for the norms in practice items.
+<!-- Add another paragraph here to elaborate on the shape of these distributions to help interpret the above point of discussion.-->
 
@@
 ## The replication crisis
-Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis", with `r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% missing.
+Interestingly, the vast majority of participants had not heard of "the replication crisis" <!-- add numeric estimate-->.
 
-```{r crisis descriptions, eval=FALSE, include=FALSE}
-write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
-crisis_descriptions = read.csv("crisis_descriptions_marked.csv") #categorised as accurate or not
-```
+<!-- For people who answered "yes" (they had heard the term) there were a couple of open-ended follow-up items: What do you think the replication is?
+Which scientific disciplines do you think are most affected by the replication crisis?
+We could analyse these and try to give some indication of whether the students who *had* heard of it actually knew what the term refers to.
+-->
 
-<!-- This needs another csv file in order to run the code above. Also, revise where the csv file is written to and loaded from.  -->
+Participants' estimates of the replicability of psychological studies was near the midpoint of the possible range <!-- about 56% - need to code this in--> .
 
-Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"?
-Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term.
-Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
-Just `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
+<!--Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
+However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
+-->
 
-Participants' estimates of the replicability of psychological studies were variable.
-The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`.
-A histogram of participants' responses is provided in Figure X.
-
-```{r rep_perc_histogram}
-hist(df$rep_perc, main = NULL, xlab = "Percentage")
-```
-_Figure X_.
-Histogram of participants' responses to the question: "Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
-We call repeating a study like this a “replication study”.
-At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?" Responses provided on a visual slider.
-
-<!-- Participants were also asked "Which scientific disciplines do you think are most affected by the replication crisis?" As we discussed, I'm not sure this response will really be useful to look at given that we have "primed" them to think of psychology as being most affected (and indeed that's what the responses largely indicate).-->
+<!-- ☐ On the above point, Comment here on the shape of the distribution for this question. -->
 
@@
 
-Our findings suggest that despite fairly significant media attention, most incoming psychology students are unaware of the replication crisis in psychology.
-In our study they tended to agree more with open science norms than they did counternorms, although this wasn't the case for all open science practices (and especially not sharing of preprints).
+Despite efforts to popularize the replicability of research the past decade, and despite popular media attention, most incoming psychology students in our sample were unaware of the replication crisis.
+Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms, although this wasn't the case for all open science practices (namely sharing of pre-prints and avoiding HARKing).
+IIt may be interesting to consider whether student norms regarding the sharing of pre-prints would be expected to have shifted since this data was collected given the rapid increase in the dissemination of pre-prints related to COVID-19.
 
-Participants' estimates of the proportion of psychological studies published each which apply each of a set of ten open science practices mostly tended to hover near 50%.
-Although this could be read as implying literally that participants believe these practices are roughly as commonly applied as they are not, it could also be read as implying a great deal of uncertainty on the part of participants [might need to unpack this idea - i.e., that if people have no idea they'll probably pick 50%].
+Participants' estimates of the proportion of psychological studies published which apply each of a set of ten open science practices tended to hover around a mean of 50%.
+Although this could be read as implying literally that participants believe these practices are roughly as commonly applied as they are not, it could also be read as implying a great deal of uncertainty on the part of participants.
+Indeed, some practices, “open access publication”, “data availability”, and “incomplete results” had a modal response of 50%, indicating that many students either literally perceived that these practices are as commonly applied as not, or selected a respon as near 50% as an indicator of indifference or uncertainty.
+In contrast, other practices with a mean response near 50% (e.g.
+registered reports) were not normally distributed around the scale midpoint.
+Instead, participants demonstrated substantial lack of agreement about the frequency of this practice.
+While the modal values were 60% (n=13) and 80% (n=13), there was also frequent endorsement of 40% (n=12), 20% (n=11) and 70% (n=11).
+As a result, it appears that there is substantial lack of consensus with regard to the practice of open access publication.
 
@@
 
-<!--
-Obviously more to say - just starting with a very rough summary.
--->
+## Limitations, strengths, and future directions
 
-## Strengths and limitations
-Our study had a relatively large sample size, but used convenience/haphazard sampling.
-The results also reflect responses of just one sample of students at one point in time.
-Generalisations to a wider population of incoming students (or students beginning psychology students in the future) can be made only very tentatively.
-Our questions also focused primarily on attitudes and beliefs, rather than probing students' factual knowledge of findings or concepts.
+Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings.
+Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only very tentative generalisations to a wider population of incoming psychology students.
+However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open-data to research practice.
+
+Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process.
+However, we did not probe students' factual knowledge of methodological findings or concepts.
+It’s quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) open science considerations without necessarily impacting their attitudes and beliefs.
+Yet, research at the tertiary level casts doubt that the disciplinary reform from the past 2 decades has had much impact on the content of our teaching (Friedrich et al., 2018).
 

### 2021-09-10 analysis/Manuscript.Rmd
moved histogram to supplemental

--- 2021-09-09 analysis/Manuscript.Rmd
@@
 
-# # import the metadata [check if I need it for these analyses?]
-# metadata <- here::here("survey", "data", "os_metadata_raw_data.csv") %>% 
-#   read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
-#   filter(!is.na(OldVariable))
+# import the metadata 
+metadata <- here::here("survey", "data", "students_metadata.csv") %>% 
+ read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
+ filter(!is.na(old_variable)) %>% 
+ dplyr::select (-c("...10", "note:"))
 ```
@@
 # gender --> need to summarise once we've recoded it in preprocessing script
-  # [breadcrumb]
 gender <- df %>% dplyr::count(gender)
@@
              "Deborah should submit her study to a journal to be checked by experts (peer reviewed) only after she has finished collecting and analysing her data."))
+
+# [breadcrumb Sept 10: pull in this info from the meta data]
+
+# recode the data so the response options have proper labels
+
+# c <- metadata %>% 
+#     filter(Scale == "OSmost") %>% 
+#     filter(NewVariable != "OSmost_text") #remove this value from metadata
+# 
+# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>% 
+#   rename ("OSmost_label" = "ItemText")
 
@@
 
-```{r norms in practice histogram}
-
-p <- in_prac_long %>%
-  ggplot(aes(x = `prevalence rating`)) +
-  geom_histogram(aes(y=stat(count)), binwidth = 10) +
-    xlab("Prevalence Ratings (%)") +
-    ylab("Frequency") +
-    facet_wrap(~practice)
-p
-
-#[breadcrumb: need to update the theme & the practice names]
-
-```
-
 <!-- There's a key point for the discussion here, I think, in that the fact that many participants guessed near 50% for these practices suggests that students may have little idea of the prevalence of these practices in reality, and certainly education is needed on that point.
@@
 
+# Supplemental Materials
+
+Figure XX displays the histograms for each of the norms in practice items.
+
+```{r norms in practice histogram}
+
+p <- in_prac_long %>%
+  ggplot(aes(x = `prevalence rating`)) +
+  geom_histogram(aes(y=stat(count)), binwidth = 10) +
+    xlab("Prevalence Ratings (%)") +
+    ylab("Frequency") +
+    theme_classic () +
+    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
+    facet_wrap(~practice, nrow = 2)
+p
+
+#[breadcrumb: need to update the theme & the practice names]
+
+```
+
 \newpage

### 2021-09-28 analysis/Manuscript.Rmd
Integrated Google Docs copy with RMarkdown

--- 2021-09-10 analysis/Manuscript.Rmd
@@
   role: null
+- name: Emily Kothe
+  affiliation: '3'
+  role: null
 shorttitle: Psychology students' beliefs about open science
@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-  Enter author note here.
-
-# Abstract: |
-
+  1 Flinders University, Australia
+  2 Massey University, New Zealand
+  3 Deakin University, Australia
+abstract: |
 ## BACKGROUND: Rapid changes to methodological best practices present significant challenges for educating students new to the field of psychology.
@@
 
-Keywords: open science, psychology, teaching, reproducibility, replication
+keywords: open science, psychology, teaching, reproducibility, replication
 wordcount: X
-
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
@@
   institution: Massey University
+editor_options: 
+  chunk_output_type: console
 ---
+
+<!--
+Teaching in Psychology ask for structured abstracts - 'For these types of article submissions, please include (in this order) a section on the background, objective(s), method, results, conclusion, and teaching implications.' 200 word limit
+The abstract also doesn't currently knit into the final document for some reason?
+
+-->
+
 <!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
@@
 
-# # import the metadata [check if I need it for these analyses?]
-# metadata <- here::here("survey", "data", "os_metadata_raw_data.csv") %>% 
-#   read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
-#   filter(!is.na(OldVariable))
+# import the metadata 
+#metadata <- here::here("survey", "data", "students_metadata.csv") %>% 
+ #read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
+ #filter(!is.na(old_variable)) %>% 
+ #dplyr::select (-c("...10", "note:"))
+
+#MW: I have commented this chunk out out temporarily because it might need tweaking - it assumes a subfolder in "survey" called "data"
+#and the last select line doesn't seem to run (no column with that name recognised)
 ```
@@
 Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
-Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe; vazireWhereAreSelfcorrecting2020].
+Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe2019; @vazireWhereAreSelfcorrecting2020].
 For example, the practice of sharing open source software corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.
@@
 
+<!--I feel like citing tweets is going to cause arguments with a reviewer, but not sure what else to do here.-->
+
 For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
@@
 This study is exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.
+
+<!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology?
+Also, if anyone else has any good citations on the value of exploratory research, can you let me know?
+-->
 
@@
 
+<!-- It's common to put participants first, but might the description flow more smoothly if we put that short Procedure subsection first?
+That way they know how we recruited people before we get to thinks like exclusions and screening -->
+
 Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
@@
 
-Of the remaining `r n` participants, most reported being
+Most participants reported that they were
 18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
 reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
-`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old.
+`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
+`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
+their gender identity as "queer man", and `r gender[3,2]` participant reported 
+non-binary gender.
 
-The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
-`r gender[2,2]` reported that they were male, `r gender[3,2]` participants reported 
-their gender identity as "queer man", and `r gender[3,2]` participants reported 
-non-binary gender.^[While the response "queer man" could potentially be coded as
+<!--We had a footnote here (below) but given the word limit it might be safely left out unless a reviewer queries it...
+
+^[While the response "queer man" could potentially be coded as
 "male", we are aware that some individuals who report gender in this way would
@@
 response in order to provide a faithful representation of the participant's 
-self-reported gender.]
+self-reported gender.] -->
 
@@
 
-```{r qual responses}
-
-# [breadcrumbs] 
- # once qual responses are coded, I will need to return here to 
- # include details about which univrsity the participant is enrolled in
- # name of qualification
- # major [how many are majoring in psyc; NAs; will decide later?]
-
-```
+<!--
+MP: Seems like we are missing some nationalities here – US nationalities? NZ? Or is this just the top 3?
+-->
 
@@
 -->
-The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing.
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [e.g., @TQMP16-4-376, @rubinWhenDoesHARKing2017, @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
+The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
 
@@
 
-<!-- Add Table X of norms and counternorms statements that map to each practice -->
+<!-- Add Table X of norms and counternorms statements that map to each practice 
+MW: The table captions/crossreferences may not be working - see the compiled document.
+-->
 
@@
 
-knitr::kable(norm_items,
+# [breadcrumb Sept 10: pull in this info from the meta data]
+
+# recode the data so the response options have proper labels
+
+# c <- metadata %>% 
+#     filter(Scale == "OSmost") %>% 
+#     filter(NewVariable != "OSmost_text") #remove this value from metadata
+# 
+# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>% 
+#   rename ("OSmost_label" = "ItemText")
+
+norm_items_wide <- pivot_wider(
+  norm_items,
+  names_from = Category,
+  values_from = Item)
+
+knitr::kable(norm_items_wide,
              caption = "Norm and counternorm items",
@@
 
+<!--MW: We need to add in the actual numbers of collaborators/institutions above - we should have a record somewhere in our Google Drive-->
+
 ## Data analysis
+<!--MW: We had this subheading in here but might not need it? The analysis is pretty clear from the descripion below-->
 
@@
 and the difference values.
-
-\@ref(tab:chunk-name)
 
@@
 Unsurprisingly, there were substantial negative correlations between most norm and counternorm pairs, with the exception of the norm and counternorm items relating to preregistrations and HARKing.
+
+<!--MW: The paragraphs above contain some numeric info that's written in manually rather than being R outputs (e.g., "three", "seven") 
+Not sure if that's a worry.
+-->
 
@@
 
+```{r norms in practice}
+
+# select columns that relate to norms in practice & pivot it long & drop the na values
+in_prac_long <- df %>% 
+  dplyr::select(c(id,preregistration:open_access)) %>% 
+      pivot_longer (cols = -id,
+                names_to = "practice",
+                values_to = "prevalence rating") %>% 
+  drop_na()
+
+# get the n values for each of the practices
+in_prac_counts <- in_prac_long %>% 
+  dplyr::group_by(practice) %>% 
+  count() %>% 
+  ungroup()
+
+# calculate means
+in_prac_ms_sds <- in_prac_long %>%
+  dplyr::group_by(practice) %>%
+  summarise(mean = mean(`prevalence rating`),
+            sd = sd(`prevalence rating`)) %>%
+  ungroup()
+
+# join the n values with the means
+in_prac_means <- in_prac_counts %>% inner_join(in_prac_ms_sds)
+
+# calculate 95% CIs
+error <- qnorm(0.975) * in_prac_means$sd/sqrt(in_prac_means$n)
+in_prac_means$lower <- in_prac_means$mean - error
+in_prac_means$upper <- in_prac_means$mean + error
+
+# combine means & SDs
+in_prac_means$`Prevalence Ratings` <- paste0(round_tidy(in_prac_means$mean,2),
+                          " (", 
+                          round_tidy(in_prac_means$sd,2),
+                            ")", 
+                            " [",
+                            round_tidy(in_prac_means$lower,2),
+                            ", ", 
+                            round_tidy(in_prac_means$upper,2),
+                            "]")
+
+# clean it up into a new dataframe with only the columns we need
+in_practice_means <- in_prac_means %>% 
+  dplyr::select(practice, `Prevalence Ratings`) %>% 
+  rename(Practice = practice)
+
+# breadcrumbs:
+# I need to use apa_tables.... (in line with papaja)
+# update practice descriptions so they make sense to readers
+
+knitr::kable(in_practice_means,
+             caption = "Means, standard deviations, and 95% confidence intervals for the prevalence ratings for each research practice",
+             digits = 2,
+             align = c('lc'))
+
+```
+
 <!-- There's a key point for the discussion here, I think, in that the fact that many participants guessed near 50% for these practices suggests that students may have little idea of the prevalence of these practices in reality, and certainly education is needed on that point.
 
-<!-- Add another paragraph here to elaborate on the shape of these distributions to help interpret the above point of discussion.-->
+We can add a table here with descriptive statistics (means? more?) for the norms in practice items.
 
@@
 ## The replication crisis
-Interestingly, the vast majority of participants had not heard of "the replication crisis" <!-- add numeric estimate-->.
+Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis", with `r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% missing.
 
-<!-- For people who answered "yes" (they had heard the term) there were a couple of open-ended follow-up items: What do you think the replication is?
-Which scientific disciplines do you think are most affected by the replication crisis?
-We could analyse these and try to give some indication of whether the students who *had* heard of it actually knew what the term refers to.
--->
+Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"?
+Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term.
+Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
+Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
 
-Participants' estimates of the replicability of psychological studies was near the midpoint of the possible range <!-- about 56% - need to code this in--> .
+Participants' estimates of the replicability of psychological studies were variable.
+The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`.
+A histogram of participants' responses is provided in Figure X.
 
-<!--Point for discussion: Interestingly, this estimate is fairly consistent (albeit perhaps slightly more optimistic) than empirical estimates from large-scale studies.
-However, it could plausibly simply reflect a great deal of uncertainty on the part of participants.
--->
+```{r rep_perc_histogram}
+hist(df$rep_perc, main = NULL, xlab = "Percentage")
+```
+_Figure X_.
+Histogram of participants' responses to the question: "Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+We call repeating a study like this a “replication study”.
+At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?" Responses provided on a visual slider.
 
-<!-- ☐ On the above point, Comment here on the shape of the distribution for this question. -->
+<!-- Participants were also asked "Which scientific disciplines do you think are most affected by the replication crisis?" As we discussed, I'm not sure this response will really be useful to look at given that we have "primed" them to think of psychology as being most affected (and indeed that's what the responses largely indicate).-->
 
@@
 Despite efforts to popularize the replicability of research the past decade, and despite popular media attention, most incoming psychology students in our sample were unaware of the replication crisis.
-Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms, although this wasn't the case for all open science practices (namely sharing of pre-prints and avoiding HARKing).
-IIt may be interesting to consider whether student norms regarding the sharing of pre-prints would be expected to have shifted since this data was collected given the rapid increase in the dissemination of pre-prints related to COVID-19.
+Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms.
+Notably this wasn't the case for all open science practices (namely sharing of pre-prints and avoiding HARKing).
+It may be interesting to consider whether student norms regarding the sharing of pre-prints would be expected to have shifted since this data was collected given the rapid increase in the dissemination of pre-prints related to COVID-19.
+On the other hand, it may well be that scientific training has enshrined the practices of peer review and generating hypotheses after analyses (e.g., Bem, 2004) as essential scientific practices that are robust to change.
+
+<!--Bem begins his guide for writing articles as, “There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
+They are rarely the same, and the correct answer is (b).”-->
 
@@
 
+<!-- MW: Should that last bit say registered reports?
+There's also quite a bit of manually written numeric info here - we should probably convert that to R code?
+-->
+
 Overall these findings suggest that while incoming psychology students may have a degree of sympathy for open science norms, they know relatively little about replicability and open science.
 
-## Limitations, strengths, and future directions
+<!-- Since the journal asks for a Teaching Implications subsection in the structured abstract, I'm thinking it'd make sense to have a Teaching Implications subsection in the discussion, about here?
+-->
 
+## Strengths and limitations
 Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings.
@@
 It’s quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) open science considerations without necessarily impacting their attitudes and beliefs.
-Yet, research at the tertiary level casts doubt that the disciplinary reform from the past 2 decades has had much impact on the content of our teaching (Friedrich et al., 2018).
+Yet, research at the tertiary level casts doubt that the disciplinary reform from the past 2 decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].
 
 <!--
-More to say here.
+MW: The bit from "It's quite possible..." is sensible, but if needed could possibly shave some words off by excluding? 
+See how we go when we check full word count
 -->
@@
 ## Directions for future research
+
+# Supplemental Materials
+
+Figure XX displays the histograms for each of the norms in practice items.
+
+```{r norms in practice histogram}
+
+p <- in_prac_long %>%
+  ggplot(aes(x = `prevalence rating`)) +
+  geom_histogram(aes(y=stat(count)), binwidth = 10) +
+    xlab("Prevalence Ratings (%)") +
+    ylab("Frequency") +
+    theme_classic () +
+    theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
+    facet_wrap(~practice, nrow = 2)
+p
+
+#[breadcrumb: need to update the theme & the practice names]
+
+```
 
@@
 We used `r cite_r("r-references.bib")` for all our analyses.
+
+<!-- This is nice to do, but it generate a 150+ word paragraph of citations to packages, including citations to packages our code doesn't directly use (e.g.
+nlme, multilevel, etc.).
+We might need to cut it down manually to a more concise list?
+-->
 

### 2021-09-28 preprocessing/preprocessing_students.R

@@ -56,7 +56,7 @@ df_lab <- here::here("survey", "data", "students_raw_data_with_labels.csv") %>%
 
 # load metadata
 metadata <- read_csv(here::here("data", "students_metadata.csv")) %>%
-  dplyr::select(-c(X10,"note:")) %>%  # delete unnecessary columns
+  #dplyr::select(-c(X10,"note:")) %>%  # delete unnecessary columns
   filter(old_variable != "NA", old_variable != "exclude") # remove the instruction variables
 
 #### CLEAN DATA ####

### 2021-10-05 analysis/Manuscript.Rmd
Trying to get ms nearly ready for submission, including word count reductions

@@
 abstract: |
-## BACKGROUND: Rapid changes to methodological best practices present significant challenges for educating students new to the field of psychology.
-Some students may have existing knowledge about recent methodological reforms (e.g., preregistration, replication).
-Yet, where knowledge is lacking, overemphasizing the problems that precipitate these reforms (e.g., p-hacking, HARKing) may lead students to de-value scientific methods as a credible means for generating knowledge.
-## OBJECTIVE: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
-## METHOD: This study examined ### incoming undergraduate psychology students’ understandings of how research *should* be conducted (norms) and how they believed research *is* conducted (practice) using an online survey.
-## RESULTS: We found that XXX. . .
-## CONCLUSION:
+## BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
+## OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology. 
+## METHOD: International online survey with participants who were about to start their first course in psychology (N = 239) .
+## RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices.
+When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%.
+Only 18% of participants had heard of the term "replication crisis".
+## CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term.
+Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
+## TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
 
@@
 Teaching in Psychology ask for structured abstracts - 'For these types of article submissions, please include (in this order) a section on the background, objective(s), method, results, conclusion, and teaching implications.' 200 word limit
+Abstract currently includes hand-typed numbers because it's hard to get them to knit up here since data processing is further below.
 The abstract also doesn't currently knit into the final document for some reason?
@@
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe2019; @vazireWhereAreSelfcorrecting2020].
-For example, the practice of sharing open source software corresponds to the Mertonian norm of *communism*: Scientists should have common ownership of scientific goods.
-Similarly, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
+For example, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
 Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
-In this sense, the ongoing reform in psychological research can partly be understood as simultaneously a set of new practices and a re-affirmation of established norms.
 
@@
 
-Second, when psychology students are beginning their university studies, they are often learning for the first time about how and why it is useful to apply scientific methods to studying human behaviour (rather than only relying on alternative sources of knowledge such as intuition or anecdote or authority).
-An emphasis on problems with replicability could at least in principle leave these students unconvinced that scientific methods for studying human behaviour are valuable *at all*, leaving them to favour even less credible alternative sources of knowledge.
-For instance, @chopikHowWhetherTeach2018 found that undergraduate students tended to trust the results of psychological studies *less* after a one-hour educational lecture about the replication crisis.
-This said, the effect of the lecture on trust of psychological studies was relatively small (d = -.36), and mean trust levels remained fairly high after the lecture (M = 4.94 on a scale of 1 to 7).
-Knowledge about incoming students’ “baseline” perceptions of the replicability of psychological science could further inform teachers about the salience of this risk.
-
-Third, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice [e.g.
-see tweets on this topic: @buraktuncaUygunTuncRmounce2021; @duyguuygun-tuncLastNightWas2021].
+Second, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice.
 This could imply a need for educators to reinforce and build on students “naive” impressions rather than radically altering their understanding of how science should be done.
@@
 For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values.
-The extent to which incoming psychology students may - or may not - typically be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
+The extent to which incoming psychology students may - or may not - be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
 
-<!--I feel like citing tweets is going to cause arguments with a reviewer, but not sure what else to do here.-->
-
-For these reasons, we aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
+We therefore aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
 Our survey encompassed questions norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is).
-In doing so we hope to provide knowledge which can inform the pedagogy of teaching about replication and open science practices.
-This study is exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.
+Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.
+We nevertheless preregistered our aims, sampling plan, exclusion criteria and data analysis plan at https://osf.io/6e2ux/?view_only=b5173ba3bf564bc495686cd0845e678b
 
 <!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology?
-Also, if anyone else has any good citations on the value of exploratory research, can you let me know?
 -->
@@
 <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+
+<!--MW: We need to include a link for accessing raw data and measures etc. -->
 
@@
 
+## Procedure
+
+Collaborators from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics.
+An invitation was sent to participants via email or a course website 1-2 weeks before their course began.
+The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month, and included a link to the survey.
+
+Ethical approval for this study was granted by (institution blinded).
+
+<!--MW: I've moved Procedure up above Participants - I think that works better for flow since otherwise we have to describe screening within the survey before we've introduced the survey itself.
+Hope this is ok.-->
+
 ## Participants
-
-<!-- It's common to put participants first, but might the description flow more smoothly if we put that short Procedure subsection first?
-That way they know how we recruited people before we get to thinks like exclusions and screening -->
 
@@
 of study in psychology at a university within the next month. For those individuals 
-who were screened out, our Qualtrics program automatically directed them to the 
-debriefing form.
+who were screened out, Qualtrics automatically directed them to a 
+debriefing
 
@@
 <!-- Mention here our discussions workshopping of common open science norms at SIPs?
-!
 -->
-The open science practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
+The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
 Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
@@
 
-We also sought to measure participants' normative beliefs about how psychological science was actually conducted by researchers around the world.
+We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world.
 To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm-counternorm pairs described above, albeit with one norm excluded on the basis of not referring to externally observable behaviour (critically evaluating published studies vs.
@@
 
-## Procedure
-
-Collaborators/Contributors/Colleagues from ## tertiary institutions in Australia (n=), New Zealand (n=), the UK (n=), and the USA (n=) invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics (CITE?).
-An invitation was sent to participants via email or a course website 1-2 weeks before their course began.
-After completing demographic information, participants completed measures of Open Science Norms and Counternorms, Norms in Practice, and Beliefs about Replications in that order.
-At the conclusion of the study participants were invited to share any comments about the survey before they were thanked for their participation and provided an informative debriefing about the aims of the study and links to further reading about open science practices in psychology.
-The survey took most participants approximately #-# minutes to complete.
-
-<!--MW: We need to add in the actual numbers of collaborators/institutions above - we should have a record somewhere in our Google Drive-->
-
-## Data analysis
-<!--MW: We had this subheading in here but might not need it? The analysis is pretty clear from the descripion below-->
-
 # Results
@@
 On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.
-The practice of registered reports was the one about which participants were most equivocal, with very similar levels of agreement (near the midpoint of 3) with both norm and counternorm for this item.
-This may be relatively unsurprising, given that the registered reports are perhaps the most recent innovation in the list of practices.
-
-Unsurprisingly, there were substantial negative correlations between most norm and counternorm pairs, with the exception of the norm and counternorm items relating to preregistrations and HARKing.
 
@@
 
-<!-- There's a key point for the discussion here, I think, in that the fact that many participants guessed near 50% for these practices suggests that students may have little idea of the prevalence of these practices in reality, and certainly education is needed on that point.
-
-We can add a table here with descriptive statistics (means? more?) for the norms in practice items.
-
--->
-
 ## The replication crisis
@@
 
-Despite efforts to popularize the replicability of research the past decade, and despite popular media attention, most incoming psychology students in our sample were unaware of the replication crisis.
+Despite efforts to improve the replicability of research the past decade, and corresponding media attention, most incoming psychology students in our sample were unaware of the replication crisis.
 Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms.
-Notably this wasn't the case for all open science practices (namely sharing of pre-prints and avoiding HARKing).
-It may be interesting to consider whether student norms regarding the sharing of pre-prints would be expected to have shifted since this data was collected given the rapid increase in the dissemination of pre-prints related to COVID-19.
-On the other hand, it may well be that scientific training has enshrined the practices of peer review and generating hypotheses after analyses (e.g., Bem, 2004) as essential scientific practices that are robust to change.
+Notably this wasn't the case for all open science practices (namely sharing of pre-prints and open data).
+It may well be that scientific training has enshrined peer review as an essential practice that is robust to change.
 
 <!--Bem begins his guide for writing articles as, “There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b).”-->
+They are rarely the same, and the correct answer is (b).”
+MW: I think the Bem paper would work here if students tended to be pro-HARKing but they tended to be against it.
+-->
 
 Participants' estimates of the proportion of psychological studies published which apply each of a set of ten open science practices tended to hover around a mean of 50%.
-Although this could be read as implying literally that participants believe these practices are roughly as commonly applied as they are not, it could also be read as implying a great deal of uncertainty on the part of participants.
-Indeed, some practices, “open access publication”, “data availability”, and “incomplete results” had a modal response of 50%, indicating that many students either literally perceived that these practices are as commonly applied as not, or selected a respon as near 50% as an indicator of indifference or uncertainty.
-In contrast, other practices with a mean response near 50% (e.g.
-registered reports) were not normally distributed around the scale midpoint.
-Instead, participants demonstrated substantial lack of agreement about the frequency of this practice.
-While the modal values were 60% (n=13) and 80% (n=13), there was also frequent endorsement of 40% (n=12), 20% (n=11) and 70% (n=11).
-As a result, it appears that there is substantial lack of consensus with regard to the practice of open access publication.
+Although this could be read as implying literally that participants believe these practices are roughly as commonly applied as not, it could imply that some participants provided responses near 50% as an indication of uncertainty or indifference.
+This said, 50% was the modal response for only a minority of practices (open access, data availability on request).
 
-<!-- MW: Should that last bit say registered reports?
-There's also quite a bit of manually written numeric info here - we should probably convert that to R code?
--->
-
-Overall these findings suggest that while incoming psychology students may have a degree of sympathy for open science norms, they know relatively little about replicability and open science.
-
-<!-- Since the journal asks for a Teaching Implications subsection in the structured abstract, I'm thinking it'd make sense to have a Teaching Implications subsection in the discussion, about here?
--->
+The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is *usually* conducted openly.
+Nevertheless, the students appear to have at least somewhat over-estimated the prevalence of some open science practices.
+For example, on average students estimated that nearly a third of published psychological studies share data openly and that nearly half of studies are preregistered.
+Although we have not conducted a systematic review it is safe to say the true figures are rather lower [see @wichertsPoorAvailabilityPsychological2006].
 
@@
 However, we did not probe students' factual knowledge of methodological findings or concepts.
-It’s quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) open science considerations without necessarily impacting their attitudes and beliefs.
-Yet, research at the tertiary level casts doubt that the disciplinary reform from the past 2 decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].
+It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) open science considerations without necessarily impacting their attitudes and beliefs.
+Yet, research at the tertiary level casts doubt that the disciplinary reform from the past two decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].
 
@@
 
-## Directions for future research
+<!-- ## Directions for future research
+
+MW: Do we need directions.. or just leave out to conserve word count?-->
+
+## Conclusion and teaching implications
+Overall these findings suggest that incoming psychology students have a degree of sympathy for open science norms.
+Nevertheless, despite significant media attention on the replication crisis, few have heard of this crisis.
+Similarly, students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices).
+It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.
+
+<!-- MW: I've added this subsection because it's signalled as a required heading in the abstract. Is there more to say here?-->
 

### 2021-10-06 analysis/Manuscript.Rmd
Formatting fixes as per email

@@
 ## TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
-
 keywords: open science, psychology, teaching, reproducibility, replication
@@
   institution: Massey University
+- id: '3'
+  institution: Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology
 editor_options: 
   chunk_output_type: console
+csl               : "apa.csl" 
 ---
@@
 Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves.
-Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices - and problems with methodological practices in psychology - is essential for becoming informed and critical consumers of psychological knowledge.
+Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices – and problems with methodological practices in psychology – is essential for becoming informed and critical consumers of psychological knowledge.
 Studies have therefore begun to explore strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
@@
 
-There were 20 scenarios in total (see Table \@ref(tab:norm_counternorm_items)).
+There were 20 scenarios in total (see Table \@ref(tab:normcounternormitems)).
 Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
@@
 MW: The table captions/crossreferences may not be working - see the compiled document.
+
+EK: for cross-referencing to work you can't have underscores in the chunk name
 -->
 
-```{r norm_counternorm_items}
+```{r normcounternormitems}
 norm_items = data.frame(
-  "Practice" = c("critical", "critical", "HARKing", "HARKing", "Info for replicability", "Info for replicability",
+  "Practice" = c("Critical thinking", "Critical thinking", "HARKing", "HARKing", "Info for replicability", "Info for replicability",
                  "Open access", "Open access", "Open data", "Open data", "Open materials", "Open materials",
@@
 
+\
+
 ### Beliefs About the Practice of Psychological Science
@@
 accepting them), and one practice added out of interest (data sharing on request).
-(see Table XX).
+(see Table \@ref(tab:normsinpracticeitems)).
 Participants were given a slider bar ranging from 0% to 100% to record their estimate.
@@
 
-```{r norms_in_practice_items}
+```{r normsinpracticeitems}
 practice_items = data.frame(
@@
 
+\
+
 ### Beliefs About Replications
@@
 Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to,
+
 > "Imagine that a set of researchers selected 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
@@
 95% confidence intervals. For this analysis, we removed three cases with missing values. 
-Table XX displays the means and standard deviations for each norm, counternorm, 
-and the difference values.
+Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values.
 
@@
 
-```{r difference between norm and counternorm}
+```{r differencebetweennormandcounternorm}
 
@@
 
+practice_means_corr$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprint", "Preregistration", "Registered reports")
+
 # breadcrumbs:
@@
 # I need to use apa_tables.... (in line with papaja)
-# update practice descriptions so they make sense to readers
+# EK - You can rotate the table, but I don't think it will rotate the page and it won't
+# carry over into word
 
@@
 <!-- I imagine we will remove the p.value column, but we might want this for now.  -->
+<!-- It's not clear which stat the pvalue relates to, I would support removing it  -->
 
 ## Norms in practice
-Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices.
+Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)).
 For many of these practices, participants’ estimates were near the midpoint of 50%.
@@
 
-```{r norms in practice}
+```{r normsinpractice}
 
@@
 
+in_practice_means$Practice <- c("Data on request", "Info for replicability", "HARKing", "p-hacking", "Open access", "Open data", "Open materials", "Preprint", "Pre-registration", "Registered report")
+
 knitr::kable(in_practice_means,
@@
 The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`.
-A histogram of participants' responses is provided in Figure X.
+A histogram of participants' responses is provided in Figure \@ref(fig:repperchistogram).
 
-```{r rep_perc_histogram}
+```{r repperchistogram, fig.cap="Histogram of participants' responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+We call repeating a study like this a \"replication study\".
+At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider."}
 hist(df$rep_perc, main = NULL, xlab = "Percentage")
 ```
-_Figure X_.
-Histogram of participants' responses to the question: "Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
-We call repeating a study like this a “replication study”.
-At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?" Responses provided on a visual slider.
 
@@
 
-Figure XX displays the histograms for each of the norms in practice items.
+Figure A displays the histograms for each of the norms in practice items.
 
-```{r norms in practice histogram}
+```{r normsinpracticehistogram}
 
-p <- in_prac_long %>%
+practice_labels <- c(
+  available_data = "Data on\nrequest",
+  detailed_methodology = "Info\nrequired\nfor replication",
+  harking = "HARKing",
+  incomplete_results = "p-hacking",
+  open_access = "Open access",
+  registered_reports = "Registered reports",
+  open_data = "Open data",
+  open_materials = "Open\nmaterials",
+  preprint_pre = "Preprints",
+  preregistration = "Preregistration",
+  registered_report = "Registered\nreport"
+)
+
+in_prac_long %>%
   ggplot(aes(x = `prevalence rating`)) +
@@
     theme(axis.text = element_text(size = 9), axis.title = element_text(size = 9)) +
-    facet_wrap(~practice, nrow = 2)
-p
+    facet_wrap(~practice, nrow = 2, labeller = labeller(practice = practice_labels))
 
-#[breadcrumb: need to update the theme & the practice names]
+#[breadcrumb: need to update the theme]
 
 ```
+*Figure A*
 
@@
 We might need to cut it down manually to a more concise list?
+
+EK: You can edit the r-refs bib directly to remove the packages that are just dependencies
 -->

### 2021-10-13 analysis/Manuscript.Rmd
minor revisions to intro

@@
 abstract: |
-## BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
-## OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology. 
-## METHOD: International online survey with participants who were about to start their first course in psychology (N = 239) .
-## RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices.
+BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
+OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in spsychology.
+METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239) .
+RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices.
 When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%.
 Only 18% of participants had heard of the term "replication crisis".
-## CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term.
+CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term.
 Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
-## TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
+TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
+
 keywords: open science, psychology, teaching, reproducibility, replication
@@
 The abstract also doesn't currently knit into the final document for some reason?
+JB: I tried to fix this too and looked at all sorts of troubleshooting guides, but no luck.
 
@@
 
-<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting
+<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting. JB: We'll need to discuss authorship order. I would 
+like to use CREDIT for our contributions. 
 It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
 The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions. 
+JB: Yes, that makes sense.
+
 To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
@@
 This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
-papaja and its many dependencies.
+papaja and its many dependencies. J
+B: Yes, that's a good note to include for folks.
 -->
@@
 # Seed for random number generation
+# JB: We aren't generating random numbers though--any reason to keep it?
 set.seed(42)
@@
 df$major <- as.character(df$major)
-# df$uni_country <- as.character(df$uni_country)
-# df$nationality <- as.character(df$nationality) [i think these should be factors]
+df$uni_country <- as.character(df$uni_country)
+df$nationality <- as.character(df$nationality)
 
-# import the metadata 
+# import the metadata [if using]
 #metadata <- here::here("survey", "data", "students_metadata.csv") %>% 
@@
 
-#MW: I have commented this chunk out out temporarily because it might need tweaking - it assumes a subfolder in "survey" called "data"
-#and the last select line doesn't seem to run (no column with that name recognised)
 ```
@@
 These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
-These apparent problems with replication have lead to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
+These apparent problems with replication have lead to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012; @wigboldus_encourage_2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
 These calls for more reproducible and transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
 Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018].
+
+<!-- If we need to cut more words, we could cut the last sentence and combine the references into the previous sentence and add a phrase like "....prompted the discipline to reflect on and measure researchers norms, attitudes, and practices..." -->
 
@@
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe2019; @vazireWhereAreSelfcorrecting2020].
-For example, the practices of sharing of preprints for open peer review and open data for checking of reproducibility corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
+For example, the practices of sharing of preprints for open peer review and open data for reproducibility checks corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
 Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
@@
 First, unlike some psychological phenomena in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018].
-Students may plausibly have some knowledge about these issues obtained prior to (or independently of) their formal studies.
-Teaching methods should thus be informed by some understanding of what students' pre-existing levels of knowledge are.
+Students may have plausibly obtained some knowledge about these issues prior to (or independently of) their formal studies.
+Teaching methods should thus be informed by some understanding of students' pre-existing levels of knowledge.
 
 Second, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice.
-This could imply a need for educators to reinforce and build on students “naive” impressions rather than radically altering their understanding of how science should be done.
-On the other hand, other evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility.
+This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done.
+On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility.
 For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values.
-The extent to which incoming psychology students may - or may not - be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
+The extent to which incoming psychology students may – or may not – be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
 
-We therefore aimed to conduct a study describing what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
-Our survey encompassed questions norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is).
+We conducted a descriptive study examining the beliefs of incoming undergraduate students in a first-year psychology unit about reproducibility and open science practices in psychology.
+Our survey encompassed questions about norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is).
 Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.

### 2021-10-17 analysis/Manuscript.Rmd
JB edits to intro and materials

@@
 # import the metadata [if using]
-#metadata <- here::here("survey", "data", "students_metadata.csv") %>% 
- #read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>% 
- #filter(!is.na(old_variable)) %>% 
- #dplyr::select (-c("...10", "note:"))
+# metadata <- here::here("survey", "data", "students_metadata.csv") %>%
+# read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>%
+# filter(!is.na(old_variable))
 
@@
 On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility.
-For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values.
+For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted, with regard to their own analyses, “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values.
 The extent to which incoming psychology students may – or may not – be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
@@
 Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.
-We nevertheless preregistered our aims, sampling plan, exclusion criteria and data analysis plan at https://osf.io/6e2ux/?view_only=b5173ba3bf564bc495686cd0845e678b
+We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp.
 
 <!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology?
+JB: That'd be great in the
+abstract and discussion?
 -->
@@
 # Methods
-We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->
+We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
+<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) --> Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6.
 
-<!--MW: We need to include a link for accessing raw data and measures etc. -->
+<!-- JB: Is there are a reason we aren't including Simmons et al as a cite? -->
 
@@
 
-Collaborators from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics.
-An invitation was sent to participants via email or a course website 1-2 weeks before their course began.
+Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics.
+An invitation was sent to participants via email or a course website 1–2 weeks before their course began.
 The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month, and included a link to the survey.
@@
 
+<!-- JB: I've renamed collaborators to contacts because they aren't on this paper and aren't necessarily people that we've previously collaborated with. -->
+
 <!--MW: I've moved Procedure up above Participants - I think that works better for flow since otherwise we have to describe screening within the survey before we've introduced the survey itself.
-Hope this is ok.-->
+Hope this is ok.
+JB: Fine with me.
+If it's an issue, we can describe the final sample of participants first and then describe the inclusion criteria later.-->
 
@@
 participants who were not eligible to participate based on the combination of our
-preregistered exclusion criteria. Specifically, we screened out people who were younger than 
-18 years (*n* = `r age_ex`). We also screened out individuals who had already 
+preregistered exclusion criteria. Specifically, we screened out people who were younger than 18 years (*n* = `r age_ex`). We also screened out individuals who had already 
 started a psychology unit at a university, regardless of whether they had 
@@
 The remaining `r n` participants were eligible based on starting their first unit 
-of study in psychology at a university within the next month. For those individuals 
-who were screened out, Qualtrics automatically directed them to a 
-debriefing
-
-Most participants reported that they were
-18-24 years old (*n* = `r age[1,2]`), `r age [2,2]` 
-reported that they were 25-34 years old, `r age [3,2]` were 35-44 years old,
-`r age [4,2]` were 45-54 years old, and `r age [5,2]` was 55-64 years old. The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
+of study in psychology at a university within the next month. Of the eligible 
+participants, most reported that they were 18–24 years old (*n* = `r age[1,2]`);
+`r age [2,2]` reported that they were 25–34 years old, `r age [3,2]` were 35–44 
+years old, `r age [4,2]` were 45–54 years old, and `r age [5,2]` was 55–64 years old. 
+The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
 `r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
@@
 Most participants reported attending university in Australia (*n* = `r uni_country[1,2]`), 
-the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = `r uni_country[4,2]`). Nearly all reported graduating from high
-school or secondary school (*n* = `r hs_status[3,2]`). Of those participants who 
-attended high school, fewer than half completed psychology courses in 
-high school (*n* = `r hs_psyc[2,2]`). Most reported their nationality as being from Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = `r nationality[24,2]`), or China
-(*n* = `r nationality[6,2]`). About 2/3rds of participants reported that at least one of their parents attended university (*n* = `r first_gen[2,2]`).
-
-<!--
-MP: Seems like we are missing some nationalities here – US nationalities? NZ? Or is this just the top 3?
--->
+the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = 
+`r uni_country[4,2]`). Nearly all reported graduating from high school or secondary 
+school (*n* = `r hs_status[3,2]`). Of those participants who attended high school, 
+fewer than half completed psychology courses in high school (*n* = `r hs_psyc[2,2]`).
+Participants reported `r nrow(nationality)` different nationalities; the most 
+common were Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = 
+`r nationality[24,2]`), and China (*n* = `r nationality[6,2]`). About two-thirds of 
+participants reported that at least one of their parents attended university 
+(*n* = `r first_gen[2,2]`).
 
@@
 <!-- Mention here our discussions workshopping of common open science norms at SIPs?
--->
+JB: I think we have to, don't we?-->
 The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
@@
 
-There were 20 scenarios in total (see Table \@ref(tab:normcounternormitems)).
-Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
-
-<!-- Add Table X of norms and counternorms statements that map to each practice 
-MW: The table captions/crossreferences may not be working - see the compiled document.
-
-EK: for cross-referencing to work you can't have underscores in the chunk name
--->
+We presented 20 scenarios (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
 
@@
 
-# recode the data so the response options have proper labels
+# c <- metadata %>%
+#     filter(scale == "norms")
 
-# c <- metadata %>% 
-#     filter(Scale == "OSmost") %>% 
-#     filter(NewVariable != "OSmost_text") #remove this value from metadata
-# 
+# add a practice column in metadata
+
+# update this text  
 # d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>%
@@
 We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world.
-To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm-counternorm pairs described above, albeit with one norm excluded on the basis of not referring to externally observable behaviour (critically evaluating published studies vs.
-accepting them), and one practice added out of interest (data sharing on request).
-(see Table \@ref(tab:normsinpracticeitems)).
-Participants were given a slider bar ranging from 0% to 100% to record their estimate.
-
-<!-- Add Table XX of 10 belief statements -->
+To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm–counternorm pairs described above, with two exceptions (see Table \@ref(tab:normsinpracticeitems)).
+We excluded one norm because it did not refer to externally observable behaviour (critically evaluating published studies vs.
+accepting them), and we included one practice out of interest (data sharing on request).
+Participants indicated their estimate on a slider bar ranging from 0% to 100%.
 
@@
   "Practice" = c("Preregistration", "Registered reports", "p-hacking", "HARKing", "Info for replicability",
-                 "Preprint", "open materials", "Open data", "Data on request", "Open access"),
+                 "Preprint", "Open materials", "Open data", "Data on request", "Open access"),
   "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
@@
 
-#Note to selves: The norm in practice items map fairly closely to norms and counternorms, but not exactly
-#I.e., there is no norm in practice item about critically evaluating published literature, but there is one about sharing
-#data on request (which isn't in the norms/counternorms)
-#I can't remember why we did this, but so it goes.
 #The ordering of this table also doesn't match the one above, which I'm leaving for the moment since we probably want to set

### 2021-10-18 analysis/Manuscript.Rmd
JB edits to results part 1

@@
 In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm.
-However, the extent to which participants endorsed open science norms varied very substantially across different practices.
+However, the extent to which participants endorsed open science norms varied substantially across different practices.
 Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing 'agree').
-They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items were all between 3.5 and 4.
+They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items varied between 3.5 and 4.
 On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.
@@
 <!--MW: The paragraphs above contain some numeric info that's written in manually rather than being R outputs (e.g., "three", "seven") 
-Not sure if that's a worry.
+Not sure if that's a worry. JB: It sort of has to be because a) it's a holistic summary
+and b) APA requires numbers below 10 to written out.
 -->
+
+<!-- JB: More of a concern for me is that we don't say anything about the 
+correlations. If we aren't going to say anything about them at all, we can 
+include them as a supplemental material? We preregistered them, so we have to 
+include them, but we don't really have to say anything about them.-->
 
@@
 practice_means_corr <- practice_means_corr %>% 
+  relocate (practice, .before = Norm) %>% 
+  relocate (p.value, .after = last_col())
+
+practice_means_corr <- practice_means_corr %>% 
   rename(Practice = practice) %>% 
-  dplyr::select(-c(estimate, conf.low, conf.high)) %>% 
-  relocate (Practice, .before = Norm) %>% 
-  relocate (p.value, .after = last_col())
+  rename("Correlation p-value" = p.value) %>% 
+  dplyr::select(-c(estimate, conf.low, conf.high))
 
@@
 
-# breadcrumbs:
 # need to figure out whether I can rotate a page in papaja
-# I need to use apa_tables.... (in line with papaja)
 # EK - You can rotate the table, but I don't think it will rotate the page and it won't
-# carry over into word
+# carry over into word. 
+# JB: Moving correlations to a supplement will sove the problem I'm trying to resolve anyway...
 
@@
 <!-- It's not clear which stat the pvalue relates to, I would support removing it  -->
+<!-- JB: I've changed the heading of the p.value column for clarity. If we pull the corrs out
+into a new table in the supplemental material, then we will want the p-value with it. -->
 

### 2021-10-29 analysis/Manuscript.Rmd
update code for abstract
update comments re abstract
minor change to wording in norms in practice

@@
 Abstract currently includes hand-typed numbers because it's hard to get them to knit up here since data processing is further below.
-The abstract also doesn't currently knit into the final document for some reason?
-JB: I tried to fix this too and looked at all sorts of troubleshooting guides, but no luck.
-
 -->
@@
 This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
-papaja and its many dependencies. J
-B: Yes, that's a good note to include for folks.
+papaja and its many dependencies. 
+JB: Yes, that's a good note to include for folks.
 -->
@@
 # carry over into word. 
-# JB: Moving correlations to a supplement will sove the problem I'm trying to resolve anyway...
+# JB: Moving correlations to a supplement will solve the problem I'm trying to resolve anyway...
 
@@
 This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
+See Figure A in Supplemental Materials to see the distribution for each item.
 Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.

### 2021-10-29 analysis/Manuscript.Rmd
JB edits to results and discussion

@@
 Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term.
-Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
+Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
 Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
@@
 Participants' estimates of the replicability of psychological studies were variable.
-The mean, _M_ =`r mean(df$rep_perc, na.rm = TRUE)` was near the midpoint of 50%, but with substantial variability around this estimate, _SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, minimum = `r min(df$rep_perc, na.rm = TRUE)`,  maximum = `r max(df$rep_perc, na.rm = TRUE)`.
+The mean (_M_ = `r mean(df$rep_perc, na.rm = TRUE)`) was near the midpoint of 50%, but with substantial variability around this estimate (_SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, range = `r min(df$rep_perc, na.rm = TRUE)` to `r max(df$rep_perc, na.rm = TRUE)`).
 A histogram of participants' responses is provided in Figure \@ref(fig:repperchistogram).
@@
 ```{r repperchistogram, fig.cap="Histogram of participants' responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
-We call repeating a study like this a \"replication study\".
-At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider."}
-hist(df$rep_perc, main = NULL, xlab = "Percentage")
+We call repeating a study like this a \'replication study\'.
+At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%."}
+hist(df$rep_perc, main = NULL, ylim = range(0,40), xlab = "Percentage")
 ```
@@
 
-Despite efforts to improve the replicability of research the past decade, and corresponding media attention, most incoming psychology students in our sample were unaware of the replication crisis.
+Despite efforts to improve the replicability of research over the past decade, and corresponding media attention, most incoming psychology students in our sample were unaware of the replication crisis.
 Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms.
@@
 
+<!-- do the histograms change our interpretation here? -->
+
 The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is *usually* conducted openly.
@@
 
+<!-- ADD IN HARDWICKE & update sentence
+
+https://journals.sagepub.com/doi/full/10.1177/1745691620979806-->
+
 ## Strengths and limitations
 Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings.
-Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only very tentative generalisations to a wider population of incoming psychology students.
-However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open-data to research practice.
+Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students.
+However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open data to research practice.
 
 Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process.
-However, we did not probe students' factual knowledge of methodological findings or concepts.
-It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) open science considerations without necessarily impacting their attitudes and beliefs.
+However, we did not probe students' factual knowledge of most methodological findings or concepts, except the replication crisis.
+It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) considerations without necessarily impacting their open science attitudes and beliefs.
 Yet, research at the tertiary level casts doubt that the disciplinary reform from the past two decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].

### 2021-10-29 analysis/Manuscript.Rmd
update minor changes

@@
 keywords: open science, psychology, teaching, reproducibility, replication
-wordcount: X
+wordcount:
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
@@
 library(tidyselect) 
-library(psychometric) # for correlation confidence intervals - might not need...
+#library(psychometric) # for correlation confidence intervals - might not need...
 library(broom)
@@
 On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.
-
-<!--MW: The paragraphs above contain some numeric info that's written in manually rather than being R outputs (e.g., "three", "seven") 
-Not sure if that's a worry. JB: It sort of has to be because a) it's a holistic summary
-and b) APA requires numbers below 10 to written out.
--->
-
-<!-- JB: More of a concern for me is that we don't say anything about the 
-correlations. If we aren't going to say anything about them at all, we can 
-include them as a supplemental material? We preregistered them, so we have to 
-include them, but we don't really have to say anything about them.-->
 

### 2021-10-29 analysis/Manuscript.Rmd
add credit & update r refs

@@
   - name: Jennifer L. Beaudry
-  affiliation: '1'
+    affiliation: '1,4'
+    role:
+      - Conceptualization
+      - Data curation
+      - Formal analysis
+      - Investigation
+      - Methodology
+      - Project administration
+      - Validation
+      - Visualization
+      - Writing - original draft
+      - Writing - review & editing
     corresponding: yes
-  address: Postal address
-  email: jbeaudry@swin.edu.au
-  role: null
+    email: jen.beaudry@flinders.edu.au
+    address: Enter postal address here
+  - name: Matt N. Williams
+    affiliation: '2'
+    role:
+      - Investigation
+      - Methodology
+      - Validation
+      - Writing - original draft
+    email: m.n.williams@massey.ac.nz
   - name: Michael C. Philipp
     affiliation: '2'
-  role: null
-- name: Matt N. Williams
-  affiliation: '2'
-  role: null
-- name: Emily Kothe
+    role:
+      - Conceptualization
+      - Investigation
+      - Methodology
+      - Project administration
+      - Writing - original draft
+    email: m.philipp@massey.ac.nz
+  - name: Emily J. Kothe
     affiliation: '3'
-  role: null
+    role:
+      - Conceptualization
+      - Data curation
+      - Validation
+      - Visualization
+      - Writing - review & editing
+    email: emily.kothe@deakin.edu.au
+
+affiliation:
+  - id: '1'
+    institution: Flinders University
+  - id: '2'
+    institution: Massey University, New Zealand
+  - id: '3'
+    institution: Deakin University
+  - id: '4'
+    institution: Swinburne University of Technology
+
 shorttitle: Psychology students' beliefs about open science
@@
   papaja::apa6_pdf: default
-authornote: |
-  1 Flinders University, Australia
-  2 Massey University, New Zealand
-  3 Deakin University, Australia
 abstract: |
@@
 keywords: open science, psychology, teaching, reproducibility, replication
-wordcount:
+wordcount:  3161 (need to update)
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
@@
 linenumbers: yes
-mask: yes
+mask: no
 draft: no
@@
 classoption: man
-affiliation:
-- id: '1'
-  institution: Swinburne University of Technology
-- id: '2'
-  institution: Massey University
-- id: '3'
-  institution: Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology
 editor_options: 
   chunk_output_type: console
-csl               : "apa.csl" 
+csl: "apa.csl" 
 ---
@@
 
-<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting. JB: We'll need to discuss authorship order. I would 
-like to use CREDIT for our contributions. 
-It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
-The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions. 
-JB: Yes, that makes sense.
-
-To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
+<!-- To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
 However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
-This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
-papaja and its many dependencies. 
-JB: Yes, that's a good note to include for folks.
+This could be useful in future for readers interested in reproducing results but who don't have or wish to install papaja and its many dependencies.
 -->
-
-<!-- The .bib file is now just from our shared library -->
 
@@
 library(finalfit) # to keep trailing zeros & round_tidy
-library(psych) #for correlation matrices
 library(tidyselect) 
-#library(psychometric) # for correlation confidence intervals - might not need...
 library(broom)
@@
 
-#The ordering of this table also doesn't match the one above, which I'm leaving for the moment since we probably want to set
-#an order of items/norms and stick to it consistently throughout
-
 ```
@@
 
-<!-- do the histograms change our interpretation here? -->
-
 The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is *usually* conducted openly.
@@
 
-<!-- ## Directions for future research
-
-MW: Do we need directions.. or just leave out to conserve word count?-->
-
 ## Conclusion and teaching implications
@@
 It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.
-
-<!-- MW: I've added this subsection because it's signalled as a required heading in the abstract. Is there more to say here?-->
 
@@
   available_data = "Data on\nrequest",
-  detailed_methodology = "Info\nrequired\nfor replication",
+  detailed_methodology = "Information\nfor replication",
   harking = "HARKing",
@@
 
-#[breadcrumb: need to update the theme]
-
 ```
@@
 
-We used `r cite_r("r-references.bib")` for all our analyses.
-
-<!-- This is nice to do, but it generate a 150+ word paragraph of citations to packages, including citations to packages our code doesn't directly use (e.g.
-nlme, multilevel, etc.).
-We might need to cut it down manually to a more concise list?
-
-EK: You can edit the r-refs bib directly to remove the packages that are just dependencies
--->
+We used `r cite_r(file = "r-references.bib", pkgs = c("broom", "finalfit", "gendercoder", "here", "papaja", "tidyverse"), withhold = FALSE)` for our analyses.
 

### 2021-11-12 analysis/Manuscript.Rmd
minor changes to text

@@
  OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in spsychology.
- METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239) .
+ METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
  RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices.
@@
 keywords: open science, psychology, teaching, reproducibility, replication
-wordcount:  3161 (need to update)
+wordcount: (need to update)
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
@@
 ```{r setup, include = FALSE}
-library(papaja) #install with devtools1
+library(papaja) #install with devtools
 library(here)
@@
 ```{r analysis-preferences}
-# Seed for random number generation
-# JB: We aren't generating random numbers though--any reason to keep it?
-set.seed(42)
+
 knitr::opts_chunk$set(
@@
 }
+
+meta_rename <-  function(df, metadata, old, new) {
+
+  keys   <- metadata[[deparse(substitute(old))]]
+  values <- metadata[[deparse(substitute(new))]]
+
+  matchlist <- setNames(values, keys)
+  names(df) <- matchlist[names(df)]
+  return(df)
+
+}
 ```
@@
 crisis_descriptions = read.csv(here::here ("data", "crisis_descriptions_marked.csv"))
+
+# import the metadata
+metadata <- here::here("data", "students_metadata.csv") %>%
+read_csv(col_names = TRUE, skip_empty_rows = TRUE, lazy = FALSE) %>%
+filter(!is.na(old_variable))
+
+# relabel the variable names
+df <- meta_rename(df, metadata = metadata, old = old_variable, new = new_variable)
 
@@
 df$nationality <- as.character(df$nationality)
-
-# import the metadata [if using]
-# metadata <- here::here("survey", "data", "students_metadata.csv") %>%
-# read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>%
-# filter(!is.na(old_variable))
 

### 2021-11-12 preprocessing/preprocessing_students.R
update the gendercoder script, doesn't work

@@ -41,6 +41,7 @@ miss_fun = function(x){
   sum(is.na(x))
 }
 
+
 ##### LOAD DATA #####
 
 # raw data without labels
@@ -77,8 +78,9 @@ df_lab <- df_lab %>%
   rename_all(paste0, "_lab") %>% # add "_num" to differentiate the columns with numbers vs. labels
   rename(id = id_lab) # except for the id column because we need that for the join!
 
-# join the two tibbles
+# join the two tibbles and delete columns that we don't need
 df <- df_num %>% inner_join(df_lab, by = "id")
+
 
 
 ##### RECODE VARIABLE NAMES #####
@@ -86,8 +88,6 @@ df <- df_num %>% inner_join(df_lab, by = "id")
 # recode variable labels according to metadata
 
 df <- meta_rename(df, metadata, old = old_variable, new = new_variable)
-
-# Breadcrumbs finish working on the metadata!
 
 
 #### CONVERT VARIABLES INTO FACTORS ####
@@ -102,8 +102,6 @@ df <- df %>%
 
 ######### RECODE GENDER ##########
 
-######### RECODE GENDER ##########
-
 custom_dictionary <- list(
   `female.` = "female",
   `femamle` = "female",
@@ -112,8 +110,13 @@ custom_dictionary <- list(
   `queer man` = "queer man"
 )
 
-df <- df %>%
-  mutate(gender  = recode_gender(gender, dictionary = c(broad, custom_dictionary), fill = TRUE))
+# original recode gender
+# df <- df %>%
+  # mutate(gender  = recode_gender(gender, dictionary = c(broad, custom_dictionary), fill = TRUE))
+
+# new recode gender (which still doesn't work)
+# df <- df %>%
+#   mutate(gender  = recode_gender(gender, dictionary = c(manylevels_en, custom_dictionary)))
 
 ########## EXCLUSION CRITERIA ############
 

### 2021-11-12 analysis/Manuscript.Rmd
minor changes to meta data code
revise intro according to MP edits

@@
  BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
- OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in spsychology.
+ OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
  METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
@@
 
-# relabel the variable names
-df <- meta_rename(df, metadata = metadata, old = old_variable, new = new_variable)
+# relabel the variable names [completed in preprocessing]
+# df <- meta_rename(df, metadata = metadata, old = old_variable, new = new_variable)
 
@@
 These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
-These apparent problems with replication have lead to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012; @wigboldus_encourage_2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
+These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012; @wigboldus_encourage_2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
 These calls for more reproducible and transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
@@
 Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe2019; @vazireWhereAreSelfcorrecting2020].
-For example, the practices of sharing of preprints for open peer review and open data for reproducibility checks corresponds to the norm of communality, and also to that of *organised skepticism*: Scientific claims should be subjected to critical scrutiny.
-Preregistration can be connected to the norm of *disinterestedness*: By making (and preregistering) decisions about how to analyse data before results are produced, a researcher can limit the degree to which the substantive results produced by different analytic strategies affect their decisions regarding which analyses to report.
+For example, the practices of sharing preprints for open peer review and posting open data for reproducibility checks corresponds to the norms of *communality* and *organised skepticism*: Scientific claims should be openly subjected to critical scrutiny.
+Preregistration can be connected to the norm of *disinterestedness*: By making preregistered decisions about how to analyse data before results are produced, a researcher limits the degree to which substantive results produced by different analytic strategies affect their decisions regarding about analyses to report.
 
@@
 Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves.
-Even for students who do not go on to conduct research themselves, an understanding of contemporary methodological practices – and problems with methodological practices in psychology – is essential for becoming informed and critical consumers of psychological knowledge.
-Studies have therefore begun to explore strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
+Even for students who do not go on to conduct research, an understanding of contemporary methodological practices---and problems with methodological practices in psychology---is essential for becoming informed and critical consumers of psychological knowledge.
+Studies have explored strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
 These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
@@
 Students may have plausibly obtained some knowledge about these issues prior to (or independently of) their formal studies.
-Teaching methods should thus be informed by some understanding of students' pre-existing levels of knowledge.
+Teaching methods should be informed by some understanding of students' pre-existing levels of knowledge.
 
-Second, anecdotal evidence suggests that some students being taught about open science practices and reforms to improve reproducibility (such as open sharing of data and analysis code) are often surprised that these are not *already* standard practice.
+Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (such as open sharing of data and analysis code) are sometimes surprised that these are not *already* standard practice.
 This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done.
 On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility.
-For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted, with regard to their own analyses, “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (i.e., p-hacking), while 9.6% reported rounding down p-values.
-The extent to which incoming psychology students may – or may not – be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
+For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted to “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (p.
+14; i.e., *p*-hacking), while 9.6% reported rounding down *p*-values.
+The extent to which incoming psychology students may---or may not---be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
 
-We conducted a descriptive study examining the beliefs of incoming undergraduate students in a first-year psychology unit about reproducibility and open science practices in psychology.
-Our survey encompassed questions about norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted) and replicability (how replicable students believe psychological research is).
-Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and does not involve the specification or testing of hypotheses.
+We conducted a descriptive study, asking incoming undergraduate psychology students about their beliefs regarding reproducibility and open science practices in psychology.
+Our survey encompassed questions concerning norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted), and replicability (how replicable students believe psychological research is).
+Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and did not involve the specification or testing of hypotheses.
 We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp.
@@
 # Methods
-We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
-<!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) --> Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6.
-
-<!-- JB: Is there are a reason we aren't including Simmons et al as a cite? -->
+Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6 [blinded].
 
@@
 
-# gender --> need to summarise once we've recoded it in preprocessing script
+# gender 
 gender <- df %>% dplyr::count(gender)
@@
 An invitation was sent to participants via email or a course website 1–2 weeks before their course began.
-The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month, and included a link to the survey.
+The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month and included a link to the survey.
 
-Ethical approval for this study was granted by (institution blinded).
-
-<!-- JB: I've renamed collaborators to contacts because they aren't on this paper and aren't necessarily people that we've previously collaborated with. -->
-
-<!--MW: I've moved Procedure up above Participants - I think that works better for flow since otherwise we have to describe screening within the survey before we've introduced the survey itself.
-Hope this is ok.
-JB: Fine with me.
-If it's an issue, we can describe the final sample of participants first and then describe the inclusion criteria later.-->
+Ethical approval for this study was granted by [institution blinded].
 
@@
 years old, `r age [4,2]` were 45–54 years old, and `r age [5,2]` was 55–64 years old. 
-The majority of participants (*n* = `r gender[1,2]`) reported that they were female, 
+Most participants (*n* = `r gender[1,2]`) reported that they were female, 
 `r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 

### 2021-11-12 preprocessing/preprocessing_students.R
minor changes

@@ -115,8 +115,8 @@ custom_dictionary <- list(
   # mutate(gender  = recode_gender(gender, dictionary = c(broad, custom_dictionary), fill = TRUE))
 
 # new recode gender (which still doesn't work)
-# df <- df %>%
-#   mutate(gender  = recode_gender(gender, dictionary = c(manylevels_en, custom_dictionary)))
+df <- df %>%
+   mutate(gender  = recode_gender(gender, dictionary = c(manylevels_en, custom_dictionary), fill = TRUE))
 
 ########## EXCLUSION CRITERIA ############
 

### 2021-11-12 analysis/Manuscript.Rmd
pull out corrs from Table 3 to supplemental table

@@
 their gender identity as "queer man", and `r gender[3,2]` participant reported 
-non-binary gender.
+non-binary gender. *We still need to fix this...see email from Nov 12th*
 
@@
 
-Our approach to measuring norms and counternorms focussed on participants' evaluation of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
+Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
 Anderson et al., 2007).
@@
 JB: I think we have to, don't we?-->
-The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficent information of replicability, preprints, open materials, open data, and open access publishing.
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the existence of important debate about the merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
+The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing.
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
 
@@
 
-We also sought to measure participants' normative beliefs about how psychological science is actually conducted by researchers around the world.
+We also sought to measure participants' normative beliefs about how researchers actually conduct psychological science.
 To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm–counternorm pairs described above, with two exceptions (see Table \@ref(tab:normsinpracticeitems)).
@@
 practice_means <- prac_means %>% 
-  dplyr::select(practice, Norm, Counternorm, Difference)
+  rename(Practice = practice) %>% 
+  dplyr::select(Practice, Norm, Counternorm, Difference)
 
-# ADD CORRELATIONS (per participant, use df)
+practice_means$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered Reports")
 
-# notes for the correlations....
-# just the correlation with CI
-# critical_corr <- round(cor(df$critical_norm, df$critical_cnorm),2)
-# critical_CI <- round(CIr(r = critical_corr, n = nrow(df), level = 0.95),2)
-
-#correlation test with CI and p-values in a clean tibble
-# critical_corr_test <- cor.test(df$critical_norm, df$critical_cnorm)
-# tidy(critical_corr_test)
-
-# use this tutorial to try to get the correlations for each practice (using the long data)
-# https://cran.r-project.org/web/packages/broom/vignettes/broom_and_dplyr.html
-
-# this will create a tibble for each practice
-
-# calculates the correlation test for each tibble & then tidies it up
-corr <- norm_cnorm_long %>% 
-  nest(data = -practice) %>% # create a tibble for each practice
-  mutate (test = map(data, ~ cor.test(.x$`norm rating`, .x$`cnorm rating`)), 
-          tidied = map(test,tidy)) %>% # run the corr & tidy it
-  unnest(tidied) # unnest it to look at the results
-
-# remove unnecessary columns, round the values, and move columns
-corr <- corr %>% 
-  dplyr::select(-c(data, test, statistic, parameter, method, alternative))  %>%
-  mutate(p.value = p_tidy(p.value, 3, prefix = "")) %>% 
-  mutate(estimate = round_tidy(estimate,2), 
-         conf.low = round_tidy(conf.low, 2), 
-         conf.high = round_tidy(conf.high, 2)) %>% 
-  dplyr::relocate(estimate, .before = conf.low) %>%  
-    dplyr::relocate(p.value, .after = last_col())
-
-# join the corr tibble with the means tibble 
-practice_means_corr <- practice_means %>% inner_join(corr, by = "practice")
-
-# combine the confidence intervals into one column
-practice_means_corr$Correlation <- paste0(practice_means_corr$estimate, 
-                            " [",
-                            practice_means_corr$conf.low,
-                            ", ", 
-                            practice_means_corr$conf.high,
-                            "]")
-
-# clean up the tibble                          
-practice_means_corr <- practice_means_corr %>% 
-  relocate (practice, .before = Norm) %>% 
-  relocate (p.value, .after = last_col())
-
-practice_means_corr <- practice_means_corr %>% 
-  rename(Practice = practice) %>% 
-  rename("Correlation p-value" = p.value) %>% 
-  dplyr::select(-c(estimate, conf.low, conf.high))
-
-practice_means_corr$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprint", "Preregistration", "Registered reports")
-
-# need to figure out whether I can rotate a page in papaja
-# EK - You can rotate the table, but I don't think it will rotate the page and it won't
-# carry over into word. 
-# JB: Moving correlations to a supplement will solve the problem I'm trying to resolve anyway...
-
-knitr::kable(practice_means_corr,
-             caption = "Means (sd) for norms, counternorms, the difference between norms and counternorms, and correlations between norms and counternorms",
+knitr::kable(practice_means,
+             caption = "Means, standard deviations, and 95% confidence intervals (in square brackets) for norms, counternorms, and the difference between norms and counternorms",
              digits = 2,
@@
 ```
-
-<!-- I imagine we will remove the p.value column, but we might want this for now.  -->
-<!-- It's not clear which stat the pvalue relates to, I would support removing it  -->
-<!-- JB: I've changed the heading of the p.value column for clarity. If we pull the corrs out
-into a new table in the supplemental material, then we will want the p-value with it. -->
 
@@
 
-in_practice_means$Practice <- c("Data on request", "Info for replicability", "HARKing", "p-hacking", "Open access", "Open data", "Open materials", "Preprint", "Pre-registration", "Registered report")
+in_practice_means$Practice <- c("Data on request", "Info for replicability", "HARKing", "p-hacking", "Open access", "Open data", "Open materials", "Preprints", "Pre-registration", "Registered report")
 
@@
 
+Table A contains the correlations between norms and counternorms, with the 95% confidence intervals and the associated *p*-value.
+
+```{r corrbetweennormandcounternorm}
+
+# ADD CORRELATIONS (per participant, use df)
+
+# use this tutorial to get the correlations for each practice (using the long data)
+# https://cran.r-project.org/web/packages/broom/vignettes/broom_and_dplyr.html
+
+# this will create a tibble for each practice
+
+# calculates the correlation test for each tibble & then tidies it up
+corr <- norm_cnorm_long %>% 
+  nest(data = -practice) %>% # create a tibble for each practice
+  mutate (test = map(data, ~ cor.test(.x$`norm rating`, .x$`cnorm rating`)), 
+          tidied = map(test,tidy)) %>% # run the corr & tidy it
+  unnest(tidied) # unnest it to look at the results
+
+# remove unnecessary columns, round the values, and move columns
+corr <- corr %>% 
+  dplyr::select(-c(data, test, statistic, parameter, method, alternative))  %>%
+  mutate(p.value = p_tidy(p.value, 3, prefix = "")) %>% 
+  mutate(estimate = round_tidy(estimate,2), 
+         conf.low = round_tidy(conf.low, 2), 
+         conf.high = round_tidy(conf.high, 2)) %>% 
+  dplyr::relocate(estimate, .before = conf.low) %>%  
+    dplyr::relocate(p.value, .after = last_col())
+
+# combine the confidence intervals into one column
+corr$Correlation <- paste0(corr$estimate, 
+                            " [",
+                            corr$conf.low,
+                            ", ", 
+                            corr$conf.high,
+                            "]")
+
+# clean up the tibble                          
+corr <- corr %>% 
+  relocate (p.value, .after = last_col()) %>% 
+  rename(Practice = practice) %>% 
+  dplyr::select(-c(estimate, conf.low, conf.high))
+
+# reorder the tibble to match the order in Table 3
+
+corr <- corr %>% 
+  arrange(match(Practice, c("critical", "hark", "info_for_rep", "open_access", "open_data", "open_materials", "phack", "preprint", "prereg", "reg_report")), desc(Practice))
+
+corr$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered reports")
+
+knitr::kable(corr,
+             caption = "Correlations between norms and counternorms with the 95% confidence intervals (in square brackets) and the associated p-value",
+             digits = 2,
+             align = c('lccc'))
+
+```
+
+\newpage
+
 Figure A displays the histograms for each of the norms in practice items.

### 2021-11-12 analysis/Manuscript.Rmd
change order table 2, revise results and discussion according to MP edits

@@
 Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and did not involve the specification or testing of hypotheses.
-We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp.
+We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded].
 
@@
 norm_items = data.frame(
-  "Practice" = c("Critical thinking", "Critical thinking", "HARKing", "HARKing", "Info for replicability", "Info for replicability",
+  "Practice" = c("Critical thinking", "Critical thinking", "HARKing", "HARKing", "Information for replicability", "Information for replicability",
                  "Open access", "Open access", "Open data", "Open data", "Open materials", "Open materials",
@@
 practice_items = data.frame(
-  "Practice" = c("Preregistration", "Registered reports", "p-hacking", "HARKing", "Info for replicability",
-                 "Preprint", "Open materials", "Open data", "Data on request", "Open access"),
+  "Practice" = c("Preregistration", "Registered Reports", "p-hacking", "HARKing", "Information for replicability",
+                 "Preprints", "Open materials", "Open data", "Data on request", "Open access"),
   "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
@@
 Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values.
+See Table \@ref(tab:corrbetweennormandcounternorm) in the Supplemental Materials for the correlations between norm and counternorm items.
 
@@
 
-practice_means$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered Reports")
+practice_means$Practice <- c("Critical thinking", "HARKing", "Information for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered Reports")
 
 knitr::kable(practice_means,
-             caption = "Means, standard deviations, and 95% confidence intervals (in square brackets) for norms, counternorms, and the difference between norms and counternorms",
+             caption = "Means and standard deviations for norms, counternorms, and the difference between norms and counternorms, with 95% confidence intervals (in square brackets)",
              digits = 2,
@@
 
-# breadcrumbs:
-# I need to use apa_tables.... (in line with papaja)
-# update practice descriptions so they make sense to readers
+# reorder the tibble to match the order in Table 2
 
-in_practice_means$Practice <- c("Data on request", "Info for replicability", "HARKing", "p-hacking", "Open access", "Open data", "Open materials", "Preprints", "Pre-registration", "Registered report")
+in_practice_means <- in_practice_means %>% 
+  arrange(match(Practice, c("preregistration", "registered_report", "phack", "harking", "info_for_rep", "preprint", "open_materials", "open_data", "available_data", "open_access")), desc(Practice))
+
+in_practice_means$Practice <- c("Preregistration", "Registered Report", "p-hacking", "HARKing", "Information for replicability", "Preprints", "Open materials", "Open data", "Data on request", "Open access")
 
@@
 ## The replication crisis
-Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis", with `r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`% indicating that they had not heard of the crisis and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% missing.
+Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis".
+Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis, and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.
 
-Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"?
+Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
 Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term.
@@
 At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%."}
+
 hist(df$rep_perc, main = NULL, ylim = range(0,40), xlab = "Percentage")
@@
 
-Participants' estimates of the proportion of psychological studies published which apply each of a set of ten open science practices tended to hover around a mean of 50%.
-Although this could be read as implying literally that participants believe these practices are roughly as commonly applied as not, it could imply that some participants provided responses near 50% as an indication of uncertainty or indifference.
+Participants' estimates of the proportion of published psychological studies that apply each of the ten open science practices tended to hover around 50%.
+Although this could imply that participants literally believe these practices are roughly as commonly applied as not, it might also represent participants' uncertainty or indifference about the application of these practices in psychological studies.
 This said, 50% was the modal response for only a minority of practices (open access, data availability on request).
@@
 For example, on average students estimated that nearly a third of published psychological studies share data openly and that nearly half of studies are preregistered.
-Although we have not conducted a systematic review it is safe to say the true figures are rather lower [see @wichertsPoorAvailabilityPsychological2006].
+Although we have not conducted a systematic review it is safe to say the true figures are lower [see *Hardwicke*].
 
@@
 Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process.
-However, we did not probe students' factual knowledge of most methodological findings or concepts, except the replication crisis.
+However, excepting the replication crisis question, we did not probe students' factual knowledge of most methodological findings or concepts.
 It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) considerations without necessarily impacting their open science attitudes and beliefs.
@@
 
-corr$Practice <- c("Critical thinking", "HARKing", "Info for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered reports")
+corr$Practice <- c("Critical thinking", "HARKing", "Information for replicability", "Open access", "Open data", "Open materials", "p-hacking", "Preprints", "Preregistration", "Registered reports")
 
@@
 ```
+\
 *Figure A*

### 2021-11-16 preprocessing/preprocessing_students.R
update gender processing to reflect changes to gendercoder

@@ -102,11 +102,11 @@ df <- df %>%
 
 ######### RECODE GENDER ##########
 
-custom_dictionary <- list(
-  `female.` = "female",
-  `femamle` = "female",
+custom_dictionary <- c(
+  `female.` = "woman",
+  `femamle` = "woman",
   `-` = NA_character_,
-  `gender no longer has a place in modern society. sex is male.` = "male",
+  `gender no longer has a place in modern society. sex is male.` = "man",
   `queer man` = "queer man"
 )
 
@@ -116,7 +116,7 @@ custom_dictionary <- list(
 
 # new recode gender (which still doesn't work)
 df <- df %>%
-   mutate(gender  = recode_gender(gender, dictionary = c(manylevels_en, custom_dictionary), fill = TRUE))
+   mutate(gender  = recode_gender(gender, dictionary = c(manylevels_en, custom_dictionary), retain_unmatched = FALSE))
 
 ########## EXCLUSION CRITERIA ############
 

### 2021-11-16 analysis/Manuscript.Rmd
Update text chunk on gender in the manuscript

@@
 years old, `r age [4,2]` were 45–54 years old, and `r age [5,2]` was 55–64 years old. 
-Most participants (*n* = `r gender[1,2]`) reported that they were female, 
-`r gender[2,2]` reported that they were male, `r gender[3,2]` participant reported 
-their gender identity as "queer man", and `r gender[3,2]` participant reported 
-non-binary gender. *We still need to fix this...see email from Nov 12th*
+Most participants (*n* = `r gender[3,2]`) reported that they were women, 
+`r gender[1,2]` reported that they were men, and `r gender[2,2]` participant reported 
+non-binary gender.
 

### 2021-11-22 analysis/Manuscript.Rmd
Matt review

@@
 abstract: |
- BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
+ BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
  OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
@@
 # import the metadata
+#MW: I've removed the argument lazy = FALSE from the read_csv command which was causing an error for me - I don't think it's an argument used by that function?
 metadata <- here::here("data", "students_metadata.csv") %>%
-read_csv(col_names = TRUE, skip_empty_rows = TRUE, lazy = FALSE) %>%
+read_csv(col_names = TRUE, skip_empty_rows = TRUE) %>%
 filter(!is.na(old_variable))
@@
 These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
-These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@simmons21WordSolution2012; @wigboldus_encourage_2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-These calls for more reproducible and transparent research practices prompted the discipline to reflect on the norms and beliefs that underpin its practice of research.
-Many studies have polled researchers' understandings of and adherence to open science norms, beliefs, and practices [e.g., @baker500ScientistsLift2016; @openscienceworkinggroup2017SurveyOpen2018; @harrisUseReproducibleResearch2018].
-
-<!-- If we need to cut more words, we could cut the last sentence and combine the references into the previous sentence and add a phrase like "....prompted the discipline to reflect on and measure researchers norms, attitudes, and practices..." -->
+These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
+These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @harrisUseReproducibleResearch2018].
 
@@
 For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted to “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (p.
-14; i.e., *p*-hacking), while 9.6% reported rounding down *p*-values.
+14; i.e., *p*-hacking), while 9.6% reported rounding down *p*-values to meet a significance threshold.
 The extent to which incoming psychology students may---or may not---be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
 
-We conducted a descriptive study, asking incoming undergraduate psychology students about their beliefs regarding reproducibility and open science practices in psychology.
+We therefore conducted a descriptive study, asking incoming undergraduate psychology students about their beliefs regarding reproducibility and open science practices in psychology.
 Our survey encompassed questions concerning norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted), and replicability (how replicable students believe psychological research is).
@@
 abstract and discussion?
+
+MW: Cool - I've put that in the conclusion of the discussion along with a link. Hope that looks ok. I don't think we can quite fit it in the abstract with the 200 word limit.
 -->
@@
 For example, on average students estimated that nearly a third of published psychological studies share data openly and that nearly half of studies are preregistered.
-Although we have not conducted a systematic review it is safe to say the true figures are lower [see *Hardwicke*].
-
-<!-- ADD IN HARDWICKE & update sentence
-
-https://journals.sagepub.com/doi/full/10.1177/1745691620979806-->
+In contrast, an examination of a random sample of 250 psychology articles published between 2014 and 2017 [@hardwickeEstimatingPrevalenceTransparency2021] found that just 2% shared open data and 3% were preregistered.
 
@@
 It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.
+
+For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource.
+These questions are available along with our data and analysis code at https://osf.io/fz6ya/?view_only=46705e978a964cf6b872f4203d718fbe
+
+<!---
+MW: We still need to upload the data and code there before submitting, but just popping this placeholder in for now.
+I guess we'll need to leave out a couple of the files that have identifiable data in them?
+I've also uploaded an exported copy of the survey on the OSF project, with author details blinded.
+-->
 
@@
 \newpage
+
 # Reproducible Code Statement

### 2021-12-03 analysis/Manuscript.Rmd
Jen edits, ready to submit?

@@
     email: jen.beaudry@flinders.edu.au
-    address: Enter postal address here
+    address: Research Development and Support, Flinders University, Bedford Park, 5042
   - name: Matt N. Williams
@@
   - id: '1'
-    institution: Flinders University
+    institution: Flinders University, Australia
   - id: '2'
@@
   - id: '3'
-    institution: Deakin University
+    institution: Deakin University, Australia
   - id: '4'
-    institution: Swinburne University of Technology
+    institution: Swinburne University of Technology, Australia
 
@@
   papaja::apa6_pdf: default
+
+acknowledgement: |
+  The idea of this research was conceived at the 2018 UQ Open Science Conference and further developed at the 2019 Society for the Improvement of Psychological Science Unconference, What do first year psychology students think about (open) science?
+  Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
+# will enter this manually on the word document
+
 abstract: |
@@
 ```{r setup, include = FALSE}
+
 library(papaja) #install with devtools
@@
 r_refs("r-references.bib")
+
 ```
@@
   results = 'as.is')
+
 ```
@@
 # import the metadata
-#MW: I've removed the argument lazy = FALSE from the read_csv command which was causing an error for me - I don't think it's an argument used by that function?
+
 metadata <- here::here("data", "students_metadata.csv") %>%
@@
 filter(!is.na(old_variable))
-
-# relabel the variable names [completed in preprocessing]
-# df <- meta_rename(df, metadata = metadata, old = old_variable, new = new_variable)
 
@@
 These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @harrisUseReproducibleResearch2018].
+These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].
 
@@
 We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded].
-
-<!-- I wonder about saying something somewhere about how the items we developed (and openly shared) in this study could be useful for teachers who might wish to assess their own students' beliefs about open science practices in psychology?
-JB: That'd be great in the
-abstract and discussion?
-
-MW: Cool - I've put that in the conclusion of the discussion along with a link. Hope that looks ok. I don't think we can quite fit it in the abstract with the 200 word limit.
--->
 
@@
 
-<!--We had a footnote here (below) but given the word limit it might be safely left out unless a reviewer queries it...
-
-^[While the response "queer man" could potentially be coded as
-"male", we are aware that some individuals who report gender in this way would
-not feel that such reclassification was appropriate. We have retained the original
-response in order to provide a faithful representation of the participant's 
-self-reported gender.] -->
-
 Most participants reported attending university in Australia (*n* = `r uni_country[1,2]`), 
@@
 JB: I think we have to, don't we?-->
-The practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing.
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
+The ten practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing.
+Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
 
-We presented 20 scenarios (see Table \@ref(tab:normcounternormitems)). Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)).
+Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
 
@@
 
-# c <- metadata %>%
-#     filter(scale == "norms")
-
-# add a practice column in metadata
-
-# update this text  
-# d <- full_join(OSmost_long, c, by = c("OSmost" = "NewVariable")) %>%
-#   rename ("OSmost_label" = "ItemText")
-
 norm_items_wide <- pivot_wider(
@@
              align = c('lll'))
+
 ```
+
+*Note*: Participants responded to each item in the context of the scenario, “Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis.” Responses were provided on a Likert-type response scale ranging from (strongly disagree) to 5 (strongly agree).
 
@@
 
-hist(df$rep_perc, main = NULL, ylim = range(0,40), xlab = "Percentage")
+# hist(df$rep_perc, main = NULL, ylim = range(0,40), xlab = "Percentage")
+
+df %>%
+  filter(!is.na(rep_perc)) %>% 
+  ggplot(aes(x = rep_perc)) +
+  geom_histogram(aes(y=stat(count)), binwidth = 10, colour = "black", fill = "grey") +
+    xlab("Percentage") +
+    ylab("Frequency") +
+    theme_classic () +
+    theme(axis.text = element_text(size = 11), axis.title = element_text(size = 11))
+
 ```
@@
 It may well be that scientific training has enshrined peer review as an essential practice that is robust to change.
-
-<!--Bem begins his guide for writing articles as, “There are two possible articles you can write: (a) the article you planned to write when you designed your study or (b) the article that makes the most sense now that you have seen the results.
-They are rarely the same, and the correct answer is (b).”
-MW: I think the Bem paper would work here if students tended to be pro-HARKing but they tended to be against it.
--->
 
@@
 For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource.
-These questions are available along with our data and analysis code at https://osf.io/fz6ya/?view_only=46705e978a964cf6b872f4203d718fbe
-
-<!---
-MW: We still need to upload the data and code there before submitting, but just popping this placeholder in for now.
-I guess we'll need to leave out a couple of the files that have identifiable data in them?
-I've also uploaded an exported copy of the survey on the OSF project, with author details blinded.
--->
+These questions are available at https://tinyurl.com/yz76f4s6 [blinded].
 
@@
 
-```{r normsinpracticehistogram}
+```{r normsinpracticehistogram, fig.cap="Histogram of participants' prevalence ratings (%) for each of the norms in practice items. Responses provided on a visual slider from 0% to 100%."}
 
@@
   available_data = "Data on\nrequest",
-  detailed_methodology = "Information\nfor replication",
+  info_for_rep = "Information\nfor replication",
   harking = "HARKing",
-  incomplete_results = "p-hacking",
+  phack = "p-hacking",
   open_access = "Open access",
@@
   ggplot(aes(x = `prevalence rating`)) +
-  geom_histogram(aes(y=stat(count)), binwidth = 10) +
+  geom_histogram(aes(y=stat(count)), binwidth = 10, colour = "black", fill = "grey") +
     xlab("Prevalence Ratings (%)") +
@@
 ```
+
 \
+
 *Figure A*
@@
 
+<!-- We have a four references that aren't including the urls. Including here so we can add them to the final document.
+
+O’Grady, C.
+(2020, December 9).
+Psychology’s replication crisis inspires ecologists to push for more reliable research.
+Science.
+https://www.sciencemag.org/news/2020/12/psychology-s-replication-crisis-inspires-ecologists-push-more-reliable-research
+
+Vazire, S. (2019). Do we want to be credible or incredible? Association for Interdisciplinary Meta-research & Open Science conference, Melbourne. https://osf.io/thm9a/
+
+Yong, E.
+(2016, March 4).
+Psychology’s replication crisis can’t be wished away.
+The Atlantic.
+https://www.theatlantic.com/science/archive/2016/03/psychologys-replication-crisis-cant-be-wished-away/472272/
+
+Yong, E.
+(2018, November 19).
+Psychology’s replication crisis is running out of excuses.
+The Atlantic.
+https://www.theatlantic.com/science/archive/2018/11/psychologys-replication-crisis-real/576223/ -->
+
 \endgroup

### 2021-12-03 preprocessing/preprocessing_students.R
polishing the doc for posting

@@ -1,5 +1,5 @@
 ##### INCOMING STUDENTS' KNOWLEDGE OF RESEARCH PRACTICES #####
-##### Jennifer Beaudry, Matthew Williams, Michael Philipp ####
+##### Jennifer Beaudry, Matthew Williams, Michael Philipp & Emily Kothe ####
 
 ##### PREPROCESSING THE DATA #####
 
@@ -110,13 +110,10 @@ custom_dictionary <- c(
   `queer man` = "queer man"
 )
 
-# original recode gender
-# df <- df %>%
-  # mutate(gender  = recode_gender(gender, dictionary = c(broad, custom_dictionary), fill = TRUE))
 
-# new recode gender (which still doesn't work)
+# recode gender
 df <- df %>%
-   mutate(gender  = recode_gender(gender, dictionary = c(manylevels_en, custom_dictionary), retain_unmatched = FALSE))
+   mutate(gender = recode_gender(gender, dictionary = c(manylevels_en, custom_dictionary), retain_unmatched = FALSE))
 
 ########## EXCLUSION CRITERIA ############
 
@@ -143,9 +140,9 @@ study_var <- c("critical_cnorm",
                  "open_access_cnorm",
                  "preregistration",
                  "registered_report",
-                 "incomplete_results",
+                 "phack",
                  "harking",
-                 "detailed_methodology",
+                 "info_for_rep",
                  "preprint_pre",
                  "open_materials",
                  "open_data",
@@ -506,6 +503,6 @@ write.csv(df, here::here("data", "students_processed.csv"), row.names = FALSE)
 ### CODING REPLICATION CRISIS QUALTITATIVE RESPONSES
 
 # write this one variable to a csv file for coding
-write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), here::here( "data", "crisis_descriptions.csv")) #written for coding
+write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), here::here( "data", "crisis_descriptions.csv"))
 
-# cannot join it because we aren't linking the responses to the ids. Will use this file in Rmd.
+#written for manual coding, which is then used in Rmd

### 2021-12-03 analysis/Manuscript.Rmd
minor formatting changes for APA

@@
 abstract: |
- BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
- OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
- METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
- RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices.
+ Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
+ Objective: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
+ Method: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
+ Results: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices.
 When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%.
 Only 18% of participants had heard of the term "replication crisis".
- CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term.
+ Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term.
 Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
- TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
+ Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
 
@@
 These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].
+These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].
 
@@
 knitr::kable(norm_items_wide,
-             caption = "Norm and counternorm items",
+             caption = "Norm and Counternorm Items",
              align = c('lll'))
@@
 knitr::kable(practice_means,
-             caption = "Means and standard deviations for norms, counternorms, and the difference between norms and counternorms, with 95% confidence intervals (in square brackets)",
+             caption = "Means and Standard Deviations for Norms, Counternorms, and the Difference between Norms and Counternorms, with 95% Confidence Intervals (in Square Brackets)",
              digits = 2,
@@
 
-## Norms in practice
+## Norms in Practice
 Participants were also asked to estimate the proportion of psychology studies globally that apply each of ten practices (see Table \@ref(tab:normsinpractice)).
@@
 knitr::kable(in_practice_means,
-             caption = "Means, standard deviations, and 95% confidence intervals for the prevalence ratings for each research practice",
+             caption = "Means, Standard Deviations, and 95% Confidence Intervals for the Prevalence Ratings for Each Research Practice",
              digits = 2,
@@
 
-## The replication crisis
+## The Replication Crisis
 Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis".
@@
 
-```{r repperchistogram, fig.cap="Histogram of participants' responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
-We call repeating a study like this a \'replication study\'.
-At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%."}
+```{r repperchistogram, fig.cap="Histogram of Participants' Estimates of the Percentage of Psychology Studies that Replicate"}
 
@@
 ```
+
+*Note* responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+We call repeating a study like this a \'replication study\'.
+At a guess, how many of these replication studies do you think would produce the same conclusions as the original studies?\" Responses provided on a visual slider from 0% to 100%.
 
@@
 
-## Strengths and limitations
+## Strengths and Limitations
 Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings.
@@
 
-## Conclusion and teaching implications
+## Conclusion and Teaching Implications
 Overall these findings suggest that incoming psychology students have a degree of sympathy for open science norms.
@@
 knitr::kable(corr,
-             caption = "Correlations between norms and counternorms with the 95% confidence intervals (in square brackets) and the associated p-value",
+             caption = "Correlations between Norms and Counternorms with the 95% Confidence Intervals (in Square Brackets) and the Associated p-values",
              digits = 2,
@@
 
-```{r normsinpracticehistogram, fig.cap="Histogram of participants' prevalence ratings (%) for each of the norms in practice items. Responses provided on a visual slider from 0% to 100%."}
+```{r normsinpracticehistogram, fig.cap="Histogram of Participants' Prevalence Ratings (%) for each of the Norms in Practice Items."}
 
@@
 
-\
-
-*Figure A*
+*Note:* Responses provided on a visual slider from 0% to 100%.
 

### 2022-01-20 analysis/Manuscript.Rmd
ToP R and R initial changes

@@
     email: emily.kothe@deakin.edu.au
-
 affiliation:
@@
     institution: Swinburne University of Technology, Australia
-
 shorttitle: Psychology students' beliefs about open science
@@
   papaja::apa6_pdf: default
-
 acknowledgement: |
@@
   Our special thanks to those who contributed to the data collection effort including: Benjamin Le, Katie Gilligan-Lee, Annayah Prosser, Ian Fairholm, Jennie Ferrell, Kait Clark, Catherine Orr, Nick Burns, Rachel Searston, Rachel Stephens, Matthew Thompson, Aaron Drummond, Kathryn McGuigan, and Peter Cannon.
-# will enter this manually on the word document
-
 abstract: |
  Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
- Objective: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
- Method: International online survey with participants who were about to start their first course in psychology at a university (N = 239).
- Results: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices.
+ Objective: We aimed to describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
+ Method: An international online survey was conducted with participants who were about to start their first course in psychology at a university (*N* = 239).
+ Results: When asked about how research should be done, most students endorsed most (but not all) of ten open science practices.
 When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%.
 Only 18% of participants had heard of the term "replication crisis".
- Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term.
-Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
+ Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students in our sample were familiar with the term.
+The students were nevertheless sympathetic toward most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
  Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
-
 keywords: open science, psychology, teaching, reproducibility, replication
@@
 These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudry_swinburne_2019; @harrisUseReproducibleResearch2018].
-
-The most comprehensive set of principles for how science *ought* to be practiced are Merton's norms of science [@mertonNoteScienceDemocracy1942].
-Scientists [@andersonExtendingMertonianNorms2010] and graduate students [@andersonGraduateStudentExperience1994] alike have historically endorsed the normative value of Merton's principles.
-Furthermore, many of the recent practices designed to make science more transparent and open reflect Mertonian norms [see @vazireWeWantBe2019; @vazireWhereAreSelfcorrecting2020].
-For example, the practices of sharing preprints for open peer review and posting open data for reproducibility checks corresponds to the norms of *communality* and *organised skepticism*: Scientific claims should be openly subjected to critical scrutiny.
-Preregistration can be connected to the norm of *disinterestedness*: By making preregistered decisions about how to analyse data before results are produced, a researcher limits the degree to which substantive results produced by different analytic strategies affect their decisions regarding about analyses to report.
+These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudrySwinburneOpenScience2019; @harrisUseReproducibleResearch2018].
 
@@
 
-Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (such as open sharing of data and analysis code) are sometimes surprised that these are not *already* standard practice.
+Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (such as open sharing of data and analysis code) are sometimes surprised that these are not already standard practice.
 This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done.
@@
 We therefore conducted a descriptive study, asking incoming undergraduate psychology students about their beliefs regarding reproducibility and open science practices in psychology.
-Our survey encompassed questions concerning norms (how students felt research *should* be conducted), norms in practice (how students believe psychological research *is* conducted), and replicability (how replicable students believe psychological research is).
+Our survey encompassed questions concerning norms (how students felt research should be conducted), norms in practice (how students believe psychological research is conducted), and replicability (how replicable students believe psychological research is).
 Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and did not involve the specification or testing of hypotheses.
-We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded].
 
 # Methods
-Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6 [blinded].
+We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded].
+Our materials, data, and analysis script are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].
 
@@
 Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics.
-An invitation was sent to participants via email or a course website 1–2 weeks before their course began.
+These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and by contacting colleagues of the research team.
+Although we did not have any specific inclusion criteria with respect to country, although [most?
+all?] of the contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
+
+Each contact then sent their students invitations to participate via email or a course website 1–2 weeks before their course began.
 The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month and included a link to the survey.
+The measures and items in the survey were presented in the same order for all participants.
 
@@
 
-Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms rather than trying to measure endorsement of the more abstract Mertonian norms (cf.
-Anderson et al., 2007).
+Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms.
 <!-- Mention here our discussions workshopping of common open science norms at SIPs?
@@
 Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)).
-Participants rated their agreement with each prescriptive statement on a 1 (strongly disagree) to 5 (strongly agree) scale.
+Participants rated their agreement with each prescriptive statement on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale.
+We used the scenario of a specific researcher rather than referring to psychology researchers in general in an attempt to make the questions more concrete and engaging, and because referring to a single named researcher made it easier to construct short and clear items.
 
@@
 
-*Note*: Participants responded to each item in the context of the scenario, “Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis.” Responses were provided on a Likert-type response scale ranging from (strongly disagree) to 5 (strongly agree).
+*Note*: Participants responded to each item in the context of the scenario, “Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis.” Responses were provided on a Likert-type response scale ranging from 1 (*strongly disagree*) to 5 (*strongly agree*).
 
@@
 However, the extent to which participants endorsed open science norms varied substantially across different practices.
-Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing 'agree').
+Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing '*agree*').
 They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items varied between 3.5 and 4.
@@
 Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
-Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term.
+Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$Accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated).
 Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
@@
 Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms.
-Notably this wasn't the case for all open science practices (namely sharing of pre-prints and open data).
+Notably this was not the case for all open science practices (namely sharing of pre-prints and open data).
 It may well be that scientific training has enshrined peer review as an essential practice that is robust to change.
@@
 
-The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is *usually* conducted openly.
+The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is usually conducted openly.
 Nevertheless, the students appear to have at least somewhat over-estimated the prevalence of some open science practices.
@@
 Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students.
-However, collectively these results demonstrate some clear topics that might be targeted in our teaching: for example, emphasising the value of pre-prints and open data to research practice.
+In particular, the fact that our sample was relatively small and mostly comprised of students from Australia or the United Kingdom limits the extent to which our findings can be generalised to other populations.
 
@@
 Yet, research at the tertiary level casts doubt that the disciplinary reform from the past two decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].
+
+While we have interpreted our findings with respect to the norm and counternorm items as reflecting the students' personal endorsement of practices, it is plausible that their responses may have also been affected by their perceptions of what we might perceive as the "right" answers.
+Differences between endorsement of norms and counternorms may have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and p-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not.
+More broadly, our choices of terminology in constructing items are very likely to have affected participants' responses to some degree.
+For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item, since failing to "protect" participants' data might sound irresponsible.
+
+We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school, although interested readers could do so using our open data.
 
@@
 ## Conclusion and Teaching Implications
-Overall these findings suggest that incoming psychology students have a degree of sympathy for open science norms.
-Nevertheless, despite significant media attention on the replication crisis, few have heard of this crisis.
-Similarly, students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices).
+Overall these findings suggest that the incoming psychology students had a degree of sympathy for open science norms.
+Nevertheless, despite significant media attention on the replication crisis, few had heard of this crisis.
+Similarly, the students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices).
 It is therefore important that teachers of psychology not assume pre-existing knowledge among incoming students.
@@
 For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource.
-These questions are available at https://tinyurl.com/yz76f4s6 [blinded].
+These questions are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].
 

### 2022-03-14 analysis/Manuscript.Rmd
revisions to ToP R and R

@@
  Method: An international online survey was conducted with participants who were about to start their first course in psychology at a university (*N* = 239).
- Results: When asked about how research should be done, most students endorsed most (but not all) of ten open science practices.
-When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%.
-Only 18% of participants had heard of the term "replication crisis".
+ Results: When asked to indicate how a researcher should conduct her study, most students endorsed most (but not all) open science practices described.
+When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates tended to average near 50%.
+Only 18% of participants reported that they had heard the term "replication crisis".
  Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students in our sample were familiar with the term.
@@
 The last decade has seen unprecedented change in methodological and reporting practices in psychology.
-These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that close replications of published psychological studies are often unable to replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
+These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that many close replications of published studies did not replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
+Of course, psychology is not alone; the replication crisis extends to other fields, including economics [@camerer_evaluating_2016] and medicine [e.g., @errington_challenges_2021].
 These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
@@
 Our materials, data, and analysis script are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].
+Ethical approval for this study was granted by [institution blinded].
 
@@
 
-Ethical approval for this study was granted by [institution blinded].
-
 ## Participants
@@
 Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms.
-<!-- Mention here our discussions workshopping of common open science norms at SIPs?
-JB: I think we have to, don't we?-->
-The ten practices assessed in our survey included: critical thinking, preregistration, registered reports, p-hacking, hypothesising after the results are known (HARKing), providing sufficient information of replicability, preprints, open materials, open data, and open access publishing.
+The ten practices assessed in our survey are listed in Table \@ref(tab:normcounternormitems).
 Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
@@
 Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)).
-Participants rated their agreement with each prescriptive statement on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale.
+Participants rated their agreement separately for each norm and counternorm on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale.
 We used the scenario of a specific researcher rather than referring to psychology researchers in general in an attempt to make the questions more concrete and engaging, and because referring to a single named researcher made it easier to construct short and clear items.
@@
 
-Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to,
+Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to:
 
@@
 Our questions focused primarily on attitudes and beliefs so that we could better document the implicit understanding that guided students’ thoughts about the research process.
-However, excepting the replication crisis question, we did not probe students' factual knowledge of most methodological findings or concepts.
-It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) considerations without necessarily impacting their open science attitudes and beliefs.
+However, we did not probe students' factual knowledge of most methodological findings or concepts, except the replication crisis.
+It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) considerations without necessarily influencing their open science attitudes and beliefs.
 Yet, research at the tertiary level casts doubt that the disciplinary reform from the past two decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].
 
-While we have interpreted our findings with respect to the norm and counternorm items as reflecting the students' personal endorsement of practices, it is plausible that their responses may have also been affected by their perceptions of what we might perceive as the "right" answers.
+Although we have interpreted our findings with respect to the norm and counternorm items as reflecting  students' personal endorsement of practices, their perceptions of what we might perceive as the "right" answers could have also influenced their responses.
 Differences between endorsement of norms and counternorms may have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and p-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not.
-More broadly, our choices of terminology in constructing items are very likely to have affected participants' responses to some degree.
+More broadly, our choices of terminology in constructing items likely affected participants' responses to some degree.
 For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item, since failing to "protect" participants' data might sound irresponsible.
+Future research could examine the influence of revised language on participants' responses.
 
-We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school, although interested readers could do so using our open data.
+We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school.
+Interested readers could conduct this comparison using our open data.
 

### 2022-03-14 preprocessing/preprocessing_students.R
Recode all students in a psych degree as having a psych major

@@ -397,7 +397,7 @@ df <- df %>%
 # create a new variable for major type
 # For participants who mention a major in psychology, code as "psychology"
 # For participants who do not, code as "not psychology"
-## TODO - check coding for participants in psychology degrees such as the B Psych
+# Code all students in a psychology degree as having a psychology major
 df <- df %>%
   mutate(major_recoded = toTitleCase(major)) %>%
   mutate(
@@ -491,8 +491,11 @@ df <- df %>%
       is.na(major_recoded) ~ NA_character_,
       degree_type == "Psychology" ~ "Psychology",
       TRUE ~ "Uncoded"
-    )
-  )
+    ))
+
+df <- df %>%
+  mutate(major_recoded = case_when(degree_type == "Psychology" ~ "Psychology",
+         TRUE ~ major_recoded))
 
 ################### WRITE DATA TO CSV #############
 

### 2022-03-14 analysis/Manuscript.Rmd
minor edits for R and R

@@
 We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded].
-Our materials, data, and analysis script are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].
+Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6 [blinded].
 Ethical approval for this study was granted by [institution blinded].
@@
 These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and by contacting colleagues of the research team.
-Although we did not have any specific inclusion criteria with respect to country, although [most?
+Although we did not have any specific inclusion criteria with respect to country, [most?
 all?] of the contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.

### 2022-03-21 analysis/Manuscript.Rmd
create Table 1 with metadata

@@
 ```{r normcounternormitems}
-norm_items = data.frame(
-  "Practice" = c("Critical thinking", "Critical thinking", "HARKing", "HARKing", "Information for replicability", "Information for replicability",
-                 "Open access", "Open access", "Open data", "Open data", "Open materials", "Open materials",
-                 "p-hacking", "p-hacking", "Preprints", "Preprints", "Preregistration", "Preregistration",
-                 "Registered reports", "Registered reports"),
-  "Category" = rep(c("Norm", "Counternorm"), times = 10),
-  "Item" = c("Deborah used previously published research to inform her research study. Deborah should be critical of the findings published in journals because published research can be wrong.",
-             "Deborah used previously published research to inform her research study.
-Deborah should accept the findings published in journals because journals would not publish research with errors.",
-             "Deborah should only describe her study as a test of a hypothesis if she decided on her hypothesis and how she would test it before she started collecting data.",
-             "Once Deborah has analysed her results, it would be good scientific practice for her to write her manuscript as if she predicted those results from the beginning.",
-             "When reporting the findings of her study, Deborah should describe how she completed the study in enough detail that another researcher could repeat her entire study without having to check any details with her - even if this means including lots of “boring” practical details in her report, or in an appendix.",
-             "When reporting the findings of her study, it would be good scientific practice for Deborah to gloss over some of the practical details so she can tell a good story.",
-             "Once her study is complete, Deborah should publish her findings in a journal that is free for others to access.",
-             "Once her study is complete, Deborah should publish the findings in the most prestigious journal she can, even if that journal charges others a fee to access the report.",
-             "When Deborah publishes her study, she should post the anonymous responses from participants online so that anyone can access and use the responses in their own research.",
-             "Deborah should keep the participants’ responses from her study protected, so that only she and her research team can access them.",
-             "Deborah should share the written materials and measures for her study openly online so that other researchers and members of the public can access and use them.",
-             "Deborah should keep the written materials and measures for her study protected, so that only she and her research team can access them.",
-             "Deborah should report the findings of all analyses of her data that she conducts.",
-             "It would be good scientific practice for Deborah to run many different analyses of her data, and report only those that produce interesting findings.",
-             "Deborah should post a manuscript describing the findings of her study openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal.",
-             "Deborah should not post a manuscript describing the findings of her study online until after it has been checked by experts (peer reviewed) and accepted for publication in a journal.",
-             "Before collecting her data, Deborah should write down what her hypotheses are and how she plans to collect and analyse data.
-She should then save her plan in an online registry so others can tell what methods and analyses she will use to test her hypotheses after collecting data.",
-             "Deborah should decide which data analyses are suitable to test her hypotheses only after looking at her data.",
-             "Deborah should submit a plan for her study to a journal to be checked by experts (peer reviewed) before she collects and analyses data.",
-             "Deborah should submit her study to a journal to be checked by experts (peer reviewed) only after she has finished collecting and analysing her data."))
 
-# [breadcrumb Sept 10: pull in this info from the meta data]
+# create a table with the norms and counternorm items from the metadata
+
+norm_items <- metadata %>% 
+  filter(scale == "norms") %>% 
+  mutate(Category = case_when(str_detect(new_variable, "_cnorm") ~ "Counternorm",
+         TRUE ~ "Norm"))   %>% 
+  select (c(text_label, item_text, Category))
 
@@
   names_from = Category,
-  values_from = Item)
+  values_from = item_text) %>% 
+  relocate(Norm, .before = Counternorm)
 
@@
              caption = "Norm and Counternorm Items",
+             col.names = c("Practice", "Norm", "Counternorm"),
              align = c('lll'))

### 2022-03-21 analysis/Manuscript.Rmd
create Table 2 with metadata

@@
 
-```{r normsinpracticeitems}
+```{r normsinpracticeitemsold, eval = FALSE}
 practice_items = data.frame(
@@
 
+```{r normsinpracticeitems}
+
+# create a table with the norms in practice items from the metadata
+
+practice_items <- metadata %>% 
+  filter(scale == "practice") %>% 
+  select (c(text_label, item_text))
+
+knitr::kable(practice_items,
+             caption = "Norms in practice items",
+             col.names = c("Practice", "Item"),
+             align = c('ll'))
+
+```
 \
@@
 Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
-Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$Accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated).
+Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated).
 Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
-Only `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
+Only `r sum(crisis_descriptions$accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
 

### 2022-03-21 analysis/Manuscript.Rmd
add interrater reliability for crisis coding

@@
 library(broom)
+library(irr)
 
@@
 crisis_descriptions = read.csv(here::here ("data", "crisis_descriptions_marked.csv"))
+inter_rater <- read.csv(here::here("data", "crisis_descriptions_marked_comparison.csv"))
 
@@
 
-```{r normsinpracticeitemsold, eval = FALSE}
-practice_items = data.frame(
-  "Practice" = c("Preregistration", "Registered Reports", "p-hacking", "HARKing", "Information for replicability",
-                 "Preprints", "Open materials", "Open data", "Data on request", "Open access"),
-  "Item" = c("The plan for collecting and analysing data for the study is posted in an online registry before data collection starts",
-             "A plan for the study is submitted to a journal to be checked by experts (peer reviewed) before the data is collected and analysed",
-             "The researchers run many different analyses of the data, and report only those that produce interesting findings",
-             "The researchers describe their results as if they predicted those results from the beginning, even if that isn’t actually true",
-             "The researchers provide enough practical detail in their written report that another researcher could fully repeat (replicate) their study without needing to ask any questions of the original researchers",
-             "A manuscript describing the findings of the study is posted openly online as soon as it is complete, even if the manuscript has not yet been checked by experts (peer reviewed) and accepted for publication in a journal",
-             "The written materials and measures for the study are posted openly online so that other researchers and members of the public can access and use them",
-             "Once the study is published, the anonymous responses from participants are posted openly online so that anyone can access and use the responses in their own research",
-             "Once the study is published, the anonymous responses from participants are available to other researchers on request",
-             "The research report describing the study and its findings is published in a journal that is free for anyone to access")
-)
-
-knitr::kable(practice_items,
-             caption = "Norms in practice items",
-             align = c('ll'))
-
-```
-
 ```{r normsinpracticeitems}
@@
 ## The Replication Crisis
+
+```{r coding qual responses}
+
+inter_rater_test <- inter_rater %>% 
+  select(c(coding_1, coding_2))
+
+# calculate the percentage of agreement
+perc_agree <- agree(inter_rater_test, tolerance = 0)
+kappa <- kappa2(inter_rater_test)
+
+```
+
 Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis".
@@
 Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
+Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions.
+They resolved the disagreements through discussion.
 Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated).
@@
 ```{r repperchistogram, fig.cap="Histogram of Participants' Estimates of the Percentage of Psychology Studies that Replicate"}
-
-# hist(df$rep_perc, main = NULL, ylim = range(0,40), xlab = "Percentage")
 
@@
 Interested readers could conduct this comparison using our open data.
-
-<!--
-MW: The bit from "It's quite possible..." is sensible, but if needed could possibly shave some words off by excluding? 
-See how we go when we check full word count
--->
 
@@
 
+```{r awarenessofrepcrisisbymajor}
+
+psyc_major <- df %>% 
+  filter(major_recoded)
+
+```
+
+Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis".
+Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis, and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.
+
+Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
+Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions.
+They resolved the disagreements through discussion.
+Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated).
+Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
+Only `r sum(crisis_descriptions$accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
+
+\newpage
+
 # Reproducible Code Statement

### 2022-03-21 analysis/Manuscript.Rmd
analyse awareness by major

@@
 
+if(! requireNamespace('box')) {
+  install.packages('box')
+}
+
 library(papaja) #install with devtools
@@
 library(broom)
-library(irr)
+
+box::use(irr[agree,kappa2]) # load just these two functions from the `irr` package
 
@@
 psyc_major <- df %>% 
-  filter(major_recoded)
+  select(c(major_recoded, crisis)) %>% 
+  na.omit() # remove NAs
+
+not_psyc <- psyc_major %>% 
+  filter(major_recoded == "Not psychology")
+
+psyc <- psyc_major %>% 
+  filter(major_recoded == "Psychology")
+
+# run the chi-square
+psyc_major_table <- table(psyc_major)
+
+chi <- chisq.test(psyc_major_table)
 
@@
 
-Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis".
-Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis, and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.
+At a reviewer's request, we ran an additional exploratory analysis to determine whether
+the proportion of students who are unaware of the replication crisis differs between psychology 
+and non-psychology majors.
+We were able to code the majors for `r length(psyc_major$major_recoded)` students; of these `r round(length(psyc$crisis)/length(psyc_major$crisis)*100, 0)`% reported that psychology was their major.
 
-Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
-Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions.
-They resolved the disagreements through discussion.
-Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated).
-Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
-Only `r sum(crisis_descriptions$accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
+Of those majoring in psychology, `r round(sum(psyc$crisis==1)/length(psyc$crisis)*100,0)`% indicated that they 
+were aware of the replication crisis. Of those majoring in another program other than psychology, 
+`r round(sum(not_psyc$crisis==1)/length(not_psyc$crisis)*100,0)`% indicated that they were aware of the replication crisis.
+A chi-square test of independence indicated that there was no significant difference between psychology
+majors and non-majors in terms of their self-reported awareness of the replication crisis, X^2^ (`r chi$parameter`) = `r round(chi$statistic,2)`, *p* = `r round(chi$p.value,2)`. 
+This lack of a signficant difference should be replicated in a larger population; however, it suggests that psychology instructors should not presume that students choosing to major in psychology are aware of the replication crisis.
 

### 2022-03-27 analysis/Manuscript.Rmd
update blind osf link

@@
 We preregistered the exploratory nature of this study at https://tinyurl.com/4p64mvwp [blinded].
-Our materials, data, and analysis script are available at https://tinyurl.com/yz76f4s6 [blinded].
+Our materials, data, and analysis script are available at https://tinyurl.com/excm4heu [blinded].
 Ethical approval for this study was granted by [institution blinded].
@@
 These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and by contacting colleagues of the research team.
-Although we did not have any specific inclusion criteria with respect to country, [most?
-all?] of the contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
+Although we did not have any specific inclusion criteria with respect to country, most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
 
-Each contact then sent their students invitations to participate via email or a course website 1–2 weeks before their course began.
+Each contact sent their students invitations to participate via email or a course website 1–2 weeks before their course began.
 The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month and included a link to the survey.
@@
 Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students.
-In particular, the fact that our sample was relatively small and mostly comprised of students from Australia or the United Kingdom limits the extent to which our findings can be generalised to other populations.
+In particular, the fact that our sample was relatively small and mostly comprised of students from Australia, NZ, or the United Kingdom limits the extent to which our findings can be generalised to other populations.
 

### 2022-03-28 analysis/Manuscript.Rmd
reduce word count in abstract & intro

@@
 abstract: |
- Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to students’ existing understandings.
- Objective: We aimed to describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in psychology.
- Method: An international online survey was conducted with participants who were about to start their first course in psychology at a university (*N* = 239).
- Results: When asked to indicate how a researcher should conduct her study, most students endorsed most (but not all) open science practices described.
-When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates tended to average near 50%.
+ Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt to students’ existing understandings.
+ Objective: We aimed to describe what incoming undergraduate students of psychology believe about reproducibility and open science practices.
+ Method: We conducted an online survey with participants who were about to start their first course in psychology at a university (*N* = 239).
+ Results: When asked to indicate how a researcher should conduct her study, most students endorsed several open science practices.
+When asked to estimate the proportion of published psychological studies that follow various open science practices, participants' estimates averaged near 50%.
 Only 18% of participants reported that they had heard the term "replication crisis".
- Conclusion: Despite relatively significant media attention on the replication crisis, few incoming psychology students in our sample were familiar with the term.
-The students were nevertheless sympathetic toward most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
+ Conclusion: Despite media attention about the replication crisis, few incoming psychology students in our sample were familiar with the term.
+The students were nevertheless in favour of most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
  Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
@@
 
-The last decade has seen unprecedented change in methodological and reporting practices in psychology.
-These changes were partly precipitated by what is popularly known as the "replication crisis": The discovery that many close replications of published studies did not replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
+Methodological and reporting practices in psychology have changed over the last decade, partly precipitated by the "replication crisis": The discovery that many close replications of published studies did not replicate the original findings [@kleinInvestigatingVariationReplicability2014; @kleinManyLabsInvestigating2018].
 Of course, psychology is not alone; the replication crisis extends to other fields, including economics [@camerer_evaluating_2016] and medicine [e.g., @errington_challenges_2021].
-These apparent problems with replication have led to a variety of potential solutions to make research practices more reproducible and transparent, including more frequent publication of replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analysis plans [@nosekPreregistrationRevolution2018].
-These calls for more reproducible and transparent research practices have prompted the discipline to reflect on and measure researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudrySwinburneOpenScience2019; @harrisUseReproducibleResearch2018].
+These apparent problems with replication have led to various potential solutions to make research practices more reproducible and transparent, including more published replication studies [see @brandtReplicationRecipeWhat2014], more thorough reporting of methods and results [@wigboldusEncouragePlayingData2016], open sharing of data [see @meyerPracticalTipsEthical2018], and preregistration of data collection and analytic plans [@nosekPreregistrationRevolution2018].
+These calls for more reproducible and transparent research practices have prompted the discipline to examine researchers' norms, attitudes, and practices [e.g., @baker500ScientistsLift2016; @beaudrySwinburneOpenScience2019; @harrisUseReproducibleResearch2018].
 
-Rapid changes in methodological practice and empirical findings present significant pedagogical challenges for the teacher of psychology.
+These rapid changes present significant pedagogical challenges for the teacher of psychology.
 Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace.
-Furthermore, training in emerging methodological practices is crucial for graduate students who may go on to apply psychological research methods themselves.
+Furthermore, knowledge of emerging methodological practices is crucial for graduate student training.
 Even for students who do not go on to conduct research, an understanding of contemporary methodological practices---and problems with methodological practices in psychology---is essential for becoming informed and critical consumers of psychological knowledge.
-Studies have explored strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020; @schonbrodtTrainingStudentsOpen2019].
+Studies have explored strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020].
 These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
-There are several reasons why this knowledge could be useful.
+This knowledge could be useful for two main reasons.
 
-First, unlike some psychological phenomena in undergraduate courses (e.g., models of working memory, or the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018].
-Students may have plausibly obtained some knowledge about these issues prior to (or independently of) their formal studies.
+First, unlike some psychological phenomena in undergraduate courses (e.g., the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018].
+As such, students may have some knowledge about these issues prior to their formal studies.
 Teaching methods should be informed by some understanding of students' pre-existing levels of knowledge.
 
-Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (such as open sharing of data and analysis code) are sometimes surprised that these are not already standard practice.
-This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of how science should be done.
+Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (e.g., open sharing of data and analysis code) are sometimes surprised that these are not already standard practice.
+This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of research practices.
 On the other hand, some evidence suggests that undergraduate students may quickly begin to engage in practices that hamper reproducibility.
-For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their Canadian sample admitted to “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (p.
+For example, @moranKnowItBad2021 found that 26.5% of the undergraduate students in their  sample admitted to “Conducting multiple statistical analyses on the same dataset in an attempt to find a statistically significant result” (p.
 14; i.e., *p*-hacking), while 9.6% reported rounding down *p*-values to meet a significance threshold.
-The extent to which incoming psychology students may---or may not---be “naive open scientists” is useful knowledge for guiding pedagogical approaches.
+Knowing the extent to which incoming psychology students may---or may not---be “naive open scientists” could help guide pedagogical approaches.
 
-We therefore conducted a descriptive study, asking incoming undergraduate psychology students about their beliefs regarding reproducibility and open science practices in psychology.
+To examine this, we conducted a descriptive study, asking incoming students in undergraduate psychology courses about their beliefs regarding reproducibility and open science practices.
 Our survey encompassed questions concerning norms (how students felt research should be conducted), norms in practice (how students believe psychological research is conducted), and replicability (how replicable students believe psychological research is).
-Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive, and did not involve the specification or testing of hypotheses.
+Our study was exploratory [see @wagenmakersAgendaPurelyConfirmatory2012] and descriptive; as such, we did not specify or test hypotheses.
 
@@
 Our materials, data, and analysis script are available at https://tinyurl.com/excm4heu [blinded].
-Ethical approval for this study was granted by [institution blinded].
+Ethical approval for this study was granted by [blinded].
 
@@
 Of those who started the survey (*n* = `r n_all`), we screened out `r ex` 
-participants who were not eligible to participate based on the combination of our
+participants who were ineligible based on our
 preregistered exclusion criteria. Specifically, we screened out people who were younger than 18 years (*n* = `r age_ex`). We also screened out individuals who had already 
@@
 
-Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms.
-The ten practices assessed in our survey are listed in Table \@ref(tab:normcounternormitems).
+Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms (see Table \@ref(tab:normcounternormitems)).
 Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
@@
 knitr::kable(practice_items,
-             caption = "Norms in practice items",
+             caption = "Norms in Practice Items",
              col.names = c("Practice", "Item"),
@@
 Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
-Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions.
-They resolved the disagreements through discussion.
-Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some or many scientific findings cannot be replicated).
-Example responses included, "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated".
-Only `r sum(crisis_descriptions$accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
+Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions and resolved the disagreements through discussion.
+Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some scientific findings cannot be replicated).
+For example, "Where previously trusted studies have been replicated the results were not able to be replicated".
+Only `r sum(crisis_descriptions$accurate == "n")` responses indicated a misunderstanding of the term (e.g., "Plagiaris[m]").
 
-Participants' estimates of the replicability of psychological studies were variable.
+Participants' estimates of the replicability of psychological studies were variable (see Figure \@ref(fig:repperchistogram)).
 The mean (_M_ = `r mean(df$rep_perc, na.rm = TRUE)`) was near the midpoint of 50%, but with substantial variability around this estimate (_SD_ = `r sd(df$rep_perc, na.rm = TRUE)`, range = `r min(df$rep_perc, na.rm = TRUE)` to `r max(df$rep_perc, na.rm = TRUE)`).
-A histogram of participants' responses is provided in Figure \@ref(fig:repperchistogram).
 
@@
 
-*Note* responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+*Note* Responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
 We call repeating a study like this a \'replication study\'.
@@
 For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource.
-These questions are available at https://osf.io/fz6ya/?view_only=51769fc1de304ad3ba0e12a26494ac40 [blinded].
+These questions are available at https://tinyurl.com/excm4heu [blinded].
 

### 2022-03-29 analysis/Manuscript.Rmd
cut words from Methods

@@
 Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics.
-These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and by contacting colleagues of the research team.
-Although we did not have any specific inclusion criteria with respect to country, most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
+These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and through contacts of the research team.
+Although we did not have inclusion criteria with respect to country, most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
 
 Each contact sent their students invitations to participate via email or a course website 1–2 weeks before their course began.
-The invitation specified that student needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month and included a link to the survey.
+The invitation specified that students needed to be 18 years or older and starting their first course/unit of study in psychology at a university within the following month and included a link to the survey.
 The measures and items in the survey were presented in the same order for all participants.
@@
 participants who were ineligible based on our
-preregistered exclusion criteria. Specifically, we screened out people who were younger than 18 years (*n* = `r age_ex`). We also screened out individuals who had already 
+preregistered exclusion criteria. Specifically, we screened out people who were younger 
+than 18 years (*n* = `r age_ex`). We also screened out individuals who had already 
 started a psychology unit at a university, regardless of whether they had 
@@
 psychology unit at a university (*n* = `r el[2,2]`); or did not answer this 
-question (*n* = `r el[5,2]`). We then excluded additional responses that 
+question (*n* = `r el[5,2]`). We excluded additional responses that 
 Qualtrics flagged as spam (*n* = `r status [1,2]`) or as a survey preview 
 (*n* = `r status [2,2]`). Finally, we excluded participants who met all other 
-eligibility criteria, but did not respond to any of the main items
-in the study (*n* = `r nmiss`).
+eligibility criteria, but did not respond to any of the main survey items (*n* = `r nmiss`).
 
-The remaining `r n` participants were eligible based on starting their first unit 
-of study in psychology at a university within the next month. Of the eligible 
-participants, most reported that they were 18–24 years old (*n* = `r age[1,2]`);
+Of the eligible `r n` participants, most reported that they were 18–24 years old (*n* = `r age[1,2]`);
 `r age [2,2]` reported that they were 25–34 years old, `r age [3,2]` were 35–44 
@@
 
-Most participants reported attending university in Australia (*n* = `r uni_country[1,2]`), 
+Most participants attended university in Australia (*n* = `r uni_country[1,2]`), 
 the United Kingdom (*n* = `r uni_country[5,2]`), or New Zealand (*n* = 
 `r uni_country[4,2]`). Nearly all reported graduating from high school or secondary 
-school (*n* = `r hs_status[3,2]`). Of those participants who attended high school, 
-fewer than half completed psychology courses in high school (*n* = `r hs_psyc[2,2]`).
+school (*n* = `r hs_status[3,2]`). Of those who attended high school, 
+fewer than half completed high school psychology courses (*n* = `r hs_psyc[2,2]`).
 Participants reported `r nrow(nationality)` different nationalities; the most 
-common were Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = 
+common were from Australia (*n* = `r nationality[3,2]`), the United Kingdom (*n* = 
 `r nationality[24,2]`), and China (*n* = `r nationality[6,2]`). About two-thirds of 
@@
 Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms (see Table \@ref(tab:normcounternormitems)).
-Although we acknowledge the merits of some of these practices are debatable [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
+Although we acknowledge the debatable merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
 
-Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario, "Imagine that Deborah is a psychology researcher who has designed a study to test a specific hypothesis." (see Table \@ref(tab:normcounternormitems)).
+Each practice was elucidated by a pair of items (pro-open science; counter-open science) in the context of a common scenario (see the note accompanying Table \@ref(tab:normcounternormitems)).
 Participants rated their agreement separately for each norm and counternorm on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale.
-We used the scenario of a specific researcher rather than referring to psychology researchers in general in an attempt to make the questions more concrete and engaging, and because referring to a single named researcher made it easier to construct short and clear items.
+We used the scenario of a specific researcher rather than referring to psychology researchers in general because it allowed us to make the items more concrete, engaging, and clear.
 
@@
 
-We also sought to measure participants' normative beliefs about how researchers actually conduct psychological science.
-To that end we asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to the ten norm–counternorm pairs described above, with two exceptions (see Table \@ref(tab:normsinpracticeitems)).
-We excluded one norm because it did not refer to externally observable behaviour (critically evaluating published studies vs.
-accepting them), and we included one practice out of interest (data sharing on request).
+We also measured participants' normative beliefs about how researchers actually conduct psychological science.
+We asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)).
+We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data sharing on request).
 Participants indicated their estimate on a slider bar ranging from 0% to 100%.
@@
 
-Participants' beliefs about the replicability of results in psychological science were indexed by two questions. The first asked participants to:
+Two questions measured participants' beliefs about the replicability of results in psychological science. The first asked participants to:
 
@@
 A second question asked participants whether they had heard of the replication crisis.
-Those who had heard of the replication crisis were asked two additional open-ended questions.
-First, they were asked to describe what the replication crisis is.
-Second, they were asked which scientific disciplines were most affected by the replication crisis.
+Those who had heard of the replication crisis were asked two additional open-ended questions: (1) describe the replication crisis, and (2) name the scientific disciplines most affected by the replication crisis.
 

### 2022-03-29 analysis/Manuscript.Rmd
reduce words from Results

@@
 We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data sharing on request).
-Participants indicated their estimate on a slider bar ranging from 0% to 100%.
+Participants indicated their estimate on a visual slider from 0% to 100%.
 
@@
 
-Estimates were recorded using a slider bar ranging from 0% to 100%. 
+Estimates were recorded using a visual slider from 0% to 100%. 
 A second question asked participants whether they had heard of the replication crisis.
@@
 
-In line with our preregistered analysis plan, we calculated the difference in means
-between responses to each norm item and its accompanying counternorm, along with 
-95% confidence intervals. For this analysis, we removed three cases with missing values. 
+As preregistered, we calculated the difference in means
+between responses to each norm item and its accompanying counternorm (with 
+95% confidence intervals). For this analysis, we removed three cases with missing values. 
 Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values.
@@
 
-In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm.
-However, the extent to which participants endorsed open science norms varied substantially across different practices.
-Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid p-hacking (means > 4; 4 representing '*agree*').
-They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies; the means for these items varied between 3.5 and 4.
+In general, the students seemed to endorse open science practices: For seven of the ten open science practices, agreement with the norm item was stronger than for the corresponding counternorm item.
+However, participants' endorsement of norms varied substantially across different practices.
+Participants most strongly endorsed norms that researchers should provide sufficient information about studies to permit replicability, be critical of published findings, and avoid *p*-hacking.
+They also tended to agree that researchers should avoid HARKing, share papers as open access, share open materials, and preregister their studies.
 On the other hand, they tended to disagree with the practice of sharing preprints prior to peer review and, to a lesser extent, with sharing open data.
@@
 For many of these practices, participants’ estimates were near the midpoint of 50%.
-This said, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
+Nonetheless, participants perceived some practices as being applied relatively infrequently: For example, the mean estimate of the prevalence of HARKing, preprint sharing before publication, and open data sharing were all near 30%.
 See Figure A in Supplemental Materials to see the distribution for each item.
-Participants perceived the most common practice was providing enough information in written reports to permit replication without asking any questions of the original researchers.
+Participants perceived that the most common practice was providing enough information in written reports to permit replication without asking questions of the original researchers.
 
@@
 Participants who indicated they had heard of the replication crisis were asked, "What do you think 'the replication crisis' is"?
-Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions and resolved the disagreements through discussion.
+Two independent coders marked the responses as accurate or inaccurate; they agreed on `r perc_agree$value`% of the descriptions and resolved disagreements through discussion.
 Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most (`r sum(crisis_descriptions$accurate =="y")/length(df$crisis_text[is.na(df$crisis_text)==FALSE])*100`%) provided responses consistent with the conventional interpretation of the term (i.e., describing a realisation that some scientific findings cannot be replicated).

### 2022-03-29 analysis/Manuscript.Rmd
reduce words from Discussion, Abstract, and Introduction

@@
     email: jen.beaudry@flinders.edu.au
-    address: Research Development and Support, Flinders University, Bedford Park, 5042
+    address: Research Development and Support, Flinders University, Bedford Park, SA, 5042
   - name: Matt N. Williams
@@
 abstract: |
- Background: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt to students’ existing understandings.
- Objective: We aimed to describe what incoming undergraduate students of psychology believe about reproducibility and open science practices.
+ Background: Understanding students’ naive conceptions about the norms that guide scientific best practice is important so that teachers can adapt to students’ existing understandings.
+ Objective: We examined what incoming undergraduate students of psychology believe about reproducibility and open science practices.
  Method: We conducted an online survey with participants who were about to start their first course in psychology at a university (*N* = 239).
@@
 
-These rapid changes present significant pedagogical challenges for the teacher of psychology.
+These changes present significant pedagogical challenges for the teacher of psychology.
 Keeping textbooks and other instructional materials up to date is difficult when supposedly well-established findings are contradicted by new replications emerging at a rapid pace.
 Furthermore, knowledge of emerging methodological practices is crucial for graduate student training.
-Even for students who do not go on to conduct research, an understanding of contemporary methodological practices---and problems with methodological practices in psychology---is essential for becoming informed and critical consumers of psychological knowledge.
+Even for students who do not go on to conduct research, an understanding of contemporary methodological practices---and problematic methodological practices---is essential for becoming informed and critical consumers of psychological knowledge.
 Studies have explored strategies for educating psychology students about replicability and open science practices [e.g., @chopikHowWhetherTeach2018; @graheHarnessingUndiscoveredResource2012; @jekelHowTeachOpen2020].
-These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what these students know or believe about open science research practices prior to entering the university classroom.
+These initiatives may help ingrain open science norms and change attitudes about research practices, but we know little about what students know or believe about open science research practices prior to entering the university classroom.
 This knowledge could be useful for two main reasons.
@@
 First, unlike some psychological phenomena in undergraduate courses (e.g., the internal workings of human senses), the replication crisis is frequently discussed in mainstream and social media [e.g., @ogradyPsychologyReplicationCrisis2020; @yongPsychologyReplicationCrisis2016; @yongPsychologyReplicationCrisis2018].
-As such, students may have some knowledge about these issues prior to their formal studies.
-Teaching methods should be informed by some understanding of students' pre-existing levels of knowledge.
+As such, incoming students might have some knowledge about these issues prior to their formal studies.
+Teaching methods should be informed by understanding students' pre-existing levels of knowledge.
 
-Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (e.g., open sharing of data and analysis code) are sometimes surprised that these are not already standard practice.
+Second, anecdotal evidence suggests that students being taught about open science practices and reproducibility reforms (e.g., open sharing of data and code) are sometimes surprised that these are not already standard practice.
 This could imply a need for educators to reinforce and build on students' “naive” impressions rather than radically altering their understanding of research practices.
@@
 Our materials, data, and analysis script are available at https://tinyurl.com/excm4heu [blinded].
-Ethical approval for this study was granted by [blinded].
+Ethical approval was granted by [blinded].
 
@@
 These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and through contacts of the research team.
-Although we did not have inclusion criteria with respect to country, most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
+We did not have inclusion criteria with respect to country, but most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
 
@@
 We asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)).
-We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data sharing on request).
+We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data availability on request).
 Participants indicated their estimate on a visual slider from 0% to 100%.
@@
 
-Despite efforts to improve the replicability of research over the past decade, and corresponding media attention, most incoming psychology students in our sample were unaware of the replication crisis.
+Despite efforts to improve the replicability of research and the corresponding media attention, most incoming psychology students in our sample were unaware of the replication crisis.
 Encouragingly, on the other hand, most tended to endorse open science norms more-so than counternorms.
@@
 
-Participants' estimates of the proportion of published psychological studies that apply each of the ten open science practices tended to hover around 50%.
-Although this could imply that participants literally believe these practices are roughly as commonly applied as not, it might also represent participants' uncertainty or indifference about the application of these practices in psychological studies.
+Participants' estimates of the proportion of published psychological studies that apply open science practices tended to hover around 50%.
+Although this could imply that participants literally believe these practices are roughly as commonly applied as not, it might also represent participants' uncertainty or indifference about the application of these practices.
 This said, 50% was the modal response for only a minority of practices (open access, data availability on request).
 
-The fact that the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is usually conducted openly.
+That the mean estimated prevalence was no higher than 64% for any practice is inconsistent with the sometime-reported claim that incoming students tend to naively assume that science is conducted openly.
 Nevertheless, the students appear to have at least somewhat over-estimated the prevalence of some open science practices.
@@
 ## Strengths and Limitations
-Despite a relatively large sample size, our results provide an imperfect picture of new psychology students’ methodological understandings.
+Despite a moderate sample size, our results provide an imperfect picture of new psychology students’ methodological understandings.
 Our use of convenience samples coupled with the imprecision of polling students’ impressions at one point in time suggest that we can make only tentative generalisations to a wider population of incoming psychology students.
-In particular, the fact that our sample was relatively small and mostly comprised of students from Australia, NZ, or the United Kingdom limits the extent to which our findings can be generalised to other populations.
+In particular, the fact that our sample mostly comprised students from Australia, NZ, or the United Kingdom limits the extent to which our findings can be generalised to other populations.
 
@@
 It is quite possible that reform in secondary school instruction has improved students’ understandings of more fundamental statistical (e.g., confidence interval estimation) and design (e.g., direct replications) considerations without necessarily influencing their open science attitudes and beliefs.
-Yet, research at the tertiary level casts doubt that the disciplinary reform from the past two decades has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].
+Yet, research at the tertiary level casts doubt that the methodological reform in psychology has had much impact on the content of our teaching [@friedrichReplicatingNationalSurvey2018].
 
-Although we have interpreted our findings with respect to the norm and counternorm items as reflecting  students' personal endorsement of practices, their perceptions of what we might perceive as the "right" answers could have also influenced their responses.
-Differences between endorsement of norms and counternorms may have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and p-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not.
+Although we have interpreted participants' responses to the norm and counternorm items as reflecting  students' personal endorsement of practices, their perceptions of what we might perceive as the "right" answers could have also influenced their responses.
+Differences between endorsement of norms and counternorms might have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and *p*-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not.
 More broadly, our choices of terminology in constructing items likely affected participants' responses to some degree.
-For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item, since failing to "protect" participants' data might sound irresponsible.
+For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item because failing to "protect" participants' data might sound irresponsible.
 Future research could examine the influence of revised language on participants' responses.
@@
 ## Conclusion and Teaching Implications
-Overall these findings suggest that the incoming psychology students had a degree of sympathy for open science norms.
-Nevertheless, despite significant media attention on the replication crisis, few had heard of this crisis.
+Our findings suggest that these incoming psychology students had a degree of sympathy for open science norms.
+Nevertheless, despite significant media attention, few had heard of the replication crisis.
 Similarly, the students seemed to be relatively unfamiliar with responses to the replication crisis (e.g., open science practices).
@@
 
-For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource.
-These questions are available at https://tinyurl.com/excm4heu [blinded].
+For teachers interested in systematically surveying their students' existing understanding of open science practices in psychology, our survey questions could be a useful resource (available at https://tinyurl.com/excm4heu [blinded]).
 
@@
 
-Table A contains the correlations between norms and counternorms, with the 95% confidence intervals and the associated *p*-value.
+Table A contains the correlations between norms and counternorms, with the 95% confidence intervals and associated *p*-values.
 
@@
 At a reviewer's request, we ran an additional exploratory analysis to determine whether
-the proportion of students who are unaware of the replication crisis differs between psychology 
+the proportion of students who are unaware of the replication crisis differed between psychology 
 and non-psychology majors.
-We were able to code the majors for `r length(psyc_major$major_recoded)` students; of these `r round(length(psyc$crisis)/length(psyc_major$crisis)*100, 0)`% reported that psychology was their major.
+We were able to code the majors for `r length(psyc_major$major_recoded)` students; of these, `r round(length(psyc$crisis)/length(psyc_major$crisis)*100, 0)`% reported that psychology was their major.
 
@@
 majors and non-majors in terms of their self-reported awareness of the replication crisis, X^2^ (`r chi$parameter`) = `r round(chi$statistic,2)`, *p* = `r round(chi$p.value,2)`. 
-This lack of a signficant difference should be replicated in a larger population; however, it suggests that psychology instructors should not presume that students choosing to major in psychology are aware of the replication crisis.
+This lack of a significant difference should be replicated in a larger population; however, it suggests that psychology instructors should not presume that students choosing to major in psychology are aware of the replication crisis.
 

### 2022-03-29 analysis/Manuscript.Rmd
deleting random words

@@
 
-Our approach to measuring norms and counternorms focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms (see Table \@ref(tab:normcounternormitems)).
+To measure norms and counternorms, we focussed on participants' evaluations of ten specific open science practices that reflected diverse open science norms (see Table \@ref(tab:normcounternormitems)).
 Although we acknowledge the debatable merits of some of these practices [@TQMP16-4-376; @rubinWhenDoesHARKing2017; @szollosiPreregistrationWorthwhile2020], we selected the items to be emblematic of common concerns in the open science movement.
@@
 Participants rated their agreement separately for each norm and counternorm on a 1 (*strongly disagree*) to 5 (*strongly agree*) scale.
-We used the scenario of a specific researcher rather than referring to psychology researchers in general because it allowed us to make the items more concrete, engaging, and clear.
+We used the scenario of a specific researcher rather than referring to psychology researchers in general because the items were more concrete, engaging, and clear.
 
@@
 
-We also measured participants' normative beliefs about how researchers actually conduct psychological science.
-We asked participants, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)).
-We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included another practice out of interest (data availability on request).
-Participants indicated their estimate on a visual slider from 0% to 100%.
+We measured participants' normative beliefs about how researchers actually conduct psychological science.
+We asked, "When you consider all of the psychology studies conducted globally each year, what percentage of them would have the following characteristics?" These practices corresponded approximately to our ten norm–counternorm pairs, with two exceptions (see Table \@ref(tab:normsinpracticeitems)).
+We excluded the critical thinking norm because it did not refer to externally observable behaviour, and we included data availability on request out of interest.
+Participants provided their estimate on a visual slider from 0% to 100%.
 
@@
 A second question asked participants whether they had heard of the replication crisis.
-Those who had heard of the replication crisis were asked two additional open-ended questions: (1) describe the replication crisis, and (2) name the scientific disciplines most affected by the replication crisis.
+Those who had heard of the crisis were asked two additional open-ended questions: (1) describe the replication crisis, and (2) name the scientific disciplines most affected by the replication crisis.
 
@@
 As preregistered, we calculated the difference in means
-between responses to each norm item and its accompanying counternorm (with 
-95% confidence intervals). For this analysis, we removed three cases with missing values. 
+between responses to each norm item and its accompanying counternorm. For this analysis, we removed three cases with missing values. 
 Table \@ref(tab:differencebetweennormandcounternorm) displays the means and standard deviations for each norm, counternorm, and the difference values.

### 2022-04-02 analysis/Manuscript.Rmd
minor tweaks pre-submission

@@
  Conclusion: Despite media attention about the replication crisis, few incoming psychology students in our sample were familiar with the term.
-The students were nevertheless in favour of most open science practices, although they appeared to overestimate the prevalence of some of these practices in psychology.
- Teaching Implications: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.
+The students were nevertheless in favour of most open science practices, although they overestimated the prevalence of some of these practices in psychology.
+ Teaching Implications: Teachers of incoming psychology students should not assume pre-existing knowledge about open science or replicability.
 keywords: open science, psychology, teaching, reproducibility, replication
-wordcount: (need to update)
+wordcount: 3,009
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
@@
 Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics.
-These contacts were identified via several avenues, including a dedicated session at the Society for the Improvement of Psychological Science 2019 annual conference, a Twitter thread, and through contacts of the research team.
+These contacts were identified via several avenues: a session at the annual meeting of the Society for the Improvement of Psychological Science (2019), a Twitter thread, and through contacts of the research team.
 We did not have inclusion criteria with respect to country, but most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
@@
 Interestingly, only `r round(sum(df$crisis==1, na.rm = TRUE)/length(df$crisis)*100, 0)`% of participants indicated they had heard of "the replication crisis".
-Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis, and `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.
+Most (`r round(sum(df$crisis==2, na.rm = TRUE)/length(df$crisis)*100, 0)`%) indicated that they had not heard of the crisis; `r round(sum(is.na(df$crisis))/length(df$crisis)*100, 0)`% did not respond.
 
@@
 
-*Note* Responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
+*Note:* Responses to the question: \"Imagine that a set of researchers select 100 published studies about psychology, and repeat each study again, exactly how it was described in the original report but with a new set of participants.
 We call repeating a study like this a \'replication study\'.
@@
 Differences between endorsement of norms and counternorms might have also been affected by wording differences between the matched options; for example, the HARKing, information for replicability, and *p*-hacking counternorm items included the phrase "good scientific practice" whereas their matched norm items did not.
-More broadly, our choices of terminology in constructing items likely affected participants' responses to some degree.
+More broadly, our choices of terminology in constructing items might have affected participants' responses to some degree.
 For example, the reference to keeping data "protected" in the open data counternorm item may have nudged participants towards endorsing this item because failing to "protect" participants' data might sound irresponsible.
@@
 We did not investigate the degree to which results differed according to whether or not participants had studied psychology in high school.
-Interested readers could conduct this comparison using our open data.
+Interested readers could conduct this and other comparisons using our open data.
 
@@
 # Supplemental Materials
+
+The supplemental materials contain three sets of results and details of the R packages we used in our analyses.
+In order, the three results are: (1) the correlations between norm and counternorm items; (2) histograms of participants’ prevalence ratings for each of the norms in practice items; and (3) an additional exploratory analysis examining whether the proportion of students who are unaware of the replication crisis differed between psychology and non-psychology majors.
 
@@
 knitr::kable(corr,
-             caption = "Correlations between Norms and Counternorms with the 95% Confidence Intervals (in Square Brackets) and the Associated p-values",
+             caption = "Correlations between Norms and Counternorms with 95% Confidence Intervals (in Square Brackets) and Associated p-values",
              digits = 2,
@@
 
-<!-- We have a four references that aren't including the urls. Including here so we can add them to the final document.
+<!-- We have four references that aren't including the urls. Including here so we can add them to the final document.
+
+Beaudry, J. L., Kaufman, J., Johnstone, T., & Given, L. (2019). Swinburne Open Science Task Force Survey Report. https://osf.io/eczvd/
 
@@
 https://www.sciencemag.org/news/2020/12/psychology-s-replication-crisis-inspires-ecologists-push-more-reliable-research
-
-Vazire, S. (2019). Do we want to be credible or incredible? Association for Interdisciplinary Meta-research & Open Science conference, Melbourne. https://osf.io/thm9a/
 

### 2022-04-02 preprocessing/preprocessing_students.R
remove unnecessary comments

@@ -94,8 +94,7 @@ df <- meta_rename(df, metadata, old = old_variable, new = new_variable)
 
 
 ###### REARRANGE THE VARIABLES IN THE TIBBLE TO ALIGN WITH SURVEY ORDER ######
-# at least somewhat; I haven't moved the number and label variables of each
-  # question together, but this brings the demographics info together
+# bring the demographics info together
 
 df <- df %>%
   relocate (c(uni_country, nationality), .after = gender)
@@ -166,11 +165,8 @@ df <- df %>%
   # also need to exclude those who were eligible, but did not answer any of the
   # key questions (nmiss = 32).
 
-# breadcrumb: add the exclusion variables to the dataframe & metadata (and remove when
-  # loading metadata) [still need to do!]
-
-# create new variables for each of the eliibility criteria
-  # capture the hieararchy of decisions, but forcing previously-excluded cases to
+# create new variables for each of the eligibility criteria
+  # capture the hierarchy of decisions, but forcing previously-excluded cases to
   # be recoded as "N/A" for each subsequent criterion
 
 df <- df %>%
@@ -395,6 +391,7 @@ df <- df %>%
 # For participants who mention a major in psychology, code as "psychology"
 # For participants who do not, code as "not psychology"
 # Code all students in a psychology degree as having a psychology major
+
 df <- df %>%
   mutate(major_recoded = toTitleCase(major)) %>%
   mutate(

### 2022-04-02 preprocessing/preprocessing_students.R
update comment

@@ -505,4 +505,4 @@ write.csv(df, here::here("data", "students_processed.csv"), row.names = FALSE)
 # write this one variable to a csv file for coding
 write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), here::here( "data", "crisis_descriptions.csv"))
 
-#written for manual coding, which is then used in Rmd
+#written for manual coding; the coded data is then used in Rmd

### 2022-04-04 analysis/Manuscript.Rmd
update word count

@@
 keywords: open science, psychology, teaching, reproducibility, replication
-wordcount: 3,009
+wordcount: 3009
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']

### 2022-04-09 analysis/Manuscript.Rmd
add text re twitter thread

@@
 keywords: open science, psychology, teaching, reproducibility, replication
-wordcount: 3009
+wordcount: 3011
 bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
@@
 # convert variables to factors as needed
-df$age <- as_factor(df$age)
+df$age <- as_factor(wtdf$age)
 df$eligibility <- as_factor(df$eligibility)
@@
 Contacts from tertiary institutions in Australia, New Zealand, the UK, and the USA invited students enrolled in their first-year psychology course to participate in the online survey hosted on Qualtrics.
-These contacts were identified via several avenues: a session at the annual meeting of the Society for the Improvement of Psychological Science (2019), a Twitter thread, and through contacts of the research team.
+These contacts were identified through several avenues: direct contact with our colleagues, a session at the international meeting of the Society for the Improvement of Psychological Science (2019), and a Twitter thread with >15,000 impressions.
 We did not have inclusion criteria with respect to country, but most contacts who advertised the study were from the United Kingdom, Australia, or New Zealand.
